### 2016-03-08 paper/laes_bayes.tex
overleaf

\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
%\documentclass{latex/emulateapj} 
%External Packages and personalized macros
%=========================================================================
%		EXTERNAL PACKAGES
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
%\usepackage[section]{placeins}
\usepackage {graphicx}
%\usepackage{graphics}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{caption}
%Non reposionated tables
\usepackage{float}
\restylefloat{table}
%Multiple columns support for tables
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}
\pdfminorversion=5

%=========================================================================
%		INTERNAL MACROS
%=========================================================================
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}

\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\apj}{ApJ}  
\newcommand{\apjs}{ApJS}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc}\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc}\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Mmin}{{\ifmmode{{M_{\rm min}}}\else{${M_{\rm min}}$}\fi}}
\newcommand{\mmin}{{\ifmmode{{M_{\rm min}}}\else{${M_{\rm min}}$}\fi}}
\newcommand{\mmax}{{\ifmmode{{M_{\rm max}}}\else{${M_{\rm max}}$}\fi}}
\newcommand{\lmmin}{{\ifmmode{{\log M_{\rm min}}}\else{${\log M_{\rm min}}$}\fi}}
\newcommand{\lmmax}{{\ifmmode{{\log M_{\rm max}}}\else{${\log M_{\rm max}}$}\fi}}

\newcommand{\Mmax}{{\ifmmode{{M_{\rm max}}}\else{${M_{\rm max}}$}\fi}}
\newcommand{\dm}{{\ifmmode{{\Delta M}}\else{$\Delta M$}\fi}}
\newcommand{\dlm}{{\ifmmode{{\Delta \log M}}\else{$\Delta \log M$}\fi}}
\newcommand{\focc}{{\ifmmode{{f_{\rm occ}}}\else{${f_{\rm occ}}$}\fi}}

\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
%SAMPLES
\newcommand{\GHBDM}{\texttt{GH}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\GHFOF}{\texttt{GH}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\IHBDM}{\texttt{IH}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\IHFOF}{\texttt{IH}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\PBDM}{\texttt{P}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\PFOF}{\texttt{P}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\IPBDM}{\texttt{IP}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\IPFOF}{\texttt{IP}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\RIPBDM}{\texttt{RIP}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\RIPFOF}{\texttt{RIP}$_{\mbox{\tiny{FOF}}}$ }

%MY COMMANDS #############################################################
\newcommand{\sub}[1]{\mbox{\scriptsize{#1}}}
\newcommand{\dtot}[2]{ \frac{ d #1 }{d #2} }
\newcommand{\dpar}[2]{ \frac{ \partial #1 }{\partial #2} }
\newcommand{\pr}[1]{ \left( #1 \right) }
\newcommand{\corc}[1]{ \left[ #1 \right] }
\newcommand{\lla}[1]{ \left\{ #1 \right\} }
\newcommand{\bds}[1]{\boldsymbol{ #1 }}
\newcommand{\oiint}{\displaystyle\bigcirc\!\!\!\!\!\!\!\!\int\!\!\!\!\!\int}
\newcommand{\mathsize}[2]{\mbox{\fontsize{#1}{#1}\selectfont $#2$}}
\newcommand{\eq}[2]{\begin{equation} \label{eq:#1} #2 \end{equation}}
\newcommand{\lth}{$\lambda_{th}$ }
\newcommand{\reff}{{\ifmmode{r_{\mbox{\tiny eff}}}\else{$r_{\mbox{\tiny eff}}$}\fi}}
%#########################################################################

%TO DO COMMANDS. Highlight region that needs extra work  #############################################################
\newcommand{\todo}{\ifmmode \text{\Huge{\(\bullet\)}} \else {\Huge$\bullet$}\fi}
% \newcommand{\todo}{\ifmmode {\Huge \bullet} \else {\Huge$\bullet$}\fi}
\newcommand{\tido}{\ifmmode {\bullet} \else $\bullet$\fi}
\newcommand{\REFS}{(\todo REFS) }
\newcommand{\toref}{(\todo REFS)}
%#########################################################################

\begin{document}

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3$}
\author[J. Mejia-Restrepo and J.E. Forero-Romero]{\parbox[t]{\textwidth}{\raggedright 
  J. Mejia-Restrepo \thanks{jemejia@das.uchile.cl}$^{1}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}
\vspace*{6pt}\\
$^1,^3$Departamento de Astronom\'{i}a, Universidad de Chile, Camino el Observatorio 1515, Santiago, Chile\\
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

\maketitle

\begin{abstract}
We present
\end{abstract}

\begin{keywords}
Cosmology: theory - large-scale structure of Universe -
Methods: data analysis - numerical - N-body simulations
\end{keywords}

% JF - 1. Intro 3/10
% JF - 2. Methodology 1/7

%*************************************************************************
\section{Introduction}
\label{sec:introduction}
\toref ADD NEWER REFERENCES
Lyman-$\alpha$ emitting galaxies (LAEs) are central to a wide range
of subjects in extragalactic astronomy. 
LAEs can be used as probes of reionization \citep{Dijkstra11}, tracers of large scale structure \citep{Koehler2007},  signposts for low metallicity stellar populations, markers of the galaxy formation process at high redshift \citep{Dayal2009,ForeroRomero2012} and tracers of active star formation \citep{Guaita2013}.

In most of those cases, capitalizing the observations requires  understanding how LAEs are formed within an explicit cosmological context. 
Under the current structure formation paradigm the dominant matter content of the Universe is dark matter (DM). 
Each galaxy is thought to be hosted by a larger dark matter structure known as a halo. \citep{Peebles1980,SpringelNature05}. 
Understanding the cosmological context of LAEs thus implies studying the galaxy-halo connection. 
Galaxy formation models suggest that the physical processes that regulate the star formation cycle are dependent on halo mass \citep{Behroozi2013a}.
The mass becomes the most important element in the halo-galaxy connection.

The goal becomes finding the typical DM halo mass of halos hosting LAES.
In the case of LAEs there are different ways to find this mass range.
One approach is theoretical, using general astrophysical principles to find the relationship between halo mass, intrinsic \ly\ luminosities and observed \ly\ luminosities. This approach is usually implemented through semi-analytic models \citep{Garel2012,Orsi2012} and  full N-body hydrodynamical simulations \citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012}.

%JF

The downside of these calculations is the uncertainty in the estimation of the escape fraction of \ly\ photons. Given the resonant nature of the \ly\ line, the escape fraction is sensitive to  the dust contents, density, temperature, topology and kinematics of the neutral Hydrogen in the interstellar medium (ISM). The process of finding a consensus on the expected value
for the \ly\ escape fraction in high redshift galaxies is still matter
of open debate
\citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.

A different approach to infer the typical mass of halos hosting
LAEs is based on the spatial clustering information. 
This approach uses the fact
that in CDM cosmologies the spatial clustering of galaxies on large
scales is entirely dictated by the halo distribution
\citep{Colberg00}, which in turn has a strong dependence on halo
mass. 
Using measurements of the angular correlation function of LAEs,
observers have put constraints on the typical mass and occupation
fraction of the putative halos hosting these galaxies
\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010,Bielby16}. 
In these studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
the conclusions derived on the halo host mass do not elaborate on the uncertainty resulting from the cosmic variance on these fields.

In this letter we investigate the impact of cosmic variance in
constraining the mass and occupation fraction of halos hosting LAEs at $z=3$.
We build mock surveys from a cosmological N-body to compare them against the observations in \cite{Bielby16} using the angular correlation function. 
We use a simple model to populate a halo in the simulation with a LAE   
assuming a minimum (\mmin) and maximum mass (\mmax) for the dark matter halos hosting LAEs without predicting a \ly\  luminosity. 
This approach bypasses all the physical uncertainties associated to star formation and radiative transfer.
We use the Markov Chain Monte Carlo technique to obtain the likelihood of the parameters given the observational constraints.

Throughout this letter we assume a $\Lambda$CDM cosmology with the
following values for the cosmological parameters, $\Omega_{m}=0.27$,
$\Omega_{\Lambda}=0.73$ and $h=0.70$, corresponding to the matter
density, vacuum density and the Hubble constant in units of 100 km
s$^{-1}$ Mpc$^{-1}$.

\section{Methodology}

The base of our method is the comparison between observations and mock
catalogs. 
This approach allows us to take explicitly into account cosmic variance. 
The comparison has four key elements. First, the observations we take as a benchmark. Second, the N-body simulation and the halo catalogs we use to build the mocks. Third, the parameters describing our model to assign a LAE to a halo. Fourth, the statistical method we adopt to compare observations and simulations.
We describe in detail these four elements in the following subsections.

\begin{figure*}
\includegraphics[width=0.99\textwidth]{likelyplot_1deg_total.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degf.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degdM.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degdMf.png}
\caption{Likelihood}
\label{fig:like}
\end{figure*}

\subsection{Observational constraints}
\label{subsec:obs}
\citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA and a flux limit
of $2\times10^17{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
Using spectroscopy they found a 22\% contamination fraction.
Their observations cover 5 (out of 9) independent and co-spatial fields of the VLT LBG Redshift Survey (VLRS). 
The  total observed  area corresponds to 1.07$\rm deg^2$ that translates to
$\sim$80$^2\hMpc^2$ in a comoving scale. \citet{Bielby16} used the
NB497  narrow-band filter whose 77\AA FWHM and 154\AA FWTM correspond to a total observational depth of 44\hMpc  and 82\hMpc comoving, respectively.

%JF

\subsection{Simulation and halo catalog}
\label{subsec:sim}

We use results from the \todo Bolshoi simulation \citep{Bolshoi}\toref which was performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side. The dark matter distribution was sampled using \todo $2048^{3}$ particles. The cosmological parameters are consistent with a Wilkinson Microwave Anisotropy Probe (WMAP) ninth year data \todo PLANK? (\toref) with a matter density
$\Omega_{\rm m} = 0.307$, cosmological constant
$\Omega_{\Lambda}=0.693$, dimensionless Hubble constant $h=0.70$, slope
of the power spectrum \todo $n=0.95$ and normalization of the power
spectrum\todo $\sigma_{8}=0.82$ \todo.  
This translates into a particle mass of \todo $m_{\rm p}=1.54\times 10^{8}$ $h^{-1}$ M$_{\odot}$.

We use halo catalogs constructed with a Bound-Density-Maxima (BDM) algorithm. The catalogs were obtained from the publicly available
Multidark database \todo \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{MultiDark}. For each
halo in the box we extract its comoving position and mass. 
We focus our work on halos more massive than $1.54\times 10^{9}$\hMsun resolved with at least  $10$ particles.
%the reasons for this choice are explained in the next sub-section.

We divide the total volume of the snapshot of the simulation at z$\sim$3
into  27 smaller mock volumes mimicking the  comoving area and depth  
reported in \citet{Bielby16} and described in \S \ref{subsec:obs}. 
This allows  us  to take explicitly into account the effects of cosmic variance.

\subsection{A model to populate halos with LAEs}
\label{subsec:mocks}

We build a model to assign LAEs to a DM halo. 
We are not concerned on the exact LAE luminosity, we only care about a yes/no answer to the following question. Does this halo host a LAE?

We first assume that a dark matter halo can host one detectable LAE at most.  
This assumption is consistent with theoretical analysis of the correlation function \citep{Jose2013b} and observations that confirm a lack of class pairs in LAEs \cite{Bond2009}.

Then we say that a halo will host a LAE with probability $f_{\rm occ}$ if and only if the halo mass is in the range $M_{\rm min}< M_{\rm h} < M_{\rm max}$.
The probability $f_{\rm occ}$ can be thought as the occupation fraction of halos which can be automatically set as the ration of the observed number of LAEs to the number of halos within the considered mass range, that is $f_{\rm occ}\equiv N_{\rm LAE}/N_{\rm halos}$.

The occupation fraction varies along  the mock fields tracing the cosmic variance changing in a factor $\sim 2$ ($\sim 0.3$, see left panel in Fig. \ref{fig:cosmicv}). The interpretation of the occupation fraction $f_{\rm occ}$ involves two phenomena: the actual presence of a star forming galaxy in a halo and its detectability as a LAE.

We do not explore any physical model to disentangle these two effects. This means that our model does not assign a luminosity or escape fraction to each
LAE.
We avoid this in order to maintain theoretical uncertainties to a minimum. 
This flexibility allows us to explore a wide range of possible masses for
the host halos without any strong theoretical prejudice regarding the
details of star formation and \ly\  escape fraction.

We also artificially contaminate our mock catalogs with 22$\%$ randomly distributed data points to mimic the fraction of interlopers in observations \citet{Bielby16} .
On top of that we apply rejection sampling  to our LAE selection taking the transmission function of the NB479 filter used in their observations as a radial selection factor.

In what follows we note by the letter ${\mathcal M}$ a model
defined by a particular choice of the two parameters $M_{\rm min}$, 
$M_{\rm  max}$. For each model  ${\mathcal M}$ we define $\tilde{f}_{\rm occ}$ as the median occupation fraction within the the mock fields and  $\Delta M \equiv \mmax-\mmin$.

\subsection{Exploring and selecting consistent models}

We use the angular correlation function to compare the observations with our mock catalogs. 
This is done trough a thorough exploration of the parameter space of the models ${\mathcal M}$  by  means of a Monte Carlo Markov Chain minimization using  the EMCEE python package \citep{emcee2013}.
We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ to vary between  $9.2$ up to $13.4$, corresponding to the halo mass range of the simulation at $z=3$. 
Given that the typical scatter  in $N_{\rm halos}$ is about 0.3 dex (i.e. about  a factor of 2), our parameter space is restricted to models where the median number of dark matter halos is larger than  $N_{\rm LAE}/3$. 
The MCMC exploration is done using a total of 24 seeds and 400 iterations (9600 models) to sample the posterior PDF,  $P(\mmin, \mmax, f_{\rm occ}| \mathcal{M}) \propto \exp(-\chi_{\mathcal M}^2/2)$, with

\begin{equation}
\chi_{\mathcal M}^2=\sum_{\theta}\left[\frac{\left( \rm{ACF}_{\mathcal M}\left(\theta\right) - \rm{ACF}_{\rm obs}\left(\theta\right)\right)^2}{ \sigma_{\rm \mathcal M}^{2}\left(\theta\right) + \sigma_{\rm obs}^{2}\left(\theta\right)}\right]
\end{equation}
%
where  $\rm{ACF}_{\mathcal M}$ and  $\rm{ACF}_{\rm obs}$ are the ACF of the explored model ${\mathcal M}$ and the observational ACF reported by \citet{Bielby16} respectively. $\sigma_{\rm \mathcal M}$ is the associated 1-$\sigma$ scatter 
of the $\rm{ACF}_{\mathcal M}$ as a product of cosmic variance and $\sigma_{\rm obs}$ is the observational error associated to $\rm{ACF}_{\rm obs}$.  The $\rm{ACF}_{\mathcal M}$s are computed using  the Landy \&  Szalay estimator  \citep{Landy1993}.

\section{Results and Discussion}

\subsection{Constraining \mmin, \mmax and \focc in DHM hosting LAEs}

In Fig. \ref{fig:like} the posterior probability distributions in the \mmin-\mmax, \mmin-\focc, \mmin-\dm, \mmax-\focc, \mmax-\dm and \focc-\dm\ parameter spaces. We find that the \mmin and \mmax parameter space cannot be well constrained mainly because of cosmic variance and the large observational Poisonnian uncertainty in the ACF. We however found that 10.0$<\log \mmin<$11.1 and 11.0$<\log\mmax<$12.8.   We interestingly find that \focc\ is basically completely determine by \mmin  going from \focc$=$0.015 when $\log\mmin=$10.0 to \focc$=$0.43 when $\log\mmin=$11.1. We remark that those models where $\log \focc>0.0$ ($\focc>1$) correspond 
to models where the number density  of halos is smaller than the number of observed LAEs but are
still consistent because of the uncertainty in the median number of LAEs in the universe due to cosmic variance.

\begin{figure}
\includegraphics[width=0.47\textwidth]{mmin_dev.png}
\includegraphics[width=0.47\textwidth]{corr.png}
\caption{Left: $\log M_{\rm min}$ vs $\log M_{\rm 50\%}$ (black), $\log M_{\rm 16\%}$-$\log M_{\rm 84\%}$ (blue) and  $\log M_{\rm 2.5\%}$-$\log M_{\rm 97.5\%}$(red) for different values of $\log M_{\rm max}$. The points are color coded by $\Delta \log M\left[\rm{M_{\odot}h^{-1} ]}\right]$. THe green line accounts for the 1:1 relation. Right: Angular Correlation functions for $\log M_{\rm min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta M$. The error bars represent the 1 sigma deviation due to cosmic variance.}
\label{fig:mmed}
\end{figure}

\subsection{Halo mass distribution within models}

In  the top panel of Fig. \ref{fig:mmed} we show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue diamonds) and 95 ($\log M_{95}$, red squares) percentiles of the LAE halo mass as a function of \lmmin\ for each of the models that we run in our MCMC simulation.  The points are color coded according to their \dlm\ associated value. We can see that the median mass, $M_{50}$, and $M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially when $\dlm\gtrsim1.0$dex. We particularly found that  $\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that $\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$ regardless of the value of \dlm. The latter is a consequence of the very steepen distribution of the dark matter mass function  and is at the same time the reason for the almost perfect one to one relation between \mmin\ and \focc. However, it can also be seen in Fig. \ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax ($\lmmin+0.2\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+1.5\rm{dex}$). Thereby, any differences in the clustering strength of models sharing the same \mmin but different \mmax should be mainly driven by the  $\sim16\%$ most massive  halos of each model $\mathcal{M}$.

In order to estimate the effect of most massive halos in  $ACF_{\mathcal{M}}$ in the bottom panel of Fig. \ref{fig:mmed} we show the computed $ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values of $\dlm$. We can see that the clustering gets stronger for larger values of \dlm. Nevertheless, due to the large impact of cosmic variance at the volume of the current observations all the models  are basically consistent within errors. The last result explain the current difficulty to put tighter constrains in \lmmax\ in our model.

\subsection{Constraining DMH mass with cosmic variance}
In the left panel of Fig. \ref{fig:cosmicv} we show the number halo distribution (NHD) in the  mock fields of the simulation for different models $\mathcal{M}$. By simple inspection one can infer an increase in the distribution with as \lmmin increase.  This trend is confirmed in the right panel of Fig. \ref{fig:cosmicv}  where we plot the central 1-$\sigma$ (blue diamonds) and 2-$\sigma$  (red dots) widths  of the NDH as a function of \lmmin. We particularly found that when we consider survey fields of $\sim1{\rm deg^2}$, the central  1-$\sigma$ (2-$\sigma$) width of the NHD increases monotonically from 0.05dex (0.10dex) when $\lmmin=9.5$ to 0.20dex (0.35dex) when $\lmmin=12.0$. The latter result opens the possibility to constrain the \lmmin (as well as the median mass) of LAEs by simply measure the width of the distribution of observed LAE along several observational fields mapping $\sim1{\rm deg^2}$ in area and the observational depth determined by the NB479 filter.

%*************************************************************************

\begin{figure}
\includegraphics[width=0.23\textwidth, height=0.19\textwidth]{ndist.png}
\includegraphics[width=0.23\textwidth, height=0.19\textwidth]{mmin_dfocc1.png}
\caption{Left: Halo number distribution  over the 54 mock field of the simulation for different models of $M_{\rm min}$-$M_{\rm max}$.Right:Width of the halo number distribution over the 54 mock field of the simulation ($\Delta \log \left( N_{\rm halos}/\tilde{N}_{\rm halos}\right)$) of the central 68 (blue diamonds) and  95(red circles)  percentiles vs $M_{\rm min}$. Points are color coded according to their associated value of $\Delta M \equiv M_{\rm min}-M_{\rm min}$. }
\label{fig:cosmicv}
\end{figure}

\bibliographystyle{mn2e}
\bibliography{references.bib}

\end{document}

### 2016-03-20 paper/ms.tex
new names

--- 2016-03-08 paper/laes_bayes.tex
@@
-\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
-%\documentclass{latex/emulateapj} 
+\documentclass{emulateapj} 
+%\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e}
+
 %External Packages and personalized macros
@@
 %=========================================================================
+%\usepackage{amsmath} 
+%\usepackage{amssymb} 
+%\usepackage[section]{placeins}
+
+\usepackage {graphicx}
+
 \usepackage{amsmath}
 \usepackage{amssymb}
-%\usepackage[section]{placeins}
+\usepackage{graphics}
+\usepackage{epsfig}
+\usepackage{float}
+\bibliographystyle{apj}
+
 \usepackage {graphicx}
+
 %\usepackage{graphics}
-\usepackage[dvips]{epsfig}
-\usepackage{epsfig}  
+%\usepackage[dvips]{epsfig}
+%\usepackage{epsfig}  
 \usepackage{color}
@@
 %Non reposionated tables
-\usepackage{float}
+%\usepackage{float}
 \restylefloat{table}
@@
 \newcommand{\zz}{$z\sim 3$} 
-\newcommand{\apj}{ApJ}  
-\newcommand{\apjs}{ApJS}  
-\newcommand{\apjl}{ApJL}  
-\newcommand{\aj}{AJ}  
-\newcommand{\mnras}{MNRAS}  
-\newcommand{\mnrassub}{MNRAS accepted}  
-\newcommand{\aap}{A\&A}  
-\newcommand{\aaps}{A\&AS}  
-\newcommand{\araa}{ARA\&A}  
-\newcommand{\nat}{Nature}  
-\newcommand{\physrep}{PhR}
-\newcommand{\pasp}{PASP}    
-\newcommand{\pasj}{PASJ}    
+%\newcommand{\apj}{ApJ}  
+%\newcommand{\apjs}{ApJS}  
+%\newcommand{\apjl}{ApJL}  
+%\newcommand{\aj}{AJ}  
+%\newcommand{\mnras}{MNRAS}  
+%\newcommand{\mnrassub}{MNRAS accepted}  
+%\newcommand{\aap}{A\&A}  
+%\newcommand{\aaps}{A\&AS}  
+%\newcommand{\araa}{ARA\&A}  
+%\newcommand{\nat}{Nature}  
+%\newcommand{\physrep}{PhR}
+%\newcommand{\pasp}{PASP}    
+%\newcommand{\pasj}{PASJ}    
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
@@
 %=========================================================================
-\title{Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3$}
-\author[J. Mejia-Restrepo and J.E. Forero-Romero]{\parbox[t]{\textwidth}{\raggedright 
-  J. Mejia-Restrepo \thanks{jemejia@das.uchile.cl}$^{1}$,
+\title{Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$}
+\author{
+  Juli\'an E. Mej\'ia-Restrepo \thanks{jemejia@das.uchile.cl}$^{1,3}$,
   Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
 }
-\vspace*{6pt}\\
-$^1,^3$Departamento de Astronom\'{i}a, Universidad de Chile, Camino el Observatorio 1515, Santiago, Chile\\
+
+\affil{
+$^1$Departamento de Astronom\'{i}a, Universidad de Chile, Camino el Observatorio 1515, Santiago, Chile\\
 $^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
-No. 18A-10, Edificio Ip, Bogot\'a, Colombia
+No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
+$^3$FACom-Instituto de F\'isica-FCEN, Universidad de Antioquia, Calle 70 No. 52-21, Medell\'in, Colombia
 }
 
-\maketitle
-
 \begin{abstract}
-We present
+We study the impact of cosmic variance and observational uncertainties in constraining the mass and  occupation fraction ($f_{\rm occ}$) of dark matter halos hosting \ly\ Emitting  Galaxies at high redshift (LAEs).
+We use a N-body simulation to construct mock catalogs with the same typical size  of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$) to match the observed  angular correlation function (ACF) and number density of LAEs.
+In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm   max}$ can only host one detectable LAE at most.
+By following a thorough Markov Chain Monte-Carlo exploration of the parameter space determined by $M_{\rm min}$ and $M_{\rm   max}$, our analysis shows that $f_{\rm occ}$ is uniquely determined by $M_{\rm min}$ regardless of $M_{\rm max}$ using the relation $\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$ .
+However, the current observational data only allows us to put weak constraints on $M_{\rm min}$, $M_{\rm max}$ and consequently on $f_{\rm occ}$. 
+Particularly, we find that $10^{9.6}\hMsun\leq M_{\rm min}\leq 10^{11.0}\hMsun$ , $10^{10.9}\hMsun\leq M_{\rm max}\leq 10^{13.0}\hMsun$ and $0.02\leq f_{\rm occ}\leq 0.30$. 
+Nevertheless, we also find that  the upcoming large surveys can help to put tighter constraints on $M_{\rm min}$ and $f_{\rm occ}$ through the width measurement of the LAE number distribution function obtained over several fields of the same size of current observations.
+Analogously, the  improvement in the precision of the measured ACF will assist in constraining $M_{\rm max}$.  
 \end{abstract}
 
-\begin{keywords}
+\keywords{
 Cosmology: theory - large-scale structure of Universe -
 Methods: data analysis - numerical - N-body simulations
-\end{keywords}
+}
 
@@
 
-The goal becomes finding the typical DM halo mass of halos hosting LAES.
+The goal becomes finding the typical DM halo mass of halos hosting LAEs.
 In the case of LAEs there are different ways to find this mass range.
@@
 Throughout this letter we assume a $\Lambda$CDM cosmology with the
-following values for the cosmological parameters, $\Omega_{m}=0.27$,
-$\Omega_{\Lambda}=0.73$ and $h=0.70$, corresponding to the matter
+following values for the cosmological parameters, $\Omega_{m}=0.30711$,
+$\Omega_{\Lambda}=0.69289$ and $h=0.70$, corresponding to the matter
 density, vacuum density and the Hubble constant in units of 100 km
 s$^{-1}$ Mpc$^{-1}$.
+
+\begin{figure}
+\includegraphics[width=0.46\textwidth, height=0.38\textwidth]{ndist.png}
+\caption{Cumulative halo number distribution function over the 27 mock fields of the simulation for different models of $M_{\rm min}$-$M_{\rm max}$.}
+\label{fig:cosmicv0}
+\end{figure}
 
@@
 %\includegraphics[width=0.47\textwidth]{likelyplot_1degdMf.png}
-\caption{Likelihood}
+\caption{One and two dimensional projections of the posterior probability distributions of \mmin, \mmax and \focc as described in the label of each sub-figure.}
 \label{fig:like}
@@
 \citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
-at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA and a flux limit
+at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA\ and a flux limit
 of $2\times10^17{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
@@
 
-We use results from the \todo Bolshoi simulation \citep{Bolshoi}\toref which was performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side.
-The dark matter distribution was sampled using \todo $2048^{3}$ particles.
-The cosmological parameters are consistent with a Wilkinson Microwave Anisotropy Probe (WMAP) ninth year data \todo PLANK?
-(\toref) with a matter density
+We use results from the  Bolshoi simulation \citep{Bolshoi} which was performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side.
+The dark matter distribution was sampled using  $2048^{3}$ particles.
+The cosmological parameters are consistent with Planck 2013 results \citep{Planck2014} with a matter density
 $\Omega_{\rm m} = 0.307$, cosmological constant
 $\Omega_{\Lambda}=0.693$, dimensionless Hubble constant $h=0.70$, slope
-of the power spectrum \todo $n=0.95$ and normalization of the power
-spectrum\todo $\sigma_{8}=0.82$ \todo.  
-This translates into a particle mass of \todo $m_{\rm p}=1.54\times 10^{8}$ $h^{-1}$ M$_{\odot}$.
+of the power spectrum  $n=0.96$ and normalization of the power
+spectrum $\sigma_{8}=0.82$.  
+This translates into a particle mass of  $m_{\rm p}=1.54\times 10^{8}$ $h^{-1}$ M$_{\odot}$.
 
 We use halo catalogs constructed with a Bound-Density-Maxima (BDM) algorithm. The catalogs were obtained from the publicly available
-Multidark database \todo \footnote{{\tt
+Multidark database  \footnote{{\tt
     http://www.multidark.org/MultiDark/}} \citep{MultiDark}. For each
@@
 
-The occupation fraction varies along  the mock fields tracing the cosmic variance changing in a factor $\sim 2$ ($\sim 0.3$, see left panel in Fig.
-\ref{fig:cosmicv}).
+Fig.
+\ref{fig:cosmicv0}  shows the cumulative halo number distribution (HND) in the  mock fields of the simulation for different models $\mathcal{M}$.
+From this figure we can see that the number of dark matter halos along the mock fields for different models $\mathcal{M}$ varies within a factor of $\sim 2$ ($\sim 0.3$dex) tracing the cosmic variance.
+As a consequence, the occupation fraction varies along  the mock fields  by the same factor factor.
 The interpretation of the occupation fraction $f_{\rm occ}$ involves two phenomena: the actual presence of a star forming galaxy in a halo and its detectability as a LAE.
@@
 
-\subsection{Constraining \mmin, \mmax and \focc in DHM hosting LAEs}
+\subsection{Constraining \mmin, \mmax\ and \focc\ in Dark Matter Halos hosting LAEs}
 
 In Fig.
-\ref{fig:like} the posterior probability distributions in the \mmin-\mmax, \mmin-\focc, \mmin-\dm, \mmax-\focc, \mmax-\dm and \focc-\dm\ parameter spaces.
-We find that the \mmin and \mmax parameter space cannot be well constrained mainly because of cosmic variance and the large observational Poisonnian uncertainty in the ACF.
-We however found that 10.0$<\log \mmin<$11.1 and 11.0$<\log\mmax<$12.8.
-We interestingly find that \focc\ is basically completely determine by \mmin  going from \focc$=$0.015 when $\log\mmin=$10.0 to \focc$=$0.43 when $\log\mmin=$11.1.
-We remark that those models where $\log \focc>0.0$ ($\focc>1$) correspond
+\ref{fig:like} we present yhe one and two dimensional projections of the posterior probability distributions of \mmin, \mmax and \focc.
+We find that the \mmin and \mmax parameter space cannot be tightly constrained mainly because of cosmic variance and the large observational Poisonnian uncertainty in the ACF.
+We however found that 9.6$<\log \mmin<$11.0 and 10.9$<\log\mmax<$13.0.
+We interestingly find that \focc\ is basically completely determined by \mmin  going from \focc$=$0.015 when $\log\mmin=$9.6 to \focc$=$0.30 when $\log\mmin=$11.0  ($\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$).
+We remark that those models where $\log \focc>0.00$ ($\focc>1$) correspond
 to models where the number density  of halos is smaller than the number of observed LAEs but are
-still consistent because of the uncertainty in the median number of LAEs in the universe due to cosmic variance.
+still consistent because of the uncertainty in the median number density of LAEs in the universe due to cosmic variance (see Fig.
+\ref{fig:cosmicv0}).%in the number of dark matter halos along the mock fields
 
 \begin{figure}
-\includegraphics[width=0.47\textwidth]{mmin_dev.png}
-\includegraphics[width=0.47\textwidth]{corr.png}
-\caption{Left: $\log M_{\rm min}$ vs $\log M_{\rm 50\%}$ (black), $\log M_{\rm 16\%}$-$\log M_{\rm 84\%}$ (blue) and  $\log M_{\rm 2.5\%}$-$\log M_{\rm 97.5\%}$(red) for different values of $\log M_{\rm max}$.
+\includegraphics[width=0.47\textwidth]{mmin_mmed_colordm.png}
+\caption{ $\log M_{\rm min}$ vs $\log M_{\rm 50\%}$ (black), $\log M_{\rm 16\%}$-$\log M_{\rm 84\%}$ (blue) and  $\log M_{\rm 2.5\%}$-$\log M_{\rm 97.5\%}$(red) for different values of $\log M_{\rm max}$.
 The points are color coded by $\Delta \log M\left[\rm{M_{\odot}h^{-1} ]}\right]$.
-THe green line accounts for the 1:1 relation.
-Right: Angular Correlation functions for $\log M_{\rm min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta M$.
-The error bars represent the 1 sigma deviation due to cosmic variance.}
+The green line diagonal line accounts for the 1:1 relation and the green vertical lines represent  the 16, 50 and 84 percentiles  of the posterior probability distribution of \mmin.}
 \label{fig:mmed}
@@
 
-In  the top panel of Fig.
+Previous  attempts to constrain the DMH mass of LAEs by means of the ACF   present their result in terms of the median mass of LAEs that is derived from the derived correlation length by means of semi-analitical prescriptions  \citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}.
+Instead, in this work we directly compare the ACF of our simulated mock catalogs with the observational ACF and present our results in terms of a  minimum and maximum mass DMH hosting LAEs.
+It is therefore necessary to connect our approach by computing the median mass of the DMH in each of the models $\mathcal{M}$.
+In   Fig.
 \ref{fig:mmed} we show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue diamonds) and 95 ($\log M_{95}$, red squares) percentiles of the LAE halo mass as a function of \lmmin\ for each of the models that we run in our MCMC simulation.
 The points are color coded according to their \dlm\ associated value.
-We can see that the median mass, $M_{50}$, and $M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially when $\dlm\gtrsim1.0$dex.
+We can see that the median mass ($M_{50}$) and $M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially when $\dlm\gtrsim1.0$dex.
 We particularly found that  $\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that $\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$ regardless of the value of \dlm.
@@
 
-In order to estimate the effect of most massive halos in  $ACF_{\mathcal{M}}$ in the bottom panel of Fig.
-\ref{fig:mmed} we show the computed $ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values of $\dlm$.
+In order to estimate the effect of most massive halos in  $ACF_{\mathcal{M}}$ in Fig.
+\ref{fig:corr} we show the computed $ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values of $\dlm$.
 We can see that the clustering gets stronger for larger values of \dlm.
 Nevertheless, due to the large impact of cosmic variance at the volume of the current observations all the models  are basically consistent within errors.
-The last result explain the current difficulty to put tighter constrains in \lmmax\ in our model.
+The last result together with the large Poissonian observational error in the ACF explain the current difficulty to put tighter constrains in \lmmax\ in our model.
 
-\subsection{Constraining DMH mass with cosmic variance}
-In the left panel of Fig.
-\ref{fig:cosmicv} we show the number halo distribution (NHD) in the  mock fields of the simulation for different models $\mathcal{M}$.
+ In Fig.
+\ref{fig:mmed} the green vertical lines represent  the 16, 50 and 84 percentiles  of the posterior probability distribution of \mmin that we previously obtained.
+From this figure we find that the median dark matter halo mass is $\tilde{M}_{\rm h} = 10^{10.6^{+0.7}_{-0.6}$.
+This result is consistent with previous estimations of  the  median dark matter halo mass reported by  \citet{Bielby16} ($\tilde{M}_{\rm h} = 10^{11.0\pm0.6}$), \citet{Gawiser07} ($\tilde{M}_{\rm h} = 10^{10.9\pm0.9}$) and \citet{Ouchi2010} ($\tilde{M}_{\rm h} = 6.7^{+42.0}_{6.7}\times10^{10}}$) using semi-analitical approaches.
+
+\begin{figure}
+
+\includegraphics[width=0.47\textwidth]{corr.png}
+\caption{ Angular Correlation functions for $\log M_{\rm min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta M$. The error bars represent the 1 sigma deviation due to cosmic variance.}
+\label{fig:corr}
+\end{figure}
+
+\subsection{Constraining Dark matter halos mass  with cosmic variance}
+Fig.
+\ref{fig:cosmicv0}  shows the  halo number distribution (HND) in the  mock fields of the simulation for different models $\mathcal{M}$.
 By simple inspection one can infer an increase in the distribution with as \lmmin increase.
-This trend is confirmed in the right panel of Fig.
+This trend is confirmed in Fig.
 \ref{fig:cosmicv}  where we plot the central 1-$\sigma$ (blue diamonds) and 2-$\sigma$  (red dots) widths  of the NDH as a function of \lmmin.
-We particularly found that when we consider survey fields of $\sim1{\rm deg^2}$, the central  1-$\sigma$ (2-$\sigma$) width of the NHD increases monotonically from 0.05dex (0.10dex) when $\lmmin=9.5$ to 0.20dex (0.35dex) when $\lmmin=12.0$.
+We particularly found that when we consider survey fields of $\sim1{\rm deg^2}$, the central  1-$\sigma$ (2-$\sigma$) width of the HND increases monotonically from 0.05dex (0.10dex) when $\lmmin=9.5$ to 0.20dex (0.35dex) when $\lmmin=12.0$.
 The latter result opens the possibility to constrain the \lmmin (as well as the median mass) of LAEs by simply measure the width of the distribution of observed LAE along several observational fields mapping $\sim1{\rm deg^2}$ in area and the observational depth determined by the NB479 filter.
@@
 \begin{figure}
-\includegraphics[width=0.23\textwidth, height=0.19\textwidth]{ndist.png}
-\includegraphics[width=0.23\textwidth, height=0.19\textwidth]{mmin_dfocc1.png}
-\caption{Left: Halo number distribution  over the 54 mock field of the simulation for different models of $M_{\rm min}$-$M_{\rm max}$.Right:Width of the halo number distribution over the 54 mock field of the simulation ($\Delta \log \left( N_{\rm halos}/\tilde{N}_{\rm halos}\right)$) of the central 68 (blue diamonds) and  95(red circles)  percentiles vs $M_{\rm min}$.
+\includegraphics[width=0.46\textwidth, height=0.33\textwidth]{mmin_dfocc1.png}
+\caption{Width of the halo number distribution over the 54 mock field of the simulation ($\Delta \log \left( N_{\rm halos}/\tilde{N}_{\rm halos}\right)$) of the central 68 (blue diamonds) and  95(red circles)  percentiles vs $M_{\rm min}$.
 Points are color coded according to their associated value of $\Delta M \equiv M_{\rm min}-M_{\rm min}$.
-}
+The green line diagonal line accounts for the 1:1 relation and the green vertical lines represent  the 16, 50 and 84 percentiles  of the posterior probability distribution of \mmin.}
 \label{fig:cosmicv}
@@
 
-\bibliographystyle{mn2e}
+\section{Conclusions}
+
+In this letter we studied the impact of cosmic variance and observational uncertainties in constraining the mass range and  occupation fraction of dark matter halos hosting  LAEs.  
+To this end, we used the BolshoiP N-body simulation to construct  27 mock fields  with the same typical size  of observed fields at  $z=3.1$ ($\sim 1 {\rm deg^2}$).  
+In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm   max}$ can only host one detectable LAE at most. 
+We explored the parameter space determined by \mmin\ and \mmax\ using Monte Carlo Markov-Chain minimization to match the observed  ACF and mean number density of LAEs.
+
+Our analysis allowed us to put weak constraints on $M_{\rm min}$, $M_{\rm max}$ and $f_{\rm occ}$ where $10^{9.7}\hMsun\leq \log M_{\rm min}\leq 10^{11.2}\hMsun$, $10^{10.9}\hMsun\leq \log M_{\rm max}\leq 10^{13.0}\hMsun$ and $0.02\hMsun\leq f_{\rm occ}\leq 0.5$, spanning three orders of magnitude in halo mass.
+Previous works\citep{Hayashino2004, Gawiser07,Ouchi2008,Bielby16} have found typical masses within somehow narrower mass ranges ($\sim 10^{10.5}$-$10^{12}$).  
+The main reason for our weaker constraints and large discrepancies with previous works resides in the cosmic variance on the typical field size in observations. 
+A thorough exploration of cosmic variance impact as we present in this letter had not been presented so far in the literature.
+
+Our analysis also allowed us to draw three results that can be used to put tighter constraints on $M_{\rm min}$, $M_{\rm max}$ and $f_{\rm occ}$ once upcoming large LAE surveys, as the HETDEX project \citep{Hetdex2011} and the HSC ultra deep survey, are available :
+\begin{enumerate}
+\item $f_{\rm occ}$ and the median mass of LAEs are almost uniquely determined by $M_{\rm min}$ regardless of $M_{\rm max}$.
+\item measuring the width of the LAE number distribution function obtained over several fields of $\approx 1$ deg$^2$ one will be able to tightly constrain  $M_{\rm min}$, $M_{\rm med}$ and $f_{\rm occ}$ up to a factor of  2.
+\item  $M_{\rm max}$ drives the ACF strength at short angular distances ($<1\,\rm arcmin$), therefore precise measurements of the ACF at such scales are crucial to accurately determine \mmax.
+\end{enumerate}
+
+\section*{Acknowledgments}
+
+JM acknowledges ``CONICYT-PCHA/doctorado Nacional para extranjeros/2013-63130316'' for their PhD scholarship support.
+
+\bibliographystyle{apj}
 \bibliography{references.bib}

### 2016-03-20 paper/ms.tex
latex setup update

@@
 \documentclass{emulateapj}
-%\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e}
-
-%External Packages and personalized macros
-%=========================================================================
-%		EXTERNAL PACKAGES
-%=========================================================================
-%\usepackage{amsmath} 
-%\usepackage{amssymb} 
-%\usepackage[section]{placeins}
-
+\submitted{{\it Submitted for publication in ApJ}}
+\usepackage{multirow,color,wrapfig,ulem}
 \usepackage {graphicx}
-
-\usepackage{amsmath}
-\usepackage{amssymb}
 \usepackage{graphics}
-\usepackage{epsfig}
-\usepackage{float}
-\bibliographystyle{apj}
-
-\usepackage {graphicx}
-
-%\usepackage{graphics}
-%\usepackage[dvips]{epsfig}
-%\usepackage{epsfig}  
-\usepackage{color}
-\usepackage[normalem]{ulem}
-\usepackage{hyperref}
-\usepackage{caption}
-%Non reposionated tables
-%\usepackage{float}
-\restylefloat{table}
-%Multiple columns support for tables
-\usepackage{array}
-\usepackage{booktabs}
-\setlength{\heavyrulewidth}{1.5pt}
-\setlength{\abovetopsep}{4pt}
-\pdfminorversion=5
+\usepackage[dvips]{epsfig}
 
@@
 \newcommand{\zz}{$z\sim 3$} 
-%\newcommand{\apj}{ApJ}  
-%\newcommand{\apjs}{ApJS}  
-%\newcommand{\apjl}{ApJL}  
-%\newcommand{\aj}{AJ}  
-%\newcommand{\mnras}{MNRAS}  
-%\newcommand{\mnrassub}{MNRAS accepted}  
-%\newcommand{\aap}{A\&A}  
-%\newcommand{\aaps}{A\&AS}  
-%\newcommand{\araa}{ARA\&A}  
-%\newcommand{\nat}{Nature}  
-%\newcommand{\physrep}{PhR}
-%\newcommand{\pasp}{PASP}    
-%\newcommand{\pasj}{PASJ}    
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
@@
 %SAMPLES
-\newcommand{\GHBDM}{\texttt{GH}$_{\mbox{\tiny{BDM}}}$ }
-\newcommand{\GHFOF}{\texttt{GH}$_{\mbox{\tiny{FOF}}}$ }
-\newcommand{\IHBDM}{\texttt{IH}$_{\mbox{\tiny{BDM}}}$ }
-\newcommand{\IHFOF}{\texttt{IH}$_{\mbox{\tiny{FOF}}}$ }
-\newcommand{\PBDM}{\texttt{P}$_{\mbox{\tiny{BDM}}}$ }
-\newcommand{\PFOF}{\texttt{P}$_{\mbox{\tiny{FOF}}}$ }
-\newcommand{\IPBDM}{\texttt{IP}$_{\mbox{\tiny{BDM}}}$ }
-\newcommand{\IPFOF}{\texttt{IP}$_{\mbox{\tiny{FOF}}}$ }
-\newcommand{\RIPBDM}{\texttt{RIP}$_{\mbox{\tiny{BDM}}}$ }
-\newcommand{\RIPFOF}{\texttt{RIP}$_{\mbox{\tiny{FOF}}}$ }
 
@@
 \begin{document}
-
 %=========================================================================
@@
 We use a N-body simulation to construct mock catalogs with the same typical size  of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$) to match the observed  angular correlation function (ACF) and number density of LAEs.
-In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm   max}$ can only host one detectable LAE at most.
+In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\mathrm h}<M_{\rm   max}$ can only host one detectable LAE at most.
 By following a thorough Markov Chain Monte-Carlo exploration of the parameter space determined by $M_{\rm min}$ and $M_{\rm   max}$, our analysis shows that $f_{\rm occ}$ is uniquely determined by $M_{\rm min}$ regardless of $M_{\rm max}$ using the relation $\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$ .
@@
 
-Then we say that a halo will host a LAE with probability $f_{\rm occ}$ if and only if the halo mass is in the range $M_{\rm min}< M_{\rm h} < M_{\rm max}$.
-The probability $f_{\rm occ}$ can be thought as the occupation fraction of halos which can be automatically set as the ration of the observed number of LAEs to the number of halos within the considered mass range, that is $f_{\rm occ}\equiv N_{\rm LAE}/N_{\rm halos}$.
+Then we say that a halo will host a LAE with probability $f_{\rm occ}$ if and only if the halo mass is in the range $M_{\rm min}< M_{\mathrm h} < M_{\rm max}$.
+The probability $f_{\rm occ}$ can be thought as the occupation fraction of halos which can be automatically set as the ration of the observed number of LAEs to the number of halos within the considered mass range, that is $f_{\rm occ}\equiv N_{\rm LAE}/N_{\mathrm halos}$.
 
@@
 We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ to vary between  $9.2$ up to $13.4$, corresponding to the halo mass range of the simulation at $z=3$. 
-Given that the typical scatter  in $N_{\rm halos}$ is about 0.3 dex (i.e.
+Given that the typical scatter  in $N_{\mathrm halos}$ is about 0.3 dex (i.e.
 about  a factor of 2), our parameter space is restricted to models where the median number of dark matter halos is larger than  $N_{\rm LAE}/3$.
-The MCMC exploration is done using a total of 24 seeds and 400 iterations (9600 models) to sample the posterior PDF,  $P(\mmin, \mmax, f_{\rm occ}| \mathcal{M}) \propto \exp(-\chi_{\mathcal M}^2/2)$, with
+The MCMC exploration is done using a total of 24 seeds and 400
+iterations (9600 models) to sample the posterior PDF,  $P(\mmin,
+\mmax, f_{\rm occ}| \mathcal{M}) \propto \exp(-\chi_{\mathcal
+  M}^2/2)$, with
 
@@
 %
-where  $\rm{ACF}_{\mathcal M}$ and  $\rm{ACF}_{\rm obs}$ are the ACF of the explored model ${\mathcal M}$ and the observational ACF reported by \citet{Bielby16} respectively.
-$\sigma_{\rm \mathcal M}$ is the associated 1-$\sigma$ scatter
-of the $\rm{ACF}_{\mathcal M}$ as a product of cosmic variance and $\sigma_{\rm obs}$ is the observational error associated to $\rm{ACF}_{\rm obs}$.
-The $\rm{ACF}_{\mathcal M}$s are computed using  the Landy \&  Szalay estimator  \citep{Landy1993}.
+where  $\rm{ACF}_{\mathcal M}$ and  $\rm{ACF}_{\rm obs}$ are the ACF
+of the explored model ${\mathcal M}$ and the observational ACF
+reported by \citet{Bielby16} respectively. $\sigma_{\rm \mathcal M}$
+is the associated 1-$\sigma$ scatter  of the $\rm{ACF}_{\mathcal M}$
+as a product of cosmic variance and  $\sigma_{\rm obs}$ is the
+observational error associated to $\rm{ACF}_{\rm obs}$.  The
+$\rm{ACF}_{\mathcal M}$s are computed using the Landy \&  Szalay
+estimator  \citep{Landy1993}.
 
@@
 
-In Fig.
-\ref{fig:like} we present yhe one and two dimensional projections of the posterior probability distributions of \mmin, \mmax and \focc.
-We find that the \mmin and \mmax parameter space cannot be tightly constrained mainly because of cosmic variance and the large observational Poisonnian uncertainty in the ACF.
-We however found that 9.6$<\log \mmin<$11.0 and 10.9$<\log\mmax<$13.0.
-We interestingly find that \focc\ is basically completely determined by \mmin  going from \focc$=$0.015 when $\log\mmin=$9.6 to \focc$=$0.30 when $\log\mmin=$11.0  ($\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$).
-We remark that those models where $\log \focc>0.00$ ($\focc>1$) correspond
-to models where the number density  of halos is smaller than the number of observed LAEs but are
-still consistent because of the uncertainty in the median number density of LAEs in the universe due to cosmic variance (see Fig.
-\ref{fig:cosmicv0}).%in the number of dark matter halos along the mock fields
+In Fig. \ref{fig:like} we present yhe one and two dimensional
+projections of the posterior probability distributions of \mmin, \mmax
+and \focc. We find that the \mmin and \mmax parameter space cannot be
+tightly constrained mainly because of cosmic variance and the large
+observational Poisonnian uncertainty in the ACF. We however found that
+9.6$<\log \mmin<$11.0 and 10.9$<\log\mmax<$13.0.   We interestingly
+find that \focc\ is basically completely determined by \mmin  going
+from \focc$=$0.015 when $\log\mmin=$9.6 to \focc$=$0.30 when
+$\log\mmin=$11.0
+($\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$). We remark that
+those models where $\log \focc>0.00$ ($\focc>1$) correspond  to models where the number density  of halos is smaller than the number of observed LAEs but are
+still consistent because of the uncertainty in the median number
+density of LAEs in the universe due to cosmic variance (see
+Fig. \ref{fig:cosmicv0}).%in the number of dark matter halos along the
+                         %mock fields
 
@@
 \includegraphics[width=0.47\textwidth]{mmin_mmed_colordm.png}
-\caption{ $\log M_{\rm min}$ vs $\log M_{\rm 50\%}$ (black), $\log M_{\rm 16\%}$-$\log M_{\rm 84\%}$ (blue) and  $\log M_{\rm 2.5\%}$-$\log M_{\rm 97.5\%}$(red) for different values of $\log M_{\rm max}$.
-The points are color coded by $\Delta \log M\left[\rm{M_{\odot}h^{-1} ]}\right]$.
-The green line diagonal line accounts for the 1:1 relation and the green vertical lines represent  the 16, 50 and 84 percentiles  of the posterior probability distribution of \mmin.}
+\caption{ $\log M_{\rm min}$ vs $\log M_{\rm 50\%}$ (black), $\log
+  M_{\rm 16\%}$-$\log M_{\rm 84\%}$ (blue) and  $\log M_{\rm
+    2.5\%}$-$\log M_{\rm 97.5\%}$(red) for different values of $\log
+  M_{\rm max}$. The points are color coded by $\Delta \log
+  M\left[\rm{M_{\odot}h^{-1} ]}\right]$. The green line diagonal line
+accounts for the 1:1 relation and the green vertical lines represent
+the 16, 50 and 84 percentiles  of the posterior probability
+distribution of \mmin.} 
 \label{fig:mmed}
@@
 
-Previous  attempts to constrain the DMH mass of LAEs by means of the ACF   present their result in terms of the median mass of LAEs that is derived from the derived correlation length by means of semi-analitical prescriptions  \citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}.
-Instead, in this work we directly compare the ACF of our simulated mock catalogs with the observational ACF and present our results in terms of a  minimum and maximum mass DMH hosting LAEs.
-It is therefore necessary to connect our approach by computing the median mass of the DMH in each of the models $\mathcal{M}$.
-In   Fig.
-\ref{fig:mmed} we show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue diamonds) and 95 ($\log M_{95}$, red squares) percentiles of the LAE halo mass as a function of \lmmin\ for each of the models that we run in our MCMC simulation.
-The points are color coded according to their \dlm\ associated value.
-We can see that the median mass ($M_{50}$) and $M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially when $\dlm\gtrsim1.0$dex.
-We particularly found that  $\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that $\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$ regardless of the value of \dlm.
-The latter is a consequence of the very steepen distribution of the dark matter mass function  and is at the same time the reason for the almost perfect one to one relation between \mmin\ and \focc.
-However, it can also be seen in Fig.
-\ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax ($\lmmin+0.2\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+1.5\rm{dex}$).
-Thereby, any differences in the clustering strength of models sharing the same \mmin but different \mmax should be mainly driven by the  $\sim16\%$ most massive  halos of each model $\mathcal{M}$.
+Previous  attempts to constrain the DMH mass of LAEs by means of the
+ACF   present their result in terms of the median mass of LAEs that is
+derived from the derived correlation length by means of
+semi-analitical prescriptions
+\citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. Instead,
+in this work we directly compare the ACF of our simulated mock
+catalogs with the observational ACF and present our results in terms
+of a  minimum and maximum mass DMH hosting LAEs. It is therefore
+necessary to connect our approach by computing the median mass of the
+DMH in each of the models $\mathcal{M}$.  In   Fig. \ref{fig:mmed} we
+show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue
+diamonds) and 95 ($\log M_{95}$, red squares) percentiles of the LAE
+halo mass as a function of \lmmin\ for each of the models that we run
+in our MCMC simulation.  The points are color coded according to their
+\dlm\ associated value. We can see that the median mass ($M_{50}$) and
+$M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially
+when $\dlm\gtrsim1.0$dex. We particularly found that
+$\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that
+$\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$
+regardless of the value of \dlm. The latter is a consequence of the
+very steepen distribution of the dark matter mass function  and is at
+the same time the reason for the almost perfect one to one relation
+between \mmin\ and \focc. However, it can also be seen in
+Fig. \ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax
+($\lmmin+0.2\rm{dex}\lesssim\log
+M_{50}\lesssim\lmmin+1.5\rm{dex}$). Thereby, any differences in the
+clustering strength of models sharing the same \mmin but different
+\mmax should be mainly driven by the  $\sim16\%$ most massive  halos
+of each model $\mathcal{M}$.
 
-In order to estimate the effect of most massive halos in  $ACF_{\mathcal{M}}$ in Fig.
-\ref{fig:corr} we show the computed $ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values of $\dlm$.
-We can see that the clustering gets stronger for larger values of \dlm.
-Nevertheless, due to the large impact of cosmic variance at the volume of the current observations all the models  are basically consistent within errors.
-The last result together with the large Poissonian observational error in the ACF explain the current difficulty to put tighter constrains in \lmmax\ in our model.
+In order to estimate the effect of most massive halos in
+$ACF_{\mathcal{M}}$ in Fig. \ref{fig:corr} we show the computed
+$ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values
+of $\dlm$. We can see that the clustering gets stronger for larger
+values of \dlm. Nevertheless, due to the large impact of cosmic
+variance at the volume of the current observations all the models  are
+basically consistent within errors. The last result together with the
+large Poissonian observational error in the ACF explain the current
+difficulty to put tighter constrains in \lmmax\ in our model.
 
- In Fig.
-\ref{fig:mmed} the green vertical lines represent  the 16, 50 and 84 percentiles  of the posterior probability distribution of \mmin that we previously obtained.
-From this figure we find that the median dark matter halo mass is $\tilde{M}_{\rm h} = 10^{10.6^{+0.7}_{-0.6}$.
-This result is consistent with previous estimations of  the  median dark matter halo mass reported by  \citet{Bielby16} ($\tilde{M}_{\rm h} = 10^{11.0\pm0.6}$), \citet{Gawiser07} ($\tilde{M}_{\rm h} = 10^{10.9\pm0.9}$) and \citet{Ouchi2010} ($\tilde{M}_{\rm h} = 6.7^{+42.0}_{6.7}\times10^{10}}$) using semi-analitical approaches.
+ In Fig. \ref{fig:mmed} the green vertical lines represent  the 16, 50
+ and 84 percentiles  of the posterior probability distribution of
+ \mmin that we previously obtained. From this figure we find that the
+ median dark matter halo mass is $\tilde{M}_{\mathrm h} =
+ 10^{10.6^{+0.7}_{-0.6}} $. 
+This result is consistent with previous
+ estimations of  the  median dark matter halo mass reported by
+ \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6}$),
+ \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
+ \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} =
+ 6.7^{+42.0}_{6.7}\times10^{10}$) using semi-analitical approaches.
 
@@
 \includegraphics[width=0.46\textwidth, height=0.33\textwidth]{mmin_dfocc1.png}
-\caption{Width of the halo number distribution over the 54 mock field of the simulation ($\Delta \log \left( N_{\rm halos}/\tilde{N}_{\rm halos}\right)$) of the central 68 (blue diamonds) and  95(red circles)  percentiles vs $M_{\rm min}$.
+\caption{Width of the halo number distribution over the 54 mock field of the simulation ($\Delta \log \left( N_{\mathrm halos}/\tilde{N}_{\mathrm halos}\right)$) of the central 68 (blue diamonds) and  95(red circles)  percentiles vs $M_{\rm min}$.
 Points are color coded according to their associated value of $\Delta M \equiv M_{\rm min}-M_{\rm min}$.
@@
 To this end, we used the BolshoiP N-body simulation to construct  27 mock fields  with the same typical size  of observed fields at  $z=3.1$ ($\sim 1 {\rm deg^2}$).  
-In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm   max}$ can only host one detectable LAE at most. 
+In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\mathrm h}<M_{\rm   max}$ can only host one detectable LAE at most. 
 We explored the parameter space determined by \mmin\ and \mmax\ using Monte Carlo Markov-Chain minimization to match the observed  ACF and mean number density of LAEs.

### 2016-03-20 code/LAE_likelyhood.py
codes data and output added

@@ -1,0 +1,783 @@
+#bin/#!/usrt/env python
+import numpy as np 
+import os
+#import matplotlib.pyplot as P
+#import correlation_lib as corr
+import sys
+import itertools
+import emcee
+import time
+from scipy.interpolate import interp1d
+from scipy.interpolate import InterpolatedUnivariateSpline as interpolation
+from scipy.integrate import simps as integral
+import matplotlib
+matplotlib.use('Agg')
+font = {'family' : 'normal',
+        'weight' : 'normal',
+        'size'   : 20}
+matplotlib.rc('font', **font)
+
+from pylab import *
+ioff()
+try:
+    os.mkdir('../output/')
+except: print '../output already exist. Not a problem'
+#tini=time.time()
+
+
+
+
+load_snap_file=1 #load the snapshot positions and massess. Default 0.
+indexes_subcat=1 #find the indexes for the subcatalogs. Default 1
+plot_ndist=1  # plot the number halo distrubition in the subacatalog. Default 0
+run_emcee=0
+compute_RR=0
+use_trans=1 # use transmission function to select LAEs
+ncatRR=1000
+fc=0.22 #Contamination fraction. 0 for no contamination.
+
+Acor=1.0/(1-fc)
+Acor=Acor*Acor # Amplutide correction factor of the ACF
+
+
+
+sufix='_1deg_fixed'
+niter=400 #number of times to iter emcee
+ndim=2 #number of parameters, 3 in this time: mmin,mma,focc.
+nwalkers=24 # number of independent walks
+ncores=24 #to optimize it should be set to nwalkers
+
+#The center and widths of the seeds for EMCEE 
+Mo=10.0 # 
+dmmin=1.0
+dmmax=1.0
+fo=0.5
+dfo=0.5
+
+#Below are the seeds to be passed to EMCEE, Here I generete them randomly using a gaussian distribution.
+
+mmin=Mo+dmmin*randn(nwalkers) 
+mmin=np.abs(mmin)
+dM=1.0*randn(nwalkers)
+dM=np.abs(dM)
+Focc=fo+dfo*randn(nwalkers)
+Focc=np.abs(Focc)    
+
+#initial seeds for the emcee walkers
+if ndim==3:
+    pos = [[mmin[i],dM[i],Focc[i]] for i in range(nwalkers)]
+if ndim==2:
+    pos = [[mmin[i],dM[i]] for i in range(nwalkers)]
[…]

### 2016-03-20 code/corner_plot.py

@@ -1,0 +1,168 @@
+from numpy import *
+import corner
+from matplotlib import *
+use('Agg')
+#import matplotlib
+
+from matplotlib.pyplot import *
+rcParams['ps.useafm'] = True
+rcParams['pdf.use14corefonts'] = True #Guarantee type 1 plots to 
+rcParams['text.usetex'] = True #Very important to force python to recognize Latex
+rcParams['legend.numpoints']=1 
+font = {'family' : 'normal',
+        'weight' : 'normal',
+        'size'   : 20}
+rc('font', **font)
+
+
+parspace=genfromtxt('../output/LAEBayes_mcmc_dM_1deg_fixed.out')
+parprob=genfromtxt('../output/LAEBayes_mcmc_dM_chi_1deg_fixed.out')
+parall=genfromtxt('../output/focc_1deg_fixed.txt')
+parspace[:,1]+=parspace[:,0]
+
+
+parprob=parprob/2.0
+
+fc=0.22
+Ac=1.0/(1.0-fc)
+Ac=Ac*Ac
+
+
+arg_ini=200
+fig = corner.corner(parspace[arg_ini:],weights=exp(parprob[arg_ini:]),bins=20, smooth=0.6, labels=[r"$\log M_{\rm min}\left[\rm{M_{\odot}h^{-1}}\right]$", r"$\log M_{\rm max}\left[\rm{M_{\odot}h^{-1}}\right]$"],quantiles=[0.16, 0.5, 0.84])
+fig.savefig('../output/likelyplot_1deg.png',  format='png', dpi=150,bbox_inches='tight')
+fig = corner.corner(transpose([parall[:,0][arg_ini:],(1-fc)*parall[:,2][arg_ini:]]),weight=exp(parprob)[ :len( parall[:,0] ) ][arg_ini:],bins=20, smooth=0.6, labels=[r"$\log M_{\rm min}\left[\rm{M_{\odot}h^{-1}}\right]$", r"$\log f_{\rm occ}$"],quantiles=[0.16, 0.5, 0.84])
+fig.savefig('../output/likelyplot_1degf.png', format='png', dpi=150,bbox_inches='tight')
[…]

### 2016-03-20 code/focc.py

@@ -1,0 +1,69 @@
+import numpy as np
+if 1:
+    posz,trans1=genfromtxt(trans_file,unpack=1)
+    zcentroid=integral(trans1*posz,posz)/integral(trans1,posz)
+    
+    mmin,dm=np.genfromtxt(fn,unpack=1)
+    likely=np.genfromtxt(fn1,unpack=1)
+    mmax=mmin+dm
+    
+    focc=np.zeros_like(mmax)
+    focc_up=np.zeros_like(mmax)
+    focc_low=np.zeros_like(mmax)
+    focc_up1=np.zeros_like(mmax)
+    focc_low1=np.zeros_like(mmax)
+
+    
+    mmed=np.zeros_like(mmax)
+    m_up=np.zeros_like(mmax)
+    m_low=np.zeros_like(mmax)
+    m_up1=np.zeros_like(mmax)
+    m_low1=np.zeros_like(mmax)
+
+
+    
+    for count1 in range(len(mmax)):
+        
+        count=0
+        
+        frac=np.zeros(nx*ny*nz)
+        mmedian=np.zeros(nx*ny*nz)
+        for i,j,k in itertools.product(range(nx),range(ny),range(nz)):
+            
+            
+            m1=mass[index[count]];z1=z[index[count]]
+            m1=np.log10(m1)
+            wmin=m1>mmin[count1]; wmax=m1<mmax[count1]
+            
+            wm=wmin*wmax
+            mm=m1[wm]
+            zm=z1[wm]
+            if len(mm)==0: continue
+            #print np.log10(Nlae_mean/(1.0*len(mm)))
+            prob=np.random.rand(len(zm))
+            zcenter=(z1.max()+z1.min())/2.0 - zcentroid 
+            posz1=posz+zcenter
+            trans_func = interp1d(posz1, trans1, kind='linear',bounds_error=False,fill_value=0)
+            pz=trans_func(zm)
+            wz=pz>prob
+            zapp=zm[wz]
+            frac[count]=np.log10(Nlae_mean/(1.0*len(zapp)))
+            count=count+1
+        if np.sum(frac)==0: continue 
+        focc[count1]=np.percentile(frac,50)
+        focc_low[count1]=np.percentile(frac,16)
+        focc_up[count1]=np.percentile(frac,84)
+        focc_low1[count1]=np.percentile(frac,2.5)
[…]

### 2016-03-21 paper/ms.tex
nueva version del plot 1

@@
 \begin{figure}
-\includegraphics[width=0.46\textwidth, height=0.38\textwidth]{ndist.png}
-\caption{Cumulative halo number distribution function over the 27 mock fields of the simulation for different models of $M_{\rm min}$-$M_{\rm max}$.}
+\includegraphics[width=0.50\textwidth]{fig1.pdf}
+\caption{Cumulative halo number density distribution function over
+  27 mock fields. Each line corresponds to a
+  different model with increasig values of $M_{\rm min}$. 
+  Different models produce different number density distributions. The
+width increases with \mmin.} 
 \label{fig:cosmicv0}
@@
 \begin{figure*}
-\includegraphics[width=0.99\textwidth]{likelyplot_1deg_total.png}
-%\includegraphics[width=0.47\textwidth]{likelyplot_1degf.png}
-%\includegraphics[width=0.47\textwidth]{likelyplot_1degdM.png}
-%\includegraphics[width=0.47\textwidth]{likelyplot_1degdMf.png}
-\caption{One and two dimensional projections of the posterior probability distributions of \mmin, \mmax and \focc as described in the label of each sub-figure.}
+\begin{center}
+\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
+\end{center}
+\caption{One and two dimensional projections of the posterior
+  probability distributions of \mmin, \mmax and \focc as described in
+  the label of each sub-figure.} 
 \label{fig:like}

### 2016-03-23 paper/ms.tex
updating tex file to clarify focc>1 and correting some typos

@@
 \caption{One and two dimensional projections of the posterior
-  probability distributions of \mmin, \mmax and \focc as described in
-  the label of each sub-figure.} 
+  probability distributions of \mmin, \mmax\ and \focc\ as described in
+  the label of each sub-figure. We remark that
+those models where $\log \focc>0.00$ ($\focc>1$) correspond  to models where the number density  of halos is smaller than the number of observed LAEs but are
+still consistent because of the uncertainty in the median number
+density of LAEs in the universe due to cosmic variance. See
+Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
 \label{fig:like}
@@
 at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA\ and a flux limit
-of $2\times10^17{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
+of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
 Using spectroscopy they found a 22\% contamination fraction.
@@
 $\sim$80$^2\hMpc^2$ in a comoving scale. \citet{Bielby16} used the
-NB497  narrow-band filter whose 77\AA FWHM and 154\AA FWTM correspond to a total observational depth of 44\hMpc  and 82\hMpc comoving, respectively.
+NB497  narrow-band filter whose 77\AA\ FWHM and 154\AA FWTM correspond to a total observational depth of 44\hMpc\  and 82\hMpc\ comoving, respectively.
 
@@
 halo in the box we extract its comoving position and mass. 
-We focus our work on halos more massive than $1.54\times 10^{9}$\hMsun resolved with at least  $10$ particles.
+We focus our work on halos more massive than $1.54\times 10^{9}$\hMsun\ resolved with at least  $10$ particles.
 %the reasons for this choice are explained in the next sub-section.
@@
 \subsection{Exploring and selecting consistent models}
-
+\label{subsec:explore}
 We use the angular correlation function to compare the observations with our mock catalogs. 
@@
 about  a factor of 2), our parameter space is restricted to models where the median number of dark matter halos is larger than  $N_{\rm LAE}/3$.
+Because of this posibility of having $N_{\mathrm halos}$  smaller than $N_{\rm LAE}$ there will be some models where    $\focc\equivN_{\rm LAE}/N_{\mathrm halo}>1$.
+Those models only reflect the uncertainty in the number density of LAEs due to cosmic variance.
+
 The MCMC exploration is done using a total of 24 seeds and 400
@@
 density of LAEs in the universe due to cosmic variance (see
-Fig. \ref{fig:cosmicv0}).%in the number of dark matter halos along the
+Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore}).%in the number of dark matter halos along the
                          %mock fields

### 2016-03-23 paper/ms.tex
little typo

@@
 $\sim$80$^2\hMpc^2$ in a comoving scale. \citet{Bielby16} used the
-NB497  narrow-band filter whose 77\AA\ FWHM and 154\AA FWTM correspond to a total observational depth of 44\hMpc\  and 82\hMpc\ comoving, respectively.
+NB497  narrow-band filter whose 77\AA\ FWHM and 154\AA\ FWTM correspond to a total observational depth of 44\hMpc\  and 82\hMpc\ comoving, respectively.
 

### 2016-03-23 paper/ms.tex
fixed latex typo

@@
 about  a factor of 2), our parameter space is restricted to models where the median number of dark matter halos is larger than  $N_{\rm LAE}/3$.
-Because of this posibility of having $N_{\mathrm halos}$  smaller than $N_{\rm LAE}$ there will be some models where    $\focc\equivN_{\rm LAE}/N_{\mathrm halo}>1$.
+Because of this posibility of having $N_{\mathrm halos}$  smaller than $N_{\rm LAE}$ there will be some models where    $\focc\equiv N_{\rm LAE}/N_{\rm halo}>1$.
 Those models only reflect the uncertainty in the number density of LAEs due to cosmic variance.

### 2016-03-30 paper/ms.tex
new caption for fig5
recent bolshoi references

@@
 \begin{figure}
-\includegraphics[width=0.50\textwidth]{fig1.pdf}
+\includegraphics[width=0.47\textwidth]{fig1.pdf}
 \caption{Cumulative halo number density distribution function over
@@
   Different models produce different number density distributions. The
-width increases with \mmin.} 
+width increases with \mmin. } 
 \label{fig:cosmicv0}
@@
 First, the observations we take as a benchmark. 
-Second, the N-body simulation and the halo catalogs we use to build the mocks.
-Third, the parameters describing our model to assign a LAE to a halo.
-Fourth, the statistical method we adopt to compare observations and simulations.
+Second, the N-body simulation and the halo catalogs we use to build
+the mocks. 
+Third, the parameters describing our model to
+assign a LAE to a halo. 
+Fourth, the statistical method we adopt to compare observations and
+simulations.  
 We describe in detail these four elements in the following subsections.
@@
 \caption{One and two dimensional projections of the posterior
-  probability distributions of \mmin, \mmax\ and \focc\ as described in
-  the label of each sub-figure. We remark that
-those models where $\log \focc>0.00$ ($\focc>1$) correspond  to models where the number density  of halos is smaller than the number of observed LAEs but are
-still consistent because of the uncertainty in the median number
-density of LAEs in the universe due to cosmic variance. See
+  probability distributions of \mmin, \mmax\ and \focc\. 
+  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
+  where the number density  of halos is smaller than the number of
+  observed LAEs but we consider them as consistent because of the uncertainty
+  in the median number density due to cosmic variance. See 
 Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
@@
 Using spectroscopy they found a 22\% contamination fraction.
-Their observations cover 5 (out of 9) independent and co-spatial fields of the VLT LBG Redshift Survey (VLRS). 
+Their observations cover 5 (out of 9) independent and co-spatial
+fields of the VLT LBG Redshift Survey (VLRS).  
 The  total observed  area corresponds to 1.07$\rm deg^2$ that translates to
-$\sim$80$^2\hMpc^2$ in a comoving scale. \citet{Bielby16} used the
-NB497  narrow-band filter whose 77\AA\ FWHM and 154\AA\ FWTM correspond to a total observational depth of 44\hMpc\  and 82\hMpc\ comoving, respectively.
-
-%JF
+$\sim$80$^2\hMpc^2$ in a comoving scale. 
+\citet{Bielby16} used the NB497  narrow-band filter whose 77\AA\ FWHM
+and 154\AA\ FWTM correspond to a total observational depth of
+44\hMpc\  and 82\hMpc\ comoving, respectively.
 
@@
 
-We use results from the  Bolshoi simulation \citep{Bolshoi} which was performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side.
-The dark matter distribution was sampled using  $2048^{3}$ particles.
-The cosmological parameters are consistent with Planck 2013 results \citep{Planck2014} with a matter density
+We use results from the Bolshoi simulation \citep{Bolshoi,BolshoiP} which was
+performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side. 
+The dark matter distribution was sampled using  $2048^{3}$
+particles. 
+The cosmological parameters are consistent with Planck
+results \citep{Planck2014} with a matter density 
 $\Omega_{\rm m} = 0.307$, cosmological constant
-$\Omega_{\Lambda}=0.693$, dimensionless Hubble constant $h=0.70$, slope
+$\Omega_{\Lambda}=0.693$, dimensionless Hubble constant $h=0.678$, slope
 of the power spectrum  $n=0.96$ and normalization of the power
-spectrum $\sigma_{8}=0.82$.  
-This translates into a particle mass of  $m_{\rm p}=1.54\times 10^{8}$ $h^{-1}$ M$_{\odot}$.
+spectrum $\sigma_{8}=0.823$.  
+This translates into a particle mass of  $m_{\rm p}=1.5\times 10^{8}$
+$h^{-1}$ M$_{\odot}$.
 
-We use halo catalogs constructed with a Bound-Density-Maxima (BDM) algorithm. The catalogs were obtained from the publicly available
-Multidark database  \footnote{{\tt
-    http://www.multidark.org/MultiDark/}} \citep{MultiDark}. For each
-halo in the box we extract its comoving position and mass. 
-We focus our work on halos more massive than $1.54\times 10^{9}$\hMsun\ resolved with at least  $10$ particles.
-%the reasons for this choice are explained in the next sub-section.
+We use halo catalogs constructed with a Bound-Density-Maxima (BDM)
+algorithm. 
+The catalogs were obtained from the publicly available Multidark
+database  \footnote{\url{http://www.multidark.org/MultiDark/}}
+\citep{MultiDark}. 
+For each  halo in the box we extract its comoving position and mass.  
+We focus our work on halos more massive than $1.5\times
+10^{9}$\hMsun\ resolved with at least  $10$ particles.
 
-We divide the total volume of the snapshot of the simulation at z$\sim$3
-into  27 smaller mock volumes mimicking the  comoving area and depth  
-reported in \citet{Bielby16} and described in \S \ref{subsec:obs}. 
-This allows  us to take explicitly into account the effects of cosmic variance.
+We split the simulation volume at z$\sim$3 into  27 smaller mock
+volumes mimicking the  area and depth reported in \citet{Bielby16} and
+described in \S \ref{subsec:obs}.
 
@@
 
-\includegraphics[width=0.47\textwidth]{corr.png}
-\caption{ Angular Correlation functions for $\log M_{\rm min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta M$. The error bars represent the 1 sigma deviation due to cosmic variance.}
+  \includegraphics[width=0.47\textwidth]{fig5.pdf}
+\caption{ Angular Correlation functions for $\log M_{\rm
+    min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta
+  M$.  
+  The shaded region represents the 1-sigma deviation due to cosmic
+  variance. Radical different models in $\Delta M$ are consistent with
+  observations once cosmic variance is modelled in detail.}
 \label{fig:corr}
@@
 
-JM acknowledges ``CONICYT-PCHA/doctorado Nacional para extranjeros/2013-63130316'' for their PhD scholarship support.
+JM acknowledges ``CONICYT-PCHA/doctorado Nacional para
+extranjeros/2013-63130316'' for their PhD scholarship support.
+
+The authors gratefully acknowledge the Gauss Centre for Supercomputing
+e.V. (\url{www.gauss-centre.eu}) and the Partnership for Advanced
+Supercomputing in Europe (PRACE, \url{www.prace-ri.eu}) for funding the
+MultiDark simulation project by providing computing time on the GCS
+Supercomputer SuperMUC at Leibniz Supercomputing Centre (LRZ,
+\url{www.lrz.de}). The Bolshoi simulations have been performed within the
+Bolshoi project of the University of California High-Performance
+AstroComputing Center (UC-HiPACC) and were run at the NASA Ames
+Research Center.
 

### 2016-03-30 paper/ms.tex
model description

@@
 10^{9}$\hMsun\ resolved with at least  $10$ particles. 
+We do not take into account sub-halos.
 
@@
 
-We build a model to assign LAEs to a DM halo. 
-We are not concerned on the exact LAE luminosity, we only care about a yes/no answer to the following question. Does this halo host a LAE?
+We build the simplest possible model to assign a LAE to each DM halo
+without trying to compute a LAE luminosity.
 
-We first assume that a dark matter halo can host one detectable LAE at most.  
-This assumption is consistent with theoretical analysis of the correlation function \citep{Jose2013b} and observations that confirm a lack of class pairs in LAEs \cite{Bond2009}.
+We first assume that a dark matter halo can host one detectable LAE at
+most.   
+This assumption is consistent with theoretical analysis of the
+correlation function \citep{Jose2013b} and observations that confirm a
+lack of class pairs in LAEs \cite{Bond2009}.  
+Then we say that a halo will host a LAE with probability $\focc$
+if and only if the halo mass is in the range $\mmin < M_{\mathrm
+  h} < \mmax$. 
+In what follows we refer to a given set of values $\focc$, $\mmin$,
+$\mmax$ as a model, $\mathcal{M}$. We also use a variable \dm to represent
+the mass range width, $\dm\equiv\ \log \mmax - \log \mmax$.
 
-Then we say that a halo will host a LAE with probability $f_{\rm occ}$ if and only if the halo mass is in the range $M_{\rm min}< M_{\mathrm h} < M_{\rm max}$.
-The probability $f_{\rm occ}$ can be thought as the occupation fraction of halos which can be automatically set as the ration of the observed number of LAEs to the number of halos within the considered mass range, that is $f_{\rm occ}\equiv N_{\rm LAE}/N_{\mathrm halos}$.
+The parameter $\focc$ can be thought as the LAE occupation fraction of
+dark matter halos.
+An astrophysical interpretation of $f_{\rm occ}$ convolves at least
+three phenomena: the actual presence of a star forming galaxy in a
+halo, the escape fraction of \ly\ radiation and its detectability as
+a LAE.   
+We do not try to disentangle these complex phenomena.
+We instead opt for an arithmentic interpretation by setting $\focc$ as
+the ratio between the observed number of LAEs and the number of halos
+within the considered mass range, that is $\focc \equiv N_{\rm
+  LAEs}/N_{\mathrm{halos}}$.
 
-Fig.
-\ref{fig:cosmicv0}  shows the cumulative halo number distribution (HND) in the  mock fields of the simulation for different models $\mathcal{M}$.
-From this figure we can see that the number of dark matter halos along the mock fields for different models $\mathcal{M}$ varies within a factor of $\sim 2$ ($\sim 0.3$dex) tracing the cosmic variance.
-As a consequence, the occupation fraction varies along  the mock fields  by the same factor factor.
-The interpretation of the occupation fraction $f_{\rm occ}$ involves two phenomena: the actual presence of a star forming galaxy in a halo and its detectability as a LAE.
+Fig. \ref{fig:cosmicv0}  shows the cumulative halo number density
+for all 27 subvolumes in the simulation, with a normalization by the
+average number density among fields. 
+Each line represents a different model $\mathcal{M}$ with fixed
+$\focc=1$ and $\dm=1.0$; and varying $\mmin$, 
+This Figure shows that the halo number density varies across
+sub-volumes, as an expression of cosmic variance. 
+As a consequence, the $\focc$ also varies across the mock fields  
+by the same factor factor.
 

### 2016-03-30 paper/ms.tex
finished revision section 1

@@
   h} < \mmax$. 
-In what follows we refer to a given set of values $\focc$, $\mmin$,
-$\mmax$ as a model, $\mathcal{M}$. We also use a variable \dm to represent
-the mass range width, $\dm\equiv\ \log \mmax - \log \mmax$.
+We also use the variable \dm to represent the mass range width,
+$\dm\equiv\ \log \mmax - \log \mmax$.
 
@@
 We do not try to disentangle these complex phenomena.
-We instead opt for an arithmentic interpretation by setting $\focc$ as
+We instead opt for an arithmetic interpretation by setting $\focc$ as
 the ratio between the observed number of LAEs and the number of halos
@@
   LAEs}/N_{\mathrm{halos}}$.
+
+For each mock catalog we also randomly remove $22\%$ LAEs to mimic the
+effect of contamination in observations \citet{Bielby16}.
+On top of that we apply rejection sampling  to our LAE selection
+taking the transmission function of the NB479 filter used in their
+observations as a radial selection factor.
 
@@
 
-We do not explore any physical model to disentangle these two effects. This means that our model does not assign a luminosity or escape fraction to each
-LAE.
-We avoid this in order to maintain theoretical uncertainties to a minimum. 
-This flexibility allows us to explore a wide range of possible masses for
-the host halos without any strong theoretical prejudice regarding the
-details of star formation and \ly\  escape fraction.
-
-We also artificially contaminate our mock catalogs with 22$\%$ randomly distributed data points to mimic the fraction of interlopers in observations \citet{Bielby16} .
-On top of that we apply rejection sampling  to our LAE selection taking the transmission function of the NB479 filter used in their observations as a radial selection factor.
-
 In what follows we note by the letter ${\mathcal M}$ a model
 defined by a particular choice of the two parameters $M_{\rm min}$, 
-$M_{\rm  max}$. For each model  ${\mathcal M}$ we define $\tilde{f}_{\rm occ}$ as the median occupation fraction within the the mock fields and  $\Delta M \equiv \mmax-\mmin$.
+$M_{\rm  max}$. For each model  ${\mathcal M}$ we define
+$\tilde{f}_{\rm occ}$ as the median occupation fraction within the the
+mock fields.
 
@@
 \label{subsec:explore}
-We use the angular correlation function to compare the observations with our mock catalogs. 
-This is done trough a thorough exploration of the parameter space of the models ${\mathcal M}$ by  means of a Monte Carlo Markov Chain minimization using  the EMCEE python package \citep{emcee2013}.
-We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ to vary between $9.2$ up to $13.4$, corresponding to the halo mass range of the simulation at $z=3$. 
-Given that the typical scatter  in $N_{\mathrm halos}$ is about 0.3 dex (i.e.
-about  a factor of 2), our parameter space is restricted to models where the median number of dark matter halos is larger than  $N_{\rm LAE}/3$.
-Because of this posibility of having $N_{\mathrm halos}$  smaller than $N_{\rm LAE}$ there will be some models where    $\focc\equiv N_{\rm LAE}/N_{\rm halo}>1$.
-Those models only reflect the uncertainty in the number density of LAEs due to cosmic variance.
+
+We make a thorough parameter space exploration of the models
+${\mathcal M}$ by  means of a Markov Chain Monte Carlo technique using
+the EMCEE python package \citep{emcee2013}.
+
+We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
+$9.2$ up to $13.4$, corresponding to the halo mass range of 
+the simulation at $z=3$.  
+We restrict the selection to models that give a minimal number denity $N_{\rm{halos}}>N_{\rm
+  LAE}/3$.  
+This means that it is possible to have $N_{\rm
+  {halos}} < N_{\rm LAE}$ and hence $\focc\equiv N_{\rm LAE}/N_{\rm
+  halo}>1$.  
+This only reflects the uncertainty in the number 
+density of LAEs due to cosmic variance.
 
 The MCMC exploration is done using a total of 24 seeds and 400
-iterations (9600 models) to sample the posterior PDF,  $P(\mmin,
-\mmax, f_{\rm occ}| \mathcal{M}) \propto \exp(-\chi_{\mathcal
-  M}^2/2)$, with
+iterations (9600 models) to sample the posterior PDF,
+$P(\mathcal{M}|\mathrm{observations}) \propto \exp(-\chi_{\mathcal
+  M}^2/2)$, with the $\chi_{\mathcal{M}}^2$ based on the Angular
+Correlation Function (ACF),
 
 \begin{equation}
-\chi_{\mathcal M}^2=\sum_{\theta}\left[\frac{\left( \rm{ACF}_{\mathcal M}\left(\theta\right) - \rm{ACF}_{\rm obs}\left(\theta\right)\right)^2}{ \sigma_{\rm \mathcal M}^{2}\left(\theta\right) + \sigma_{\rm obs}^{2}\left(\theta\right)}\right]
+\chi_{\mathcal M}^2=
+\sum_{\theta}\left[\frac{\left( \rm{ACF}_{\mathcal
+      M}\left(\theta\right) - \rm{ACF}_{\rm
+      obs}\left(\theta\right)\right)^2}{ \sigma_{\rm \mathcal
+      M}^{2}\left(\theta\right) + \sigma_{\rm
+      obs}^{2}\left(\theta\right)}\right] 
 \end{equation}
@@
 of the explored model ${\mathcal M}$ and the observational ACF
-reported by \citet{Bielby16} respectively. $\sigma_{\rm \mathcal M}$
-is the associated 1-$\sigma$ scatter  of the $\rm{ACF}_{\mathcal M}$
-as a product of cosmic variance and  $\sigma_{\rm obs}$ is the
-observational error associated to $\rm{ACF}_{\rm obs}$.  The
-$\rm{ACF}_{\mathcal M}$s are computed using the Landy \&  Szalay
+reported by \citet{Bielby16} respectively. 
+$\sigma_{\rm \mathcal M}$ is the associated 1-$\sigma$ scatter  of the
+$\rm{ACF}_{\mathcal M}$ as a product of cosmic variance and
+$\sigma_{\rm obs}$ is the observational error associated to
+$\rm{ACF}_{\rm obs}$.   
+We compute the $\rm{ACF}_{\mathcal M}$ using the Landy \&  Szalay
 estimator  \citep{Landy1993}.

### 2016-03-30 paper/ms.tex
revisando results + discussion

@@
 
-% JF - 1. Intro 3/10
-% JF - 2. Methodology 1/7
-
 %*************************************************************************
@@
 of subjects in extragalactic astronomy. 
-LAEs can be used as probes of reionization \citep{Dijkstra11}, tracers of large scale structure \citep{Koehler2007},  signposts for low metallicity stellar populations, markers of the galaxy formation process at high redshift \citep{Dayal2009,ForeroRomero2012} and tracers of active star formation \citep{Guaita2013}.
+LAEs can be used as probes of reionization \citep{Dijkstra11}, tracers
+of large scale structure \citep{Koehler2007},  signposts for low
+metallicity stellar populations, markers of the galaxy formation
+process at high redshift \citep{Dayal2009,ForeroRomero2012} and
+tracers of active star formation \citep{Guaita2013}.
 
-In most of those cases, capitalizing the observations requires  understanding how LAEs are formed within an explicit cosmological context. 
-Under the current structure formation paradigm the dominant matter content of the Universe is dark matter (DM). 
-Each galaxy is thought to be hosted by a larger dark matter structure known as a halo. \citep{Peebles1980,SpringelNature05}. 
-Understanding the cosmological context of LAEs thus implies studying the galaxy-halo connection. 
+In most of those cases, capitalizing the observations requires
+understanding how LAEs are formed within an explicit cosmological
+context.  
+Under the current structure formation paradigm the dominant matter
+content of the Universe is dark matter (DM).  
+Each galaxy is thought to be hosted by a larger dark matter structure
+known as a halo. \citep{Peebles1980,SpringelNature05}.  
+Understanding the cosmological context of LAEs thus implies studying
+the galaxy-halo connection.  
 Galaxy formation models suggest that the physical processes that regulate the star formation cycle are dependent on halo mass \citep{Behroozi2013a}.
@@
 In the case of LAEs there are different ways to find this mass range.
-One approach is theoretical, using general astrophysical principles to find the relationship between halo mass, intrinsic \ly\ luminosities and observed \ly\ luminosities.
-This approach is usually implemented through semi-analytic models \citep{Garel2012,Orsi2012} and  full N-body hydrodynamical simulations \citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012}.
+One approach is theoretical, using general astrophysical principles to
+find the relationship between halo mass, intrinsic \ly\ luminosities
+and observed \ly\ luminosities. This approach is usually implemented
+through semi-analytic models \citep{Garel2012,Orsi2012} and  full
+N-body hydrodynamical simulations \citep{Laursen2007, Dayal2009,
+  ForeroRomero2011, Yajima2012}.
 
-%JF
-
-The downside of these calculations is the uncertainty in the estimation of the escape fraction of \ly\ photons.
-Given the resonant nature of the \ly\ line, the escape fraction is sensitive to  the dust contents, density, temperature, topology and kinematics of the neutral Hydrogen in the interstellar medium (ISM).
-The process of finding a consensus on the expected value
-for the \ly\ escape fraction in high redshift galaxies is still matter
-of open debate
+The downside of these calculations is the uncertainty in the
+estimation of the escape fraction of \ly\ photons. Given the resonant
+nature of the \ly\ line, the escape fraction is sensitive to  the dust
+contents, density, temperature, topology and kinematics of the neutral
+Hydrogen in the interstellar medium (ISM). The process of finding a
+consensus on the expected value for the \ly\ escape fraction in high
+redshift galaxies is still matter of open debate
 \citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.
@@
 In these studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
-the conclusions derived on the halo host mass do not elaborate on the uncertainty resulting from the cosmic variance on these fields.
+the conclusions derived on the halo host mass do not elaborate on the
+uncertainty resulting from the cosmic variance on these fields.
 
@@
 constraining the mass and occupation fraction of halos hosting LAEs at $z=3$.
-We build mock surveys from a cosmological N-body to compare them against the observations in \cite{Bielby16} using the angular correlation function. 
+We build mock surveys from a cosmological N-body to compare them
+against the observations in \cite{Bielby16} using the angular
+correlation function.  
 We use a simple model to populate a halo in the simulation with a LAE   
-assuming a minimum (\mmin) and maximum mass (\mmax) for the dark matter halos hosting LAEs without predicting a \ly\  luminosity. 
-This approach bypasses all the physical uncertainties associated to star formation and radiative transfer.
-We use the Markov Chain Monte Carlo technique to obtain the likelihood of the parameters given the observational constraints.
+assuming a minimum (\mmin) and maximum mass (\mmax) for the dark
+matter halos hosting LAEs without predicting a \ly\  luminosity.  
+This approach bypasses all the physical uncertainties associated to
+star formation and radiative transfer. 
+We use the Markov Chain Monte Carlo technique to obtain the likelihood
+of the parameters given the observational constraints.
 
@@
 
-\subsection{A model to populate halos with LAEs}
+\subsection{A simple LAE model}
 \label{subsec:mocks}
@@
 
-\subsection{Exploring and selecting consistent models}
+\subsection{Model Selection}
 \label{subsec:explore}
@@
 the simulation at $z=3$.  
-We restrict the selection to models that give a minimal number denity $N_{\rm{halos}}>N_{\rm
-  LAE}/3$.  
-This means that it is possible to have $N_{\rm
-  {halos}} < N_{\rm LAE}$ and hence $\focc\equiv N_{\rm LAE}/N_{\rm
-  halo}>1$.  
+We restrict the selection to models that give a minimal number density 
+$N_{\rm{halos}}>N_{\rm LAE}/3$.   
+This means that it is possible to have $N_{\rm{halos}} < N_{\rm LAE}$
+and hence $\focc\equiv N_{\rm{LAE}}/N_{\rm{halos}}>1$.   
 This only reflects the uncertainty in the number 
@@
 \section{Results and Discussion}
+\label{sec:results}
 
-\subsection{Constraining \mmin, \mmax\ and \focc\ in Dark Matter Halos hosting LAEs}
+\subsection{Constraints on Model Parameters}
 
-In Fig. \ref{fig:like} we present yhe one and two dimensional
-projections of the posterior probability distributions of \mmin, \mmax
-and \focc. We find that the \mmin and \mmax parameter space cannot be
-tightly constrained mainly because of cosmic variance and the large
-observational Poisonnian uncertainty in the ACF. We however found that
-9.6$<\log \mmin<$11.0 and 10.9$<\log\mmax<$13.0.   We interestingly
-find that \focc\ is basically completely determined by \mmin  going
-from \focc$=$0.015 when $\log\mmin=$9.6 to \focc$=$0.30 when
-$\log\mmin=$11.0
-($\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$). We remark that
-those models where $\log \focc>0.00$ ($\focc>1$) correspond  to models where the number density  of halos is smaller than the number of observed LAEs but are
-still consistent because of the uncertainty in the median number
-density of LAEs in the universe due to cosmic variance (see
-Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore}).%in the number of dark matter halos along the
-                         %mock fields
+Fig. \ref{fig:like} shows the one and two dimensional projections of
+the posterior probability distributions of the parameters in our LAE model. 
+This Figure represents our main result: \mmin, \mmax\  and \focc\ cannot
+be tightly constrained from the available observations.
+
+The preferred $1-\sigma$ range for the masses is $9.6<\log \mmin<11.0$
+and $10.9<\log\mmax<13.0$.
+\focc\ is completely determined by \mmin\ from \focc$=$0.015 when
+$\log\mmin=9.6$ to $\focc=0.30$ when $\log\mmin=11.0$. 
+We compute the power-law dependece between \focc\ and \mmin\ to be 
+\begin{equation}
+\focc = 0.1\left(\frac{\mmin}{10^{10.5}\hMsun}\right)^{0.93}.
+\end{equation}
+We remind to the reader that models whith $\log \focc>0.00$ ($\focc>1$)
+correspond to cases where the halo number density is smaller 
+than the number of observed LAEs but are  still consistent because of
+the uncertainty in the median number density of LAEs in the universe
+due to cosmic variance (see Fig. \ref{fig:cosmicv0} and
+\S\ref{subsec:explore}).
 
@@
 
-\subsection{Halo mass distribution within models}
+\subsection{Median Halo Mass Within Models}
 
-Previous  attempts to constrain the DMH mass of LAEs by means of the
-ACF   present their result in terms of the median mass of LAEs that is
-derived from the derived correlation length by means of
-semi-analitical prescriptions
-\citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. Instead,
-in this work we directly compare the ACF of our simulated mock
-catalogs with the observational ACF and present our results in terms
-of a  minimum and maximum mass DMH hosting LAEs. It is therefore
-necessary to connect our approach by computing the median mass of the
-DMH in each of the models $\mathcal{M}$.  In   Fig. \ref{fig:mmed} we
+We now compute the median mass, $\log M_{50}$, of the LAE hosting halos for each model
+$\mathcal{M}$; $\log M_{50}$ allows a direct comparison between our
+results and previous results in the literature
+\citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} that used
+a more simplified approach.
+
+In   Fig. \ref{fig:mmed} we
 show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue

### 2016-03-30 paper/ms.tex
nuevo orden en las figuras

@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
-\end{center}
-\caption{One and two dimensional projections of the posterior
-  probability distributions of \mmin, \mmax\ and \focc\. 
-  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
-  where the number density  of halos is smaller than the number of
-  observed LAEs but we consider them as consistent because of the uncertainty
-  in the median number density due to cosmic variance. See 
-Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
-\label{fig:like}
-\end{figure*}
-
 \subsection{Observational constraints}
@@
 
+\begin{figure}
+  \includegraphics[width=0.47\textwidth]{fig5.pdf}
+\caption{ Angular Correlation functions for $\log M_{\rm
+    min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta
+  M$.  
+  The shaded region in the models represents the $1-\sigma$ variation
+  due to cosmic variance. Radical different models in $\Delta M$ are consistent with
+  observations once cosmic variance is modelled in detail.} 
+\label{fig:corr}
+\end{figure}
+
 We make a thorough parameter space exploration of the models
@@
 estimator  \citep{Landy1993}.
+
+Fig. \ref{fig:corr} shows the observational ACF by
+\citet{Bielby16} compared to the ACF in three different models with a
+wide range in $\dm$.  
+This already shows that radically different models can be compatible
+with observations once cosmic variance uncertainties are modelled in
+detail.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
+\end{center}
+\caption{One and two dimensional projections of the posterior
+  probability distributions of \mmin, \mmax\ and \focc\. 
+  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
+  where the number density  of halos is smaller than the number of
+  observed LAEs but we consider them as consistent because of the uncertainty
+  in the median number density due to cosmic variance. See 
+Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
+\label{fig:like}
+\end{figure*}
 
@@
 
-\begin{figure}
-
-  \includegraphics[width=0.47\textwidth]{fig5.pdf}
-\caption{ Angular Correlation functions for $\log M_{\rm
-    min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta
-  M$.  
-  The shaded region represents the 1-sigma deviation due to cosmic
-  variance. Radical different models in $\Delta M$ are consistent with
-  observations once cosmic variance is modelled in detail.}
-\label{fig:corr}
-\end{figure}
-
 \subsection{Constraining Dark matter halos mass  with cosmic variance}

### 2016-03-30 paper/ms.tex
rewriting

@@
 and hence $\focc\equiv N_{\rm{LAE}}/N_{\rm{halos}}>1$.   
-This only reflects the uncertainty in the number 
-density of LAEs due to cosmic variance.
+We include the $1/3$ factor to account for the uncertainty in the number 
+density of LAEs due to cosmic variance, expecting it to be on the
+same order as the dark matter halo cosmic variance shown in
+Fig. \ref{fig:cosmicv0}.
 
@@
 
-\subsection{Median Halo Mass Within Models}
+\subsection{Median Halo Mass and Halo Mass Width within Models}
 
-We now compute the median mass, $\log M_{50}$, of the LAE hosting halos for each model
-$\mathcal{M}$; $\log M_{50}$ allows a direct comparison between our
+We now compute the median mass, $\log M_{50}$, and the $1\sigma$ halo mass
+width, $\Delta M_{1\sigma} \equiv \log M_{84} - \log M_{16}$, of the LAE hosting halos for each model
+$\mathcal{M}$ (here $M_{p}$ represents the $p$ percentile of the mass distribution);
+$\log M_{50}$ and $M_{1\sigma}$ allow a direct comparison between our
 results and previous results in the literature
@@
 
-In   Fig. \ref{fig:mmed} we
-show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue
-diamonds) and 95 ($\log M_{95}$, red squares) percentiles of the LAE
-halo mass as a function of \lmmin\ for each of the models that we run
-in our MCMC simulation.  The points are color coded according to their
+In Fig. \ref{fig:mmed} we show the $\log M_{50}$-$\Delta M_{1\sigma}$
+plane for the models selected in the $1\sigma$ posterior region for
+\mmin. The color encodes the $\mmin$ value.
+
+The points are color coded according to their
 \dlm\ associated value. We can see that the median mass ($M_{50}$) and

### 2016-03-30 code/corner_plot.py
adding a comment to focc_1deg_fixed.txt to specify to order or columns

@@ -17,7 +17,7 @@ rc('font', **font)
 
 parspace=genfromtxt('../output/LAEBayes_mcmc_dM_1deg_fixed.out')
 parprob=genfromtxt('../output/LAEBayes_mcmc_dM_chi_1deg_fixed.out')
-parall=genfromtxt('../output/focc_1deg_fixed.txt')
+parall=genfromtxt('../output/focc_1deg_fixed.txt',sxiprows=1)
 parspace[:,1]+=parspace[:,0]
 
 

### 2016-04-02 paper/ms.tex
updated ms with new plot
caption figure 4

@@
 \end{equation}
-We remind to the reader that models whith $\log \focc>0.00$ ($\focc>1$)
+We remind the reader that models whith $\log \focc>0.00$ ($\focc>1$)
 correspond to cases where the halo number density is smaller 
-than the number of observed LAEs but are  still consistent because of
-the uncertainty in the median number density of LAEs in the universe
-due to cosmic variance (see Fig. \ref{fig:cosmicv0} and
+than the number of observed LAEs but are  still considered consistent
+because of the expected uncertainty in the median number density of
+LAEs due to cosmic variance (see Fig. \ref{fig:cosmicv0} and
 \S\ref{subsec:explore}).
@@
 \begin{figure}
-\includegraphics[width=0.47\textwidth]{mmin_mmed_colordm.png}
-\caption{ $\log M_{\rm min}$ vs $\log M_{\rm 50\%}$ (black), $\log
-  M_{\rm 16\%}$-$\log M_{\rm 84\%}$ (blue) and  $\log M_{\rm
-    2.5\%}$-$\log M_{\rm 97.5\%}$(red) for different values of $\log
-  M_{\rm max}$. The points are color coded by $\Delta \log
-  M\left[\rm{M_{\odot}h^{-1} ]}\right]$. The green line diagonal line
-accounts for the 1:1 relation and the green vertical lines represent
-the 16, 50 and 84 percentiles  of the posterior probability
-distribution of \mmin.} 
+\includegraphics[width=0.47\textwidth]{fig4.pdf}
+\caption{Median mass, $\log M_{50}$, and mass width $\Delta
+  M_{1\sigma}=\log M_{84} - \log M_{16}$, for all models with low
+  $\chi^2_{\mathcal{M}}/2 < 1.0$. The median mass spans two orders of
+  magnitude with a mean value around $10^{10.5}$\hMsun. The
+  width has a median of $0.3$ dex (a factor of $2$ in
+  mass) with a maximum value of $0.7$ dex (a factor of 5). This means
+  that all models consistent with observations have a very narrow
+  range in halo mass where the LAEs are expected to be hosted.} 
 \label{fig:mmed}

### 2016-04-04 paper/ms.tex
updated paragraphs in discussion about median and widths

@@
 \begin{abstract}
-We study the impact of cosmic variance and observational uncertainties in constraining the mass and  occupation fraction ($f_{\rm occ}$) of dark matter halos hosting \ly\ Emitting  Galaxies at high redshift (LAEs).
+We study the impact of cosmic variance and observational uncertainties
+in constraining the mass and  occupation fraction ($f_{\rm occ}$) of
+dark matter halos hosting \ly\ Emitting  Galaxies at high redshift
+(LAEs). 
 We use a N-body simulation to construct mock catalogs with the same typical size  of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$) to match the observed  angular correlation function (ACF) and number density of LAEs.
@@
 
+\begin{figure}
+  \includegraphics[width=0.47\textwidth]{fig5.pdf}
+\caption{ Angular Correlation functions for $\log M_{\rm
+    min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta
+  M$.  
+  The shaded region in the models represents the $1-\sigma$ variation
+  due to cosmic variance. Radical different models in $\Delta M$ are consistent with
+  observations once cosmic variance is modelled in detail.} 
+\label{fig:corr}
+\end{figure}
+
 \subsection{Simulation and halo catalog}
@@
 described in \S \ref{subsec:obs}.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
+\end{center}
+\caption{One and two dimensional projections of the posterior
+  probability distributions of \mmin, \mmax\ and \focc\. 
+  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
+  where the number density  of halos is smaller than the number of
+  observed LAEs but we consider them as consistent because of the uncertainty
+  in the median number density due to cosmic variance. See 
+Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
+\label{fig:like}
+\end{figure*}
 
@@
 
-\begin{figure}
-  \includegraphics[width=0.47\textwidth]{fig5.pdf}
-\caption{ Angular Correlation functions for $\log M_{\rm
-    min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta
-  M$.  
-  The shaded region in the models represents the $1-\sigma$ variation
-  due to cosmic variance. Radical different models in $\Delta M$ are consistent with
-  observations once cosmic variance is modelled in detail.} 
-\label{fig:corr}
-\end{figure}
-
 We make a thorough parameter space exploration of the models
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
-\end{center}
-\caption{One and two dimensional projections of the posterior
-  probability distributions of \mmin, \mmax\ and \focc\. 
-  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
-  where the number density  of halos is smaller than the number of
-  observed LAEs but we consider them as consistent because of the uncertainty
-  in the median number density due to cosmic variance. See 
-Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
-\label{fig:like}
-\end{figure*}
-
 \section{Results and Discussion}
@@
   magnitude with a mean value around $10^{10.5}$\hMsun. The
-  width has a median of $0.3$ dex (a factor of $2$ in
-  mass) with a maximum value of $0.7$ dex (a factor of 5). This means
-  that all models consistent with observations have a very narrow
-  range in halo mass where the LAEs are expected to be hosted.} 
+  mass width $\Delta M_{1\sigma}$ has a median of $0.3$ dex (a factor
+  of $2$ in mass) with a maximum value of $0.7$ dex (a factor of
+  5). This means that all models consistent with observations have a
+  very narrow range in halo mass.}
 \label{fig:mmed}
@@
 We now compute the median mass, $\log M_{50}$, and the $1\sigma$ halo mass
-width, $\Delta M_{1\sigma} \equiv \log M_{84} - \log M_{16}$, of the LAE hosting halos for each model
-$\mathcal{M}$ (here $M_{p}$ represents the $p$ percentile of the mass distribution);
-$\log M_{50}$ and $M_{1\sigma}$ allow a direct comparison between our
-results and previous results in the literature
+width, $\Delta M_{1\sigma} \equiv \log M_{84} - \log M_{16}$, of the
+LAE hosting halos for each model  $\mathcal{M}$ (here $M_{p}$
+represents the $p$ percentile of the mass distribution); $\log M_{50}$
+and $M_{1\sigma}$ allow a direct comparison between our results and
+previous results in the literature
 \citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} that used
@@
 In Fig. \ref{fig:mmed} we show the $\log M_{50}$-$\Delta M_{1\sigma}$
-plane for the models selected in the $1\sigma$ posterior region for
-\mmin. The color encodes the $\mmin$ value.
+plane for the models selected to have $\chi^{2}_{\mathcal{M}}/2 < 1$,
+which roughly correspond to the $1\sigma$ region in the posterior
+distribution for the model parameters. The color encodes the
+$\chi^{2}_{\mathcal{M}}/2$ value. The median mass has a wide distribution
+spanning two orders of magnitude.
 
-The points are color coded according to their
-\dlm\ associated value. We can see that the median mass ($M_{50}$) and
-$M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially
-when $\dlm\gtrsim1.0$dex. We particularly found that
-$\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that
-$\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$
-regardless of the value of \dlm. The latter is a consequence of the
-very steepen distribution of the dark matter mass function  and is at
-the same time the reason for the almost perfect one to one relation
-between \mmin\ and \focc. However, it can also be seen in
-Fig. \ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax
-($\lmmin+0.2\rm{dex}\lesssim\log
-M_{50}\lesssim\lmmin+1.5\rm{dex}$). Thereby, any differences in the
-clustering strength of models sharing the same \mmin but different
-\mmax should be mainly driven by the  $\sim16\%$ most massive  halos
-of each model $\mathcal{M}$.
+From this distribution we obtain $\log M_{50} = 10.5\pm 0.6$ or
+equivalently $M_{50} = 3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.  
+The $1\sigma$ uncertainty for this median value is estimated from the
+$16$ and $84$ percentile values in the $\log M_{50}$ distribution.  
+This result is consistent with previous
+ estimations of  the  median dark matter halo mass reported by
+ \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6}$),
+ \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
+ \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} =
+ 6.7^{+42.0}_{6.7}\times10^{10}$) using semi-analitical approaches.
 
-In order to estimate the effect of most massive halos in
-$ACF_{\mathcal{M}}$ in Fig. \ref{fig:corr} we show the computed
+However, the same Figure \ref{fig:mmed} shows something interesting
+that semi-analytical approaches were not able to predict.
+The mass width, $\Delta M{1\sigma}$, that is the width of the mass
+distribution for a given model with fixed $\mmin$ and $\mmax$, has a
+median value and $1\sigma$ uncertainty of $\Delta M{1\sigma} =
+0.55^{+0.11}_{-0.31}$ dex.
+This means that the mass range for halos hosting LAEs is very narrow,
+there is only a factor of $2$ to $4$ between the lower and upper mass
+boundary.
+
+In summary, the median mass could be anything in the range
+$10^{9.5}$\hMsun and $10^{11.5}$, but the width is highly constrained
+to be between $0.2$ and $0.6$ dex.
+
+In Fig. \ref{fig:corr} we show the computed
 $ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values
@@
 difficulty to put tighter constrains in \lmmax\ in our model.
-
- In Fig. \ref{fig:mmed} the green vertical lines represent  the 16, 50
- and 84 percentiles  of the posterior probability distribution of
- \mmin that we previously obtained. From this figure we find that the
- median dark matter halo mass is $\tilde{M}_{\mathrm h} =
- 10^{10.6^{+0.7}_{-0.6}} $. 
-This result is consistent with previous
- estimations of  the  median dark matter halo mass reported by
- \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6}$),
- \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
- \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} =
- 6.7^{+42.0}_{6.7}\times10^{10}$) using semi-analitical approaches.
 

### 2016-04-06 paper/ms.tex
minor edits in discussion

@@
   M_{1\sigma}=\log M_{84} - \log M_{16}$, for all models with low
-  $\chi^2_{\mathcal{M}}/2 < 1.0$. The median mass spans two orders of
-  magnitude with a mean value around $10^{10.5}$\hMsun. The
-  mass width $\Delta M_{1\sigma}$ has a median of $0.3$ dex (a factor
+  $\chi^2_{\mathcal{M}}/2 < 1.0$. 
+  The median mass spans two orders of magnitude with a mean value
+  around $10^{10.5}$\hMsun.   
+  The mass width $\Delta M_{1\sigma}$ has a median of $0.3$ dex (a factor
   of $2$ in mass) with a maximum value of $0.7$ dex (a factor of
@@
 
-However, the same Figure \ref{fig:mmed} shows something interesting
+However, the same Figure \ref{fig:mmed} shows something 
 that semi-analytical approaches were not able to predict.
-The mass width, $\Delta M{1\sigma}$, that is the width of the mass
+The mass width, $\Delta M_{1\sigma}$, that is the width of the mass
 distribution for a given model with fixed $\mmin$ and $\mmax$, has a
-median value and $1\sigma$ uncertainty of $\Delta M{1\sigma} =
+median value and $1\sigma$ uncertainty of $\Delta M_{1\sigma} =
 0.55^{+0.11}_{-0.31}$ dex.
-This means that the mass range for halos hosting LAEs is very narrow,
-there is only a factor of $2$ to $4$ between the lower and upper mass
+This means that the mass range for halos hosting LAEs is very narrow.
+There is only a factor of $2$ to $4$ between the lower and upper mass
 boundary.
 
-In summary, the median mass could be anything in the range
-$10^{9.5}$\hMsun and $10^{11.5}$, but the width is highly constrained
-to be between $0.2$ and $0.6$ dex.
+Summarizing, the median mass could be anything in the range
+$10^{9.5}$\hMsun and $10^{11.5}$ (a $2.0$ dex range), but the width is
+highly constrained to be between $0.2$ and $0.6$ dex.
 

### 2016-04-06 paper/ms.tex
correcting a small typo

@@
 Summarizing, the median mass could be anything in the range
-$10^{9.5}$\hMsun and $10^{11.5}$ (a $2.0$ dex range), but the width is
+$10^{9.5}$\hMsun\ and $10^{11.5}$\hMsun\ (a $2.0$ dex range), but the width is
 highly constrained to be between $0.2$ and $0.6$ dex.

### 2016-04-18 paper/ms.tex
manuscript with cosmic variance plots
new caption in last figure

@@
 \subsection{Constraining Dark matter halos mass  with cosmic variance}
-Fig.
-\ref{fig:cosmicv0}  shows the  halo number distribution (HND) in the  mock fields of the simulation for different models $\mathcal{M}$.
-By simple inspection one can infer an increase in the distribution with as \lmmin increase.
-This trend is confirmed in Fig.
-\ref{fig:cosmicv}  where we plot the central 1-$\sigma$ (blue diamonds) and 2-$\sigma$  (red dots) widths  of the NDH as a function of \lmmin.
-We particularly found that when we consider survey fields of $\sim1{\rm deg^2}$, the central  1-$\sigma$ (2-$\sigma$) width of the HND increases monotonically from 0.05dex (0.10dex) when $\lmmin=9.5$ to 0.20dex (0.35dex) when $\lmmin=12.0$.
-The latter result opens the possibility to constrain the \lmmin (as well as the median mass) of LAEs by simply measure the width of the distribution of observed LAE along several observational fields mapping $\sim1{\rm deg^2}$ in area and the observational depth determined by the NB479 filter.
+Fig. \ref{fig:cosmicv0}  shows the  halo number distribution (HND) in
+the  mock fields of the simulation for different models
+$\mathcal{M}$. By simple inspection one can infer an increase in the
+distribution with as \lmmin increase.  This trend is confirmed in
+Fig. \ref{fig:cosmicv}  where we plot the central 1-$\sigma$ (blue
+diamonds) and 2-$\sigma$  (red dots) widths  of the NDH as a function
+of \lmmin. We particularly found that when we consider survey fields
+of $\sim1{\rm deg^2}$, the central  1-$\sigma$ (2-$\sigma$) width of
+the HND increases monotonically from 0.05dex (0.10dex) when
+$\lmmin=9.5$ to 0.20dex (0.35dex) when $\lmmin=12.0$. The latter
+result opens the possibility to constrain the \lmmin (as well as the
+median mass) of LAEs by simply measure the width of the distribution
+of observed LAE along several observational fields mapping $\sim1{\rm
+  deg^2}$ in area and the observational depth determined by the NB479
+filter.
 
@@
 \begin{figure}
-\includegraphics[width=0.46\textwidth, height=0.33\textwidth]{mmin_dfocc1.png}
-\caption{Width of the halo number distribution over the 54 mock field of the simulation ($\Delta \log \left( N_{\mathrm halos}/\tilde{N}_{\mathrm halos}\right)$) of the central 68 (blue diamonds) and  95(red circles)  percentiles vs $M_{\rm min}$.
-Points are color coded according to their associated value of $\Delta M \equiv M_{\rm min}-M_{\rm min}$.
-The green line diagonal line accounts for the 1:1 relation and the green vertical lines represent  the 16, 50 and 84 percentiles  of the posterior probability distribution of \mmin.}
-\label{fig:cosmicv}
+\includegraphics[width=0.49\textwidth]{fig6.pdf}
+\caption{$1\sigma$ width of the number density distribution over the
+  54 mock fields of the simulation as a function of \mmin. 
+  Only the models that have a good match with observations
+  ($\chi_{\mathcal M}/2 < 1$) are included.
+  The strong dependence of $n/ \langle n\rangle$ with \mmin was
+  parameterized as a power law with the parameters shown in the legend.
+\label{fig:cosmicv}}
 \end{figure}
@@
 
-In this letter we studied the impact of cosmic variance and observational uncertainties in constraining the mass range and  occupation fraction of dark matter halos hosting  LAEs.  
-To this end, we used the BolshoiP N-body simulation to construct  27 mock fields  with the same typical size  of observed fields at  $z=3.1$ ($\sim 1 {\rm deg^2}$).  
-In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\mathrm h}<M_{\rm   max}$ can only host one detectable LAE at most. 
-We explored the parameter space determined by \mmin\ and \mmax\ using Monte Carlo Markov-Chain minimization to match the observed  ACF and mean number density of LAEs.
+In this letter we studied the impact of cosmic variance and
+observational uncertainties in constraining the mass range and
+occupation fraction of dark matter halos hosting  LAEs.   
+To this end, we used the BolshoiP N-body simulation to construct  27
+mock fields  with the same typical size  of observed fields at
+$z=3.1$ ($\sim 1 {\rm deg^2}$).   
+In our model a dark matter halo with mass in the range $M_{\rm
+  min}<M_{\mathrm h}<M_{\rm   max}$ can only host one detectable LAE
+at most.  
+We explored the parameter space determined by \mmin\ and \mmax\ using
+Monte Carlo Markov-Chain minimization to match the observed  ACF and
+mean number density of LAEs.
 
-Our analysis allowed us to put weak constraints on $M_{\rm min}$, $M_{\rm max}$ and $f_{\rm occ}$ where $10^{9.7}\hMsun\leq \log M_{\rm min}\leq 10^{11.2}\hMsun$, $10^{10.9}\hMsun\leq \log M_{\rm max}\leq 10^{13.0}\hMsun$ and $0.02\hMsun\leq f_{\rm occ}\leq 0.5$, spanning three orders of magnitude in halo mass.
-Previous works\citep{Hayashino2004, Gawiser07,Ouchi2008,Bielby16} have found typical masses within somehow narrower mass ranges ($\sim 10^{10.5}$-$10^{12}$).  
-The main reason for our weaker constraints and large discrepancies with previous works resides in the cosmic variance on the typical field size in observations. 
-A thorough exploration of cosmic variance impact as we present in this letter had not been presented so far in the literature.
+Our analysis allowed us to put weak constraints on $M_{\rm min}$,
+$M_{\rm max}$ and $f_{\rm occ}$ where $10^{9.7}\hMsun\leq \log M_{\rm
+  min}\leq 10^{11.2}\hMsun$, $10^{10.9}\hMsun\leq \log M_{\rm max}\leq
+10^{13.0}\hMsun$ and $0.02\hMsun\leq f_{\rm occ}\leq 0.5$, spanning
+three orders of magnitude in halo mass. 
+Previous works\citep{Hayashino2004, Gawiser07,Ouchi2008,Bielby16} have
+found typical masses within somehow narrower mass ranges ($\sim
+10^{10.5}$-$10^{12}$).   
+The main reason for our weaker constraints and large discrepancies
+with previous works resides in the cosmic variance on the typical
+field size in observations.  
+A thorough exploration of cosmic variance impact as we present in this
+letter had not been presented so far in the literature.
 
-Our analysis also allowed us to draw three results that can be used to put tighter constraints on $M_{\rm min}$, $M_{\rm max}$ and $f_{\rm occ}$ once upcoming large LAE surveys, as the HETDEX project \citep{Hetdex2011} and the HSC ultra deep survey, are available :
+Our analysis also allowed us to draw three results that can be used to
+put tighter constraints on $M_{\rm min}$, $M_{\rm max}$ and $f_{\rm
+  occ}$ once upcoming large LAE surveys, as the HETDEX project
+\citep{Hetdex2011} and the HSC ultra deep survey, are available : 
 \begin{enumerate}
-\item $f_{\rm occ}$ and the median mass of LAEs are almost uniquely determined by $M_{\rm min}$ regardless of $M_{\rm max}$.
-\item measuring the width of the LAE number distribution function obtained over several fields of $\approx 1$ deg$^2$ one will be able to tightly constrain  $M_{\rm min}$, $M_{\rm med}$ and $f_{\rm occ}$ up to a factor of  2.
-\item  $M_{\rm max}$ drives the ACF strength at short angular distances ($<1\,\rm arcmin$), therefore precise measurements of the ACF at such scales are crucial to accurately determine \mmax.
+\item $f_{\rm occ}$ and the median mass of LAEs are almost uniquely
+  determined by $M_{\rm min}$ regardless of $M_{\rm max}$. \item
+  measuring the width of the LAE number distribution function obtained
+  over several fields of $\approx 1$ deg$^2$ one will be able to
+  tightly constrain  $M_{\rm min}$, $M_{\rm med}$ and $f_{\rm occ}$ up
+  to a factor of  2.  
+\item  $M_{\rm max}$ drives the ACF strength at short angular
+  distances ($<1\,\rm arcmin$), therefore precise measurements of the
+  ACF at such scales are crucial to accurately determine \mmax. 
 \end{enumerate}

### 2016-04-20 paper/ms.tex
including part of Valentinos comments

@@
 in constraining the mass and  occupation fraction ($f_{\rm occ}$) of
-dark matter halos hosting \ly\ Emitting  Galaxies at high redshift
-(LAEs). 
+dark matter halos hosting \ly\ Emitting  Galaxies ((LAEs) at high redshift. 
 We use a N-body simulation to construct mock catalogs with the same typical size  of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$) to match the observed  angular correlation function (ACF) and number density of LAEs.
 In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\mathrm h}<M_{\rm   max}$ can only host one detectable LAE at most.
-By following a thorough Markov Chain Monte-Carlo exploration of the parameter space determined by $M_{\rm min}$ and $M_{\rm   max}$, our analysis shows that $f_{\rm occ}$ is uniquely determined by $M_{\rm min}$ regardless of $M_{\rm max}$ using the relation $\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$ .
-However, the current observational data only allows us to put weak constraints on $M_{\rm min}$, $M_{\rm max}$ and consequently on $f_{\rm occ}$. 
+By following a Markov Chain Monte-Carlo exploration of the parameter space determined by $M_{\rm min}$ and $M_{\rm   max}$, our analysis shows that $f_{\rm occ}$ is uniquely determined by $M_{\rm min}$ regardless of $M_{\rm max}$ using the relation $\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$ .
+However, the current observational data only allows us to put weak constraints on $M_{\rm min}$ and consequently on $f_{\rm occ}$.
 Particularly, we find that $10^{9.6}\hMsun\leq M_{\rm min}\leq 10^{11.0}\hMsun$ , $10^{10.9}\hMsun\leq M_{\rm max}\leq 10^{13.0}\hMsun$ and $0.02\leq f_{\rm occ}\leq 0.30$.
-Nevertheless, we also find that  the upcoming large surveys can help to put tighter constraints on $M_{\rm min}$ and $f_{\rm occ}$ through the width measurement of the LAE number distribution function obtained over several fields of the same size of current observations.
+Nevertheless, we also find that  the upcoming large surveys can help to put tighter constraints on $M_{\rm min}$ and $f_{\rm occ}$ through the width of the distribution  of the	  LAE number density obtained over several fields of the same size of current observations.
 Analogously, the  improvement in the precision of the measured ACF will assist in constraining $M_{\rm max}$.
@@
 the galaxy-halo connection.  
-Galaxy formation models suggest that the physical processes that regulate the star formation cycle are dependent on halo mass \citep{Behroozi2013a}.
+Galaxy formation models suggest that the physical processes that regulate the star formation cycle are dependent on halo mass \citep[e.g.][]{Behroozi2013a}.
 The mass becomes the most important element in the halo-galaxy connection.
@@
 constraining the mass and occupation fraction of halos hosting LAEs at $z=3$.
-We build mock surveys from a cosmological N-body to compare them
-against the observations in \cite{Bielby16} using the angular
+We build mock surveys from a cosmological N-body simulation to compare them
+against the observations of \cite{Bielby16} using the angular
 correlation function.  
@@
   Different models produce different number density distributions. The
-width increases with \mmin. } 
+width of the distribution increases with \mmin. } 
 \label{fig:cosmicv0}
@@
 Using spectroscopy they found a 22\% contamination fraction.
-Their observations cover 5 (out of 9) independent and co-spatial
+Their observations cover 5 (out of 9) independent and adjacent
 fields of the VLT LBG Redshift Survey (VLRS).  
@@
 \citet{Bielby16} used the NB497  narrow-band filter whose 77\AA\ FWHM
-and 154\AA\ FWTM correspond to a total observational depth of
+and 154\AA\ Full width  tenth maximum (FWTM) correspond to a total observational depth of
 44\hMpc\  and 82\hMpc\ comoving, respectively.
@@
 \caption{ Angular Correlation functions for $\log M_{\rm
-    min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta
+    min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta \log
   M$.  
   The shaded region in the models represents the $1-\sigma$ variation
-  due to cosmic variance. Radical different models in $\Delta M$ are consistent with
+  due to cosmic variance. Radically different models in $\Delta \log M$ are consistent with
   observations once cosmic variance is modelled in detail.} 
@@
   h} < \mmax$. 
-We also use the variable \dm to represent the mass range width,
-$\dm\equiv\ \log \mmax - \log \mmax$.
+We also use the variable \dlm to represent the mass range width,
+$\dlm\equiv\ \log \mmax - \log \mmax$.
 
@@
 
-For each mock catalog we also randomly remove $22\%$ LAEs to mimic the
-effect of contamination in observations \citet{Bielby16}.
+For each mock catalog we also randomly remove $22\%$ of the mock-LAEs and replace 
+them with randomly distrubuted point to mimic the
+effect of contamination in \citet{Bielby16} observations.
 On top of that we apply rejection sampling  to our LAE selection 
-taking the transmission function of the NB479 filter used in their
-observations as a radial selection factor.
+along the radial direction
+taking the transmission function of the NB479 filter used in \citet{Bielby16}
+observations.
 
@@
 Each line represents a different model $\mathcal{M}$ with fixed
-$\focc=1$ and $\dm=1.0$; and varying $\mmin$, 
+$\focc=1$ and $\dlm=1.0$; and varying $\mmin$, 
 This Figure shows that the halo number density varies across
@@
 \citet{Bielby16} compared to the ACF in three different models with a
-wide range in $\dm$.  
+wide range in $\dlm$.  
 This already shows that radically different models can be compatible
@@
 \includegraphics[width=0.47\textwidth]{fig4.pdf}
-\caption{Median mass, $\log M_{50}$, and mass width $\Delta
+\caption{Median mass, $\log M_{50}$, and mass width $\Delta \log
   M_{1\sigma}=\log M_{84} - \log M_{16}$, for all models with low
@@
   around $10^{10.5}$\hMsun.   
-  The mass width $\Delta M_{1\sigma}$ has a median of $0.3$ dex (a factor
+  The mass width $\Delta \log M_{1\sigma}$ has a median of $0.3$ dex (a factor
   of $2$ in mass) with a maximum value of $0.7$ dex (a factor of
@@
 We now compute the median mass, $\log M_{50}$, and the $1\sigma$ halo mass
-width, $\Delta M_{1\sigma} \equiv \log M_{84} - \log M_{16}$, of the
+width, $\Delta \log M_{1\sigma} \equiv \log M_{84} - \log M_{16}$, of the
 LAE hosting halos for each model  $\mathcal{M}$ (here $M_{p}$
@@
 
-In Fig. \ref{fig:mmed} we show the $\log M_{50}$-$\Delta M_{1\sigma}$
+In Fig. \ref{fig:mmed} we show the $\log M_{50}$-$\Delta \log M_{1\sigma}$
 plane for the models selected to have $\chi^{2}_{\mathcal{M}}/2 < 1$,
@@
 that semi-analytical approaches were not able to predict.
-The mass width, $\Delta M_{1\sigma}$, that is the width of the mass
+The mass width, $\Delta \log M_{1\sigma}$, that is the width of the mass
 distribution for a given model with fixed $\mmin$ and $\mmax$, has a
-median value and $1\sigma$ uncertainty of $\Delta M_{1\sigma} =
+median value and $1\sigma$ uncertainty of $\Delta \log M_{1\sigma} =
 0.55^{+0.11}_{-0.31}$ dex.

### 2016-04-20 paper/ms.tex
abstract rewritten

@@
 We study the impact of cosmic variance and observational uncertainties
-in constraining the mass and  occupation fraction ($f_{\rm occ}$) of
-dark matter halos hosting \ly\ Emitting  Galaxies ((LAEs) at high redshift. 
-We use a N-body simulation to construct mock catalogs with the same typical size  of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$) to match the observed  angular correlation function (ACF) and number density of LAEs.
-In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\mathrm h}<M_{\rm   max}$ can only host one detectable LAE at most.
-By following a Markov Chain Monte-Carlo exploration of the parameter space determined by $M_{\rm min}$ and $M_{\rm   max}$, our analysis shows that $f_{\rm occ}$ is uniquely determined by $M_{\rm min}$ regardless of $M_{\rm max}$ using the relation $\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$ .
-However, the current observational data only allows us to put weak constraints on $M_{\rm min}$ and consequently on $f_{\rm occ}$.
-Particularly, we find that $10^{9.6}\hMsun\leq M_{\rm min}\leq 10^{11.0}\hMsun$ , $10^{10.9}\hMsun\leq M_{\rm max}\leq 10^{13.0}\hMsun$ and $0.02\leq f_{\rm occ}\leq 0.30$.
-Nevertheless, we also find that  the upcoming large surveys can help to put tighter constraints on $M_{\rm min}$ and $f_{\rm occ}$ through the width of the distribution  of the	  LAE number density obtained over several fields of the same size of current observations.
-Analogously, the  improvement in the precision of the measured ACF will assist in constraining $M_{\rm max}$.
+in constraining the mass and occupation fraction, \focc, of
+dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
+We construct mock catalogs from an N-body simulation to match the 
+typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
+In our model a dark matter halo with mass in the range $\mmin
+<M_{\mathrm h}<\mmax$ can only host one detectable LAEat most.    
+We explore the parameter space determined by \mmin, \mmax\ and \focc\
+with a Markov Chain Monte-Carlo algorithm using as observational
+constraints the angular correlation function (ACF) and the LAEs number density. 
+We find that the preferred minium and maximum masses in our model span
+a wide range $10^{9.6}\hMsun\leq \mmin \leq 10^{11.0}\hMsun$ ,
+$10^{10.9}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
+wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
+As a consequence the median mass, $M_{50}$, of all models consistent with
+observations has a large uncertainty $M_{50} =
+3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun, in agreement with the most recent
+observational estimates.
+However, we find that the same individual models have a relatively tight
+mass gap, $\Delta M \equiv \log_{10}\mmax - \log_{10}\mmin$, of $\Delta
+M\approx 0.3$dex.
+We are also able show that \focc\ is uniquely determined by $M_{\rm
+  min}$, regardless of $M_{\rm max}$, by
+$\focc\sim0.1(\mmin/10^{10.5}\hMsun )^{0.93}$.  
+However, the current observational data only allows us to put weak
+constraints on \mmin\ and consequently on \focc.
+We show that upcoming large surveys covering at least $50$ deg$^{2}$
+will be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
+distribution width, $W_{1\sigma}$, constructed over several fields of
+$\sim 1$ deg$^{2}$ using the relationship, $W_{1\sigma} =
+0.138\times (\mmin/10^{11}\hMsun )^{0.177}$, calibrated from our results.
 \end{abstract}

### 2016-04-20 paper/ms.tex
conclusions

@@
 constraints on \mmin\ and consequently on \focc.
-We show that upcoming large surveys covering at least $50$ deg$^{2}$
-will be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
+We argue that upcoming large surveys covering at least $25$ deg$^{2}$
+should be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
 distribution width, $W_{1\sigma}$, constructed over several fields of
@@
 
-The parameter $\focc$ can be thought as the LAE occupation fraction of
-dark matter halos.
 An astrophysical interpretation of $f_{\rm occ}$ convolves at least
-three phenomena: the actual presence of a star forming galaxy in a
-halo, the escape fraction of \ly\ radiation and its detectability as
-a LAE.   
-We do not try to disentangle these complex phenomena.
-We instead opt for an arithmetic interpretation by setting $\focc$ as
-the ratio between the observed number of LAEs and the number of halos
-within the considered mass range, that is $\focc \equiv N_{\rm
+four phenomena: the actual presence of a star forming galaxy in a
+halo, a duty cycle in the star formation rate, the escape fraction of
+\ly\ radiation and its detectability as a LAE.   
+We do not try to disentangle these effects.
+We instead opt for a purely arithmetic interpretation by setting
+$\focc$ as the ratio between the observed number of LAEs and the
+number of halos within the considered mass range, that is $\focc \equiv N_{\rm
   LAEs}/N_{\mathrm{halos}}$.
@@
 For each mock catalog we also randomly remove $22\%$ of the mock-LAEs and replace 
-them with randomly distrubuted point to mimic the
-effect of contamination in \citet{Bielby16} observations.
+them with randomly distrubuted points to mimic the effect of
+contamination in \citet{Bielby16} observations. 
 On top of that we apply rejection sampling  to our LAE selection 
-along the radial direction
-taking the transmission function of the NB479 filter used in \citet{Bielby16}
-observations.
+along the radial direction taking the transmission function of the
+NB479 filter used in \citet{Bielby16} observations.
 
@@
 occupation fraction of dark matter halos hosting  LAEs.   
-To this end, we used the BolshoiP N-body simulation to construct  27
-mock fields  with the same typical size  of observed fields at
-$z=3.1$ ($\sim 1 {\rm deg^2}$).   
+To this end we used the BolshoiP N-body simulation to construct  27 mock fields
+with the same typical size  of observed fields at $z=3.1$ ($\sim 1
+{\rm deg^2}$).      
 In our model a dark matter halo with mass in the range $M_{\rm
@@
 mean number density of LAEs.    
+It is the first time that such a thorough exploration of the cosmic
+variance impact on LAEs statistics is presented in the literature.
 
-Our analysis allowed us to put weak constraints on $M_{\rm min}$,
-$M_{\rm max}$ and $f_{\rm occ}$ where $10^{9.7}\hMsun\leq \log M_{\rm
-  min}\leq 10^{11.2}\hMsun$, $10^{10.9}\hMsun\leq \log M_{\rm max}\leq
-10^{13.0}\hMsun$ and $0.02\hMsun\leq f_{\rm occ}\leq 0.5$, spanning
-three orders of magnitude in halo mass. 
-Previous works\citep{Hayashino2004, Gawiser07,Ouchi2008,Bielby16} have
-found typical masses within somehow narrower mass ranges ($\sim
-10^{10.5}$-$10^{12}$).   
-The main reason for our weaker constraints and large discrepancies
-with previous works resides in the cosmic variance on the typical
-field size in observations.  
-A thorough exploration of cosmic variance impact as we present in this
-letter had not been presented so far in the literature.
+We find that once cosmic variance is taken into account, the
+observational data can only put weak constraints on \ \mmax\ and \focc. 
+When we translate these loos constraints into the median mass, we find
+a general consistency with previous works \citep{Hayashino2004,
+  Gawiser07,Ouchi2008} specially with the most recent one
+\citep{Bielby16}.
 
-Our analysis also allowed us to draw three results that can be used to
-put tighter constraints on $M_{\rm min}$, $M_{\rm max}$ and $f_{\rm
-  occ}$ once upcoming large LAE surveys, as the HETDEX project
-\citep{Hetdex2011} and the HSC ultra deep survey, are available : 
+Nevertheless, our analysis allowed us to draw three results that can
+be used to put tighter constraints on \mmin, \mmax and \focc once
+upcoming large LAE surveys, such as the HETDEX project 
+\citep{Hetdex2011} and the HSC ultra deep survey, are available: 
 \begin{enumerate}
-\item $f_{\rm occ}$ and the median mass of LAEs are almost uniquely
-  determined by $M_{\rm min}$ regardless of $M_{\rm max}$. \item
-  measuring the width of the LAE number distribution function obtained
-  over several fields of $\approx 1$ deg$^2$ one will be able to
-  tightly constrain  $M_{\rm min}$, $M_{\rm med}$ and $f_{\rm occ}$ up
-  to a factor of  2.  
-\item  $M_{\rm max}$ drives the ACF strength at short angular
+\item \focc is uniquely determined by \mmin, regardless of
+  \mmax. A precise determination of \mmin\ will thus fix \focc.
+\item The width of the LAE number distribution function
+  obtained over several fields of $\approx 1$ deg$^2$ is tightly
+  correlated with \mmin. That measurement with next generation surveys
+  will be able to constrain \mmin within a factor of $\sim 2$.
+\item  \mmax drives the ACF strength at short angular
   distances ($<1\,\rm arcmin$), therefore precise measurements of the
@@
 extranjeros/2013-63130316'' for their PhD scholarship support.
+
+JEFR acknowledges financial support from Vicerrector\'ia de
+Investigaciones at Uniandes from a a FAPA project.
 

### 2016-04-21 paper/ms.tex
bolshoi
Valentinos comments added. We still need to do a new FIG 2 where we clearly show how cosmic variance make it difficult to constrain Mmin. Jaime, please also compile this tex file and commit the PDF.  I always get a problem with the references when I try to compile

@@
 assuming a minimum (\mmin) and maximum mass (\mmax) for the dark
-matter halos hosting LAEs without predicting a \ly\  luminosity.  
+matter halos hosting LAEs  without assuming  an underlying relation 
+between the \ly\  luminosity and the dark matter halo mass.  
 This approach bypasses all the physical uncertainties associated to
@@
 \citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
-at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA\ and a flux limit
+at $z\sim 3$  with Ly-$\alpha$ equivalent widths of $\gtrsim$65\AA\ and a Ly-$\alpha$ flux limit
 of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
-Using spectroscopy they found a 22\% contamination fraction.
+Using spectroscopy they found a 22\% contamination fraction $f_{\rm c}$.
 Their observations cover 5 (out of 9) independent and adjacent
@@
 
-We use results from the Bolshoi simulation \citep{Bolshoi,BolshoiP} which was
+We use results from the BolshoiP simulation \citep{Bolshoi,BolshoiP} 
 performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side. 
@@
 halo, a duty cycle in the star formation rate, the escape fraction of
-\ly\ radiation and its detectability as a LAE.   
-We do not try to disentangle these effects.
+\ly\ radiation and its detectability as a LAE with Ly-$\alpha$ equivalent widths of $\gtrsim$65\AA.   
+We do not try to disentangle these effects and do not assume an underlying relation between the
+$\alpha$ luminosity and the dark matter halo mass.
 We instead opt for a purely arithmetic interpretation by setting
@@
 
-For each mock catalog we also randomly remove $22\%$ of the mock-LAEs and replace 
-them with randomly distrubuted points to mimic the effect of
+For each mock catalog we also randomly remove a fraction $f_{\rm c}=0.22$  of the mock-LAEs and replace 
+them with randomly distrubuted points to mimic the effect of interloper
 contamination   in \citet{Bielby16} observations. 
@@
 
-We make a thorough parameter space exploration of the models
-${\mathcal M}$ by  means of a Markov Chain Monte Carlo technique using
+We  explore the parameter space of the models
+${\mathcal M}$ by  means of the Markov Chain Monte Carlo technique using
 the EMCEE python package \citep{emcee2013}.
 
-We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
+The MCMC exploration is done using a total of 24 seeds and 400
+iterations (9600 models) to sample the posterior  probability distribution function 
+($P(\mathcal{M}|\mathrm{observations}$) based on the Angular
+Correlation Function (ACF). We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
 $9.2$ up to $13.4$, corresponding to the halo mass range of
@@
 same order as the dark matter halo cosmic variance shown in
-Fig. \ref{fig:cosmicv0}.
-
-The MCMC exploration is done using a total of 24 seeds and 400
-iterations (9600 models) to sample the posterior PDF,
-$P(\mathcal{M}|\mathrm{observations}) \propto \exp(-\chi_{\mathcal
-  M}^2/2)$, with the $\chi_{\mathcal{M}}^2$ based on the Angular
-Correlation Function (ACF),
+Fig. \ref{fig:cosmicv0}.   Our likelihood is taken proportional to
+$ \exp(-\chi_{\mathcal  M}^2/2)$, with the $\chi_{\mathcal{M}}^2$ where:
 
@@
 %
-where  $\rm{ACF}_{\mathcal M}$ and  $\rm{ACF}_{\rm obs}$ are the ACF
+Here  $\rm{ACF}_{\mathcal M}$ and  $\rm{ACF}_{\rm obs}$ are the ACF
 of the explored model ${\mathcal M}$ and the observational ACF
@@
 $\rm{ACF}_{\rm obs}$.
+
 We compute the $\rm{ACF}_{\mathcal M}$ using the Landy \&  Szalay
-estimator  \citep{Landy1993}.
+estimator  \citep{Landy1993}. After this,  we correct the computed ACF
+from the contamination fraction of interlopers $f_{\rm c}$ multiplying the
+ACF by a factor of $1/(1-f_{\rm c})^{2}$  following the  procedure described in
+ \citet{Bielby16}.
 
@@
   around $10^{10.5}$\hMsun.   
-  The mass width $\Delta \log M_{1\sigma}$ has a median of $0.3$ dex (a factor
-  of $2$ in mass) with a maximum value of $0.7$ dex (a factor of
+  The mass width $\Delta \log M_{1\sigma}$ has a median of $0.55$ dex (a factor
+  of $\sim3$ in mass) with a maximum value of $0.7$ dex (a factor of
   5). This means that all models consistent with observations have a
@@
 \citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} that used
-a more simplified approach.
+a more simplified semi-analitical approach.
 
@@
  \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
- \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} =
- 6.7^{+42.0}_{6.7}\times10^{10}$) using semi-analitical approaches.
+ \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} = 10^{10.8^{+1.8}_{-0.8}$) 
+using semi-analitical approaches.
 
@@
 There is only a factor of $2$ to $4$ between the lower and upper mass
-boundary.
+boundary of the central 68 percentile of the mass distribution. 
+\todo HERE WE NEED TO CLARIFY THAT MMAX CAN BE STILL VERY 
+LARGE BECAUSE OF THE ASSYMETRY IN THE DARK MATTER HALO MASS 
+FUNCTION MAYBE MENTIONING THE 2-SIGMA WIDTH THAT IS WAY MUCH 
+HIGHER THAN THE 1-SIGMA WIDTH. THIS IS ACTUALLY THE REASON FOR 
+THE POOR CONSTRAIN THAT WE OBTAIN IN MMAX BUT IT IS STILL IMPORTANT
+BECAUSE IT DETRMINES THE  STRENGTH OF THE CLUSTERING AT SHORT SCALES.
 
 Summarizing, the median mass could be anything in the range
-$10^{9.5}$\hMsun\ and $10^{11.5}$\hMsun\ (a $2.0$ dex range), but the width is
-highly constrained to be between $0.2$ and $0.6$ dex.
+$10^{9.5}$\hMsun\ and $10^{11.5}$\hMsun\ (a $2.0$ dex range), 
+but the 1-$\sigma$ width of the mass distribution is highly constrained 
+to be between $0.2$ and $0.6$ dex.
 
 In Fig. \ref{fig:corr} we show the computed
-$ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values
-of $\dlm$. We can see that the clustering gets stronger for larger
+$ACF_{\mathcal{M}}$ of models with $\lmmin=10.5$ and different values
+of $\dlm$. We can see that the clustering gets slightly stronger for larger
 values of \dlm. Nevertheless, due to the large impact of cosmic
@@
 $\mathcal{M}$. By simple inspection one can infer an increase in the
-distribution with as \lmmin increase.  This trend is confirmed in
+distribution with as \lmmin\ increases.  This trend is confirmed in
 Fig. \ref{fig:cosmicv}  where we plot the central 1-$\sigma$ (blue
@@
 \item \focc is uniquely determined by \mmin, regardless of
-  \mmax. A precise determination of \mmin\ will thus fix \focc.
+  \mmax. A precise determination of \mmin\ will thus fix \focc. As a consequence of this, for a given  \mmin the media mass is also  fixed.
+
+\item ALSO MENTION THIS HERE BECAUSE IS A STRONG CONSTRAIN:
+ the 1-$\sigma$ width of the mass distribution is highly constrained to be between $0.2$ and $0.6$ dex.
+
 \item The width of the LAE number distribution function
@@
   will be able to constrain \mmin within a factor of $\sim 2$.
-\item  \mmax drives the ACF strength at short angular
-  distances ($<1\,\rm arcmin$), therefore precise measurements of the
-  ACF at such scales are crucial to accurately determine \mmax.  
+\item The ACF becomes slightly stronger at short angular
+  distances ($<1\,\rm arcmin$) when \mmax\ increases therefore precise
+ measurements of the  ACF at such scales are crucial to accurately
+ determine \mmax.  
 \end{enumerate}
@@
 
-JM acknowledges ``CONICYT-PCHA/doctorado Nacional para
+JEMR acknowledges ``CONICYT-PCHA/doctorado Nacional para
 extranjeros/2013-63130316'' for their PhD scholarship support.

### 2016-04-25 paper/ms.tex
fixed compilation problem
small changes to ms.tex

@@
 We  explore the parameter space of the models
-${\mathcal M}$ by  means of the Markov Chain Monte Carlo technique using
-the EMCEE python package \citep{emcee2013}.
+${\mathcal M}$ by  means of the Affine Invariant  Markov Chain Monte Carlo technique using
+the EMCEE python package \citep[][and references therein]{emcee2013}.
 
@@
  \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
- \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} = 10^{10.8^{+1.8}_{-0.8}$) 
-using semi-analitical approaches.
+ \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} = 10^{10.8^{+1.8}_{-0.8}}$) 
+using semi-analitical approaches.   MENTION THAT OUR MASS IS SYSTEMATICALLY LOWER
+AND THAT (ONLY IF MAKE SENSE) WE DO NOT DISAGREE  THAT DARK MATTER OF BIELBY AND OTHERS  OF THEIR PARTICULAR FIELDS IRE WRONG, BUT WHEN THE COSMIC VARIANCE IS INCLUDES THAT IMPLIES THAT THA THE MEAIN MASS OF LAES IN THE UNIVERSE IS SMALLER (BECAUSE OF THE ASSIMETRY IN THE NUMBER DENSITY DISTRIBUTION FUNCTION).
+DO SEMIANALITIC MODELS ASSUME GAUSSIAN DISTRIBUTION OF MATTER PERTURBATIONS?
 
@@
  the 1-$\sigma$ width of the mass distribution is highly constrained to be between $0.2$ and $0.6$ dex.
+SOMETHING THAT IS ALSO IMPORTANT IS THAT THIS CONSTRAIN IS ASSUMING OUR MODEL IS RIGHT, IF IT HAPPENS TO BE THAT THE FUNCTION THAT RELATES LUMINOSITY WITH MASS IS VERY STEPPEN THEN THE RESULTS MAY CHANGE.
 

### 2016-04-25 paper/ms.tex
updated references

@@
 \label{sec:introduction}
-\toref ADD NEWER REFERENCES
+
 Lyman-$\alpha$ emitting galaxies (LAEs) are central to a wide range
 of subjects in extragalactic astronomy. 
-LAEs can be used as probes of reionization \citep{Dijkstra11}, tracers
-of large scale structure \citep{Koehler2007},  signposts for low
-metallicity stellar populations, markers of the galaxy formation
-process at high redshift \citep{Dayal2009,ForeroRomero2012} and
-tracers of active star formation \citep{Guaita2013}.
+LAEs can be used as probes of reionization \citep[for a recent review
+  see][and references therein]{Dijkstra14}, tracers  of large scale structure
+\citep{Koehler2007}, signposts for low metallicity stellar
+populations \citep[for a recent review see][and references
+  therein]{Hayes15}, markers of the galaxy formation process at high
+redshift \citep{Partridge67,Rhoads00,Blanc11} and tracers of active
+star formation.
 
@@
 the galaxy-halo connection.  
-Galaxy formation models suggest that the physical processes that regulate the star formation cycle are dependent on halo mass \citep[e.g.][]{Behroozi2013a}.
-The mass becomes the most important element in the halo-galaxy connection.
+Galaxy formation models suggest that the physical processes that
+regulate the star formation cycle are dependent on halo mass
+\citep[e.g.][]{Behroozi2013a}. 
+The mass becomes the most important element in the halo-galaxy
+connection.
 
@@
 find the relationship between halo mass, intrinsic \ly\ luminosities
-and observed \ly\ luminosities. This approach is usually implemented
-through semi-analytic models \citep{Garel2012,Orsi2012} and  full
-N-body hydrodynamical simulations \citep{Laursen2007, Dayal2009,
-  ForeroRomero2011, Yajima2012}.
+and observed \ly\ luminosities. 
+This approach is usually implemented through semi-analytic models
+\citep{Garel2012,Orsi2012} and  full N-body hydrodynamical simulations
+\citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012}.
 
 The downside of these calculations is the uncertainty in the
-estimation of the escape fraction of \ly\ photons. Given the resonant
-nature of the \ly\ line, the escape fraction is sensitive to  the dust
-contents, density, temperature, topology and kinematics of the neutral
-Hydrogen in the interstellar medium (ISM). The process of finding a
-consensus on the expected value for the \ly\ escape fraction in high
-redshift galaxies is still matter of open debate
-\citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.
+estimation of the escape fraction of \ly\ photons. 
+Given the resonant nature of the \ly\ line, the escape fraction is
+sensitive to  the dust contents, density, temperature, topology and
+kinematics of the neutral Hydrogen in the interstellar medium (ISM). 
+The process of finding a consensus on the expected value for the
+\ly\ escape fraction in high redshift galaxies is still matter of open
+debate
+\citep{Neufeld1991,Verhamme2006,ForeroRomero2012,Dijkstra2012,Laursen2013,Orsi2012,Yajima14}.
 
@@
 We use a simple model to populate a halo in the simulation with a LAE   
-assuming a minimum (\mmin) and maximum mass (\mmax) for the dark
+assuming a minimum, \mmin, and maximum mass, \mmax, for the dark
 matter halos hosting LAEs  without assuming  an underlying relation 
@@
 star formation and radiative transfer. 
-We use the Markov Chain Monte Carlo technique to obtain the likelihood
-of the parameters given the observational constraints.
+We then use the Markov Chain Monte Carlo technique to obtain the
+likelihood of the parameters given the observational constraints.
 

### 2016-04-25 paper/ms.tex
fixed references into main file. fixed keywords

@@
 However, we find that the same individual models have a relatively tight
-mass gap, $\Delta M \equiv \log_{10}\mmax - \log_{10}\mmin$, of $\Delta
-M\approx 0.3$dex.
+$1\sigma$ mass gap $\Delta M_{1\sigma}\approx 0.4$ dex.
 We are also able show that \focc\ is uniquely determined by $M_{\rm
-  min}$, regardless of $M_{\rm max}$, by
-$\focc\sim0.1(\mmin/10^{10.5}\hMsun )^{0.93}$.  
-However, the current observational data only allows us to put weak
-constraints on \mmin\ and consequently on \focc.
+  min}$, regardless of $M_{\rm max}$. 
 We argue that upcoming large surveys covering at least $25$ deg$^{2}$
@@
 distribution width, $W_{1\sigma}$, constructed over several fields of
-$\sim 1$ deg$^{2}$ using the relationship, $W_{1\sigma} =
-0.138\times (\mmin/10^{11}\hMsun )^{0.177}$, calibrated from our results.
+$\sim 1$ deg$^{2}$.
 \end{abstract}
@@
 \keywords{
-Cosmology: theory - large-scale structure of Universe -
-Methods: data analysis - numerical - N-body simulations
+Galaxies: halos --- Galaxies: high-redshift --- Galaxies: statistics
+--- Dark Matter --- Methods: numerical 
 }
@@
   27 mock fields. Each line corresponds to a
-  different model with increasig values of $M_{\rm min}$. 
-  Different models produce different number density distributions. The
-width of the distribution increases with \mmin. } 
+  different model with increasig values of \mmin. 
+  Different models produce different number density distributions. 
+  The width of the distribution increases with \mmin. } 
 \label{fig:cosmicv0}
@@
 Nevertheless, our analysis allowed us to draw three results that can
-be used to put tighter constraints on \mmin, \mmax and \focc once
+be used to put tighter constraints on \mmin and \focc once
 upcoming large LAE surveys, such as the HETDEX project 
 \citep{Hetdex2011} and the HSC ultra deep survey, are available:
+
 \begin{enumerate}
@@
   \mmax. A precise determination of \mmin\ will thus fix \focc. As a consequence of this, for a given  \mmin the media mass is also  fixed.
-
-\item ALSO MENTION THIS HERE BECAUSE IS A STRONG CONSTRAIN:
- the 1-$\sigma$ width of the mass distribution is highly constrained to be between $0.2$ and $0.6$ dex.
-SOMETHING THAT IS ALSO IMPORTANT IS THAT THIS CONSTRAIN IS ASSUMING OUR MODEL IS RIGHT, IF IT HAPPENS TO BE THAT THE FUNCTION THAT RELATES LUMINOSITY WITH MASS IS VERY STEPPEN THEN THE RESULTS MAY CHANGE.
 
@@
   will be able to constrain \mmin within a factor of $\sim 2$.
-\item The ACF becomes slightly stronger at short angular
-  distances ($<1\,\rm arcmin$) when \mmax\ increases therefore precise
- measurements of the  ACF at such scales are crucial to accurately
- determine \mmax.  
+
+We also find that the 1-$\sigma$ width of the mass distribution is
+highly constrained to be between $0.2$ and $0.6$ dex. 
+This result imposes constraints on different models for LAEs formation
+in a cosmological context as to why observable LAEs are constrained
+into a narrow halo mass range.
+
+Overall, our approach highlights the importance of forward modelling
+to take explicitly into account the effects of cosmic variance.
+We expect this
+
 \end{enumerate}
@@
 \bibliographystyle{apj}
-\bibliography{references.bib}
+%\bibliography{references.bib}
+\begin{thebibliography}{38}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Adams} {et~al.}(2011){Adams}, {Blanc}, {Hill}, {Gebhardt}, {Drory},
+  {Hao}, {Bender}, {Byun}, {Ciardullo}, {Cornell}, {Finkelstein}, {Fry},
+  {Gawiser}, {Gronwall}, {Hopp}, {Jeong}, {Kelz}, {Kelzenberg}, {Komatsu},
+  {MacQueen}, {Murphy}, {Odoms}, {Roth}, {Schneider}, {Tufts}, \&
+  {Wilkinson}}]{Hetdex2011}
+{Adams}, J.~J., {Blanc}, G.~A., {Hill}, G.~J., {Gebhardt}, K., {Drory}, N.,
+  {Hao}, L., {Bender}, R., {Byun}, J., {Ciardullo}, R., {Cornell}, M.~E.,
+  {Finkelstein}, S.~L., {Fry}, A., {Gawiser}, E., {Gronwall}, C., {Hopp}, U.,
+  {Jeong}, D., {Kelz}, A., {Kelzenberg}, R., {Komatsu}, E., {MacQueen}, P.~J.,
+  {Murphy}, J., {Odoms}, P.~S., {Roth}, M., {Schneider}, D.~P., {Tufts}, J.~R.,
+  \& {Wilkinson}, C.~P. 2011, \apjs, 192, 5
+
+\bibitem[{{Behroozi} {et~al.}(2013){Behroozi}, {Wechsler}, \&
+  {Conroy}}]{Behroozi2013a}
+{Behroozi}, P.~S., {Wechsler}, R.~H., \& {Conroy}, C. 2013, \apj, 770, 57
+
+\bibitem[{{Bielby} {et~al.}(2016){Bielby}, {Tummuangpak}, {Shanks}, {Francke},
+  {Crighton}, {Ba{\~n}ados}, {Gonz{\'a}lez-L{\'o}pez}, {Infante}, \&
+  {Orsi}}]{Bielby16}
+{Bielby}, R.~M., {Tummuangpak}, P., {Shanks}, T., {Francke}, H., {Crighton},
+  N.~H.~M., {Ba{\~n}ados}, E., {Gonz{\'a}lez-L{\'o}pez}, J., {Infante}, L., \&
+  {Orsi}, A. 2016, \mnras, 456, 4061
+
+\bibitem[{{Blanc} {et~al.}(2011){Blanc}, {Adams}, {Gebhardt}, {Hill}, {Drory},
+  {Hao}, {Bender}, {Ciardullo}, {Finkelstein}, {Fry}, {Gawiser}, {Gronwall},
+  {Hopp}, {Jeong}, {Kelzenberg}, {Komatsu}, {MacQueen}, {Murphy}, {Roth},
+  {Schneider}, \& {Tufts}}]{Blanc11}
+{Blanc}, G.~A., {Adams}, J.~J., {Gebhardt}, K., {Hill}, G.~J., {Drory}, N.,
+  {Hao}, L., {Bender}, R., {Ciardullo}, R., {Finkelstein}, S.~L., {Fry}, A.~B.,
+  {Gawiser}, E., {Gronwall}, C., {Hopp}, U., {Jeong}, D., {Kelzenberg}, R.,
+  {Komatsu}, E., {MacQueen}, P., {Murphy}, J.~D., {Roth}, M.~M., {Schneider},
+  D.~P., \& {Tufts}, J. 2011, \apj, 736, 31
+
+\bibitem[{{Bond} {et~al.}(2009){Bond}, {Gawiser}, {Gronwall}, {Ciardullo},
+  {Altmann}, \& {Schawinski}}]{Bond2009}
+{Bond}, N.~A., {Gawiser}, E., {Gronwall}, C., {Ciardullo}, R., {Altmann}, M.,
+  \& {Schawinski}, K. 2009, \apj, 705, 639
+
+\bibitem[{{Colberg} {et~al.}(2000){Colberg}, {White}, {Yoshida}, {MacFarland},
+  {Jenkins}, {Frenk}, {Pearce}, {Evrard}, {Couchman}, {Efstathiou}, {Peacock},
+  {Thomas}, \& {Virgo Consortium}}]{Colberg00}
+{Colberg}, J.~M., {White}, S.~D.~M., {Yoshida}, N., {MacFarland}, T.~J.,
+  {Jenkins}, A., {Frenk}, C.~S., {Pearce}, F.~R., {Evrard}, A.~E., {Couchman},
+  H.~M.~P., {Efstathiou}, G., {Peacock}, J.~A., {Thomas}, P.~A., \& {Virgo
+  Consortium}. 2000, \mnras, 319, 209
+
+\bibitem[{{Dayal} {et~al.}(2009){Dayal}, {Ferrara}, {Saro}, {Salvaterra},
+  {Borgani}, \& {Tornatore}}]{Dayal2009}
+{Dayal}, P., {Ferrara}, A., {Saro}, A., {Salvaterra}, R., {Borgani}, S., \&
+  {Tornatore}, L. 2009, \mnras, 400, 2000
+
+\bibitem[{{Dijkstra}(2014)}]{Dijkstra14}
+{Dijkstra}, M. 2014, \pasa, 31, e040
+
+\bibitem[{{Dijkstra} \& {Kramer}(2012)}]{Dijkstra2012}
+{Dijkstra}, M., \& {Kramer}, R. 2012, \mnras, 424, 1672
+
+\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
+  {Goodman}}]{emcee2013}
+{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
+  125, 306
+
+\bibitem[{{Forero-Romero} {et~al.}(2011){Forero-Romero}, {Yepes},
+  {Gottl{\"o}ber}, {Knollmann}, {Cuesta}, \& {Prada}}]{ForeroRomero2011}
+{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., {Knollmann}, S.~R.,
+  {Cuesta}, A.~J., \& {Prada}, F. 2011, \mnras, 415, 3666
+
+\bibitem[{{Forero-Romero} {et~al.}(2012){Forero-Romero}, {Yepes},
+  {Gottl{\"o}ber}, \& {Prada}}]{ForeroRomero2012}
+{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., \& {Prada}, F. 2012,
+  \mnras, 419, 952
+
+\bibitem[{{Garel} {et~al.}(2012){Garel}, {Blaizot}, {Guiderdoni}, {Schaerer},
+  {Verhamme}, \& {Hayes}}]{Garel2012}
+{Garel}, T., {Blaizot}, J., {Guiderdoni}, B., {Schaerer}, D., {Verhamme}, A.,
+  \& {Hayes}, M. 2012, \mnras, 422, 310
+
+\bibitem[{{Gawiser} {et~al.}(2007{\natexlab{a}}){Gawiser}, {Francke}, {Lai},
+  {Schawinski}, {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos},
+  {Blanc}, {Fazio}, \& {Feldmeier}}]{Gawiser2007}
+{Gawiser}, E., {Francke}, H., {Lai}, K., {Schawinski}, K., {Gronwall}, C.,
+  {Ciardullo}, R., {Quadri}, R., {Orsi}, A., {Barrientos}, L.~F., {Blanc},
+  G.~A., {Fazio}, G., \& {Feldmeier}, J.~J. 2007{\natexlab{a}}, \apj, 671, 278
+
+\bibitem[{{Gawiser} {et~al.}(2007{\natexlab{b}}){Gawiser}, {Francke}, {Lai},
+  {Schawinski}, {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos},
+  {Blanc}, {Fazio}, {Feldmeier}, {Huang}, {Infante}, {Lira}, \&
+  {Padilla}}]{Gawiser07}
+{Gawiser}, E., {Francke}, H., {Lai}, K., {Schawinski}, K., {Gronwall}, C.,
+  {Ciardullo}, R., {Quadri}, R., {Orsi}, A., {Barrientos}, L.~F., {Blanc},
+  G.~A., {Fazio}, G., {Feldmeier}, J.~J., {Huang}, J.-s., {Infante}, L.,
+  {Lira}, P., \& {Padilla}, N. 2007{\natexlab{b}}, \apj, 671, 278
+
+\bibitem[{{Hayashino} {et~al.}(2004){Hayashino}, {Matsuda}, {Tamura},
+  {Yamauchi}, {Yamada}, {Ajiki}, {Fujita}, {Murayama}, {Nagao}, {Ohta},
+  {Okamura}, {Ouchi}, {Shimasaku}, {Shioya}, \& {Taniguchi}}]{Hayashino2004}
+{Hayashino}, T., {Matsuda}, Y., {Tamura}, H., {Yamauchi}, R., {Yamada}, T.,
+  {Ajiki}, M., {Fujita}, S.~S., {Murayama}, T., {Nagao}, T., {Ohta}, K.,
+  {Okamura}, S., {Ouchi}, M., {Shimasaku}, K., {Shioya}, Y., \& {Taniguchi}, Y.
+  2004, \aj, 128, 2073
+
+\bibitem[{{Hayes}(2015)}]{Hayes15}
+{Hayes}, M. 2015, \pasa, 32, e027
+
+\bibitem[{{Jose} {et~al.}(2013){Jose}, {Srianand}, \&
+  {Subramanian}}]{Jose2013b}
+{Jose}, C., {Srianand}, R., \& {Subramanian}, K. 2013, ArXiv e-prints
+
+\bibitem[{{Klypin} {et~al.}(2014){Klypin}, {Yepes}, {Gottlober}, {Prada}, \&
+  {Hess}}]{BolshoiP}
+{Klypin}, A., {Yepes}, G., {Gottlober}, S., {Prada}, F., \& {Hess}, S. 2014,
+  ArXiv e-prints
+
+\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
+  {Primack}}]{Bolshoi}
+{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102
+
+\bibitem[{{Koehler} {et~al.}(2007){Koehler}, {Schuecker}, \&
+  {Gebhardt}}]{Koehler2007}
+{Koehler}, R.~S., {Schuecker}, P., \& {Gebhardt}, K. 2007, \aap, 462, 7
+
+\bibitem[{{Landy} \& {Szalay}(1993)}]{Landy1993}
+{Landy}, S.~D., \& {Szalay}, A.~S. 1993, \apj, 412, 64
+
+\bibitem[{{Laursen} {et~al.}(2013){Laursen}, {Duval}, \&
+  {{\"O}stlin}}]{Laursen2013}
+{Laursen}, P., {Duval}, F., \& {{\"O}stlin}, G. 2013, \apj, 766, 124
+
+\bibitem[{{Laursen} \& {Sommer-Larsen}(2007)}]{Laursen2007}
+{Laursen}, P., \& {Sommer-Larsen}, J. 2007, \apjl, 657, L69
+
+\bibitem[{{Neufeld}(1991)}]{Neufeld1991}
+{Neufeld}, D.~A. 1991, \apjl, 370, L85
+
+\bibitem[{{Nilsson} {et~al.}(2007){Nilsson}, {M{\o}ller}, {M{\"o}ller},
+  {Fynbo}, {Micha{\l}owski}, {Watson}, {Ledoux}, {Rosati}, {Pedersen}, \&
+  {Grove}}]{Nilsson2007}
+{Nilsson}, K.~K., {M{\o}ller}, P., {M{\"o}ller}, O., {Fynbo}, J.~P.~U.,
+  {Micha{\l}owski}, M.~J., {Watson}, D., {Ledoux}, C., {Rosati}, P.,
+  {Pedersen}, K., \& {Grove}, L.~F. 2007, \aap, 471, 71
+
+\bibitem[{{Orsi} {et~al.}(2012){Orsi}, {Lacey}, \& {Baugh}}]{Orsi2012}
+{Orsi}, A., {Lacey}, C.~G., \& {Baugh}, C.~M. 2012, \mnras, 425, 87
+
+\bibitem[{{Ouchi} {et~al.}(2008){Ouchi}, {Shimasaku}, {Akiyama}, {Simpson},
+  {Saito}, {Ueda}, {Furusawa}, {Sekiguchi}, {Yamada}, {Kodama}, {Kashikawa},
+  {Okamura}, {Iye}, {Takata}, {Yoshida}, \& {Yoshida}}]{Ouchi2008}
+{Ouchi}, M., {Shimasaku}, K., {Akiyama}, M., {Simpson}, C., {Saito}, T.,
+  {Ueda}, Y., {Furusawa}, H., {Sekiguchi}, K., {Yamada}, T., {Kodama}, T.,
+  {Kashikawa}, N., {Okamura}, S., {Iye}, M., {Takata}, T., {Yoshida}, M., \&
+  {Yoshida}, M. 2008, \apjs, 176, 301
+
+\bibitem[{{Ouchi} {et~al.}(2010){Ouchi}, {Shimasaku}, {Furusawa}, {Saito},
+  {Yoshida}, {Akiyama}, {Ono}, {Yamada}, {Ota}, {Kashikawa}, {Iye}, {Kodama},
+  {Okamura}, {Simpson}, \& {Yoshida}}]{Ouchi2010}
+{Ouchi}, M., {Shimasaku}, K., {Furusawa}, H., {Saito}, T., {Yoshida}, M.,
+  {Akiyama}, M., {Ono}, Y., {Yamada}, T., {Ota}, K., {Kashikawa}, N., {Iye},
+  M., {Kodama}, T., {Okamura}, S., {Simpson}, C., \& {Yoshida}, M. 2010, \apj,
+  723, 869
+
+\bibitem[{{Partridge} \& {Peebles}(1967)}]{Partridge67}
+{Partridge}, R.~B., \& {Peebles}, P.~J.~E. 1967, \apj, 147, 868
+
+\bibitem[{{Peebles}(1980)}]{Peebles1980}
+{Peebles}, P.~J.~E. 1980, {The large-scale structure of the universe}
+
+\bibitem[{{Planck Collaboration} {et~al.}(2014){Planck Collaboration}, {Ade},
+  {Aghanim}, {Armitage-Caplan}, {Arnaud}, {Ashdown}, {Atrio-Barandela},
+  {Aumont}, {Baccigalupi}, {Banday}, \& et~al.}]{Planck2014}
+{Planck Collaboration}, {Ade}, P.~A.~R., {Aghanim}, N., {Armitage-Caplan}, C.,
+  {Arnaud}, M., {Ashdown}, M., {Atrio-Barandela}, F., {Aumont}, J.,
+  {Baccigalupi}, C., {Banday}, A.~J., \& et~al. 2014, \aap, 571, A16
+
+\bibitem[{{Rhoads} {et~al.}(2000){Rhoads}, {Malhotra}, {Dey}, {Stern},
+  {Spinrad}, \& {Jannuzi}}]{Rhoads00}
+{Rhoads}, J.~E., {Malhotra}, S., {Dey}, A., {Stern}, D., {Spinrad}, H., \&
+  {Jannuzi}, B.~T. 2000, \apjl, 545, L85
+
+\bibitem[{Riebe {et~al.}(2013)Riebe, Partl, Enke, Forero-Romero, Gottlöber,
+  Klypin, Lemson, Prada, Primack, Steinmetz, \& Turchaninov}]{MultiDark}
+Riebe, K., Partl, A.~M., Enke, H., Forero-Romero, J., Gottlöber, S., Klypin,
+  A., Lemson, G., Prada, F., Primack, J.~R., Steinmetz, M., \& Turchaninov, V.
+  2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[{{Springel} {et~al.}(2005){Springel}, {White}, {Jenkins}, {Frenk},
+  {Yoshida}, {Gao}, {Navarro}, {Thacker}, {Croton}, {Helly}, {Peacock}, {Cole},
+  {Thomas}, {Couchman}, {Evrard}, {Colberg}, \& {Pearce}}]{SpringelNature05}
+{Springel}, V., {White}, S.~D.~M., {Jenkins}, A., {Frenk}, C.~S., {Yoshida},
+  N., {Gao}, L., {Navarro}, J., {Thacker}, R., {Croton}, D., {Helly}, J.,
+  {Peacock}, J.~A., {Cole}, S., {Thomas}, P., {Couchman}, H., {Evrard}, A.,
+  {Colberg}, J., \& {Pearce}, F. 2005, \nat, 435, 629
+
+\bibitem[{{Verhamme} {et~al.}(2006){Verhamme}, {Schaerer}, \&
+  {Maselli}}]{Verhamme2006}
+{Verhamme}, A., {Schaerer}, D., \& {Maselli}, A. 2006, \aap, 460, 397
+
+\bibitem[{{Yajima} {et~al.}(2012){Yajima}, {Choi}, \& {Nagamine}}]{Yajima2012}
+{Yajima}, H., {Choi}, J.-H., \& {Nagamine}, K. 2012, \mnras, 427, 2889
+
+\bibitem[{{Yajima} {et~al.}(2014){Yajima}, {Li}, {Zhu}, {Abel}, {Gronwall}, \&
+  {Ciardullo}}]{Yajima14}
+{Yajima}, H., {Li}, Y., {Zhu}, Q., {Abel}, T., {Gronwall}, C., \& {Ciardullo},
+  R. 2014, \mnras, 440, 776
+
+\end{thebibliography}
 

### 2016-04-25 paper/ms.tex
referencias, conclusiones

@@
 observations has a large uncertainty $M_{50} =
-3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun, in agreement with the most recent
-observational estimates.
+3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.
 However, we find that the same individual models have a relatively tight
-$1\sigma$ mass gap $\Delta M_{1\sigma}\approx 0.4$ dex.
+$1\sigma$ mass gap $\Delta M_{1\sigma} = 0.55^{+0.11}_{-0.31}$ dex.
 We are also able show that \focc\ is uniquely determined by $M_{\rm
@@
 $16$ and $84$ percentile values in the $\log M_{50}$ distribution.
-This result is consistent with previous
- estimations of  the  median dark matter halo mass reported by
- \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6}$),
- \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
- \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} = 10^{10.8^{+1.8}_{-0.8}}$) 
-using semi-analitical approaches.   MENTION THAT OUR MASS IS SYSTEMATICALLY LOWER
-AND THAT (ONLY IF MAKE SENSE) WE DO NOT DISAGREE  THAT DARK MATTER OF BIELBY AND OTHERS  OF THEIR PARTICULAR FIELDS IRE WRONG, BUT WHEN THE COSMIC VARIANCE IS INCLUDES THAT IMPLIES THAT THA THE MEAIN MASS OF LAES IN THE UNIVERSE IS SMALLER (BECAUSE OF THE ASSIMETRY IN THE NUMBER DENSITY DISTRIBUTION FUNCTION).
-DO SEMIANALITIC MODELS ASSUME GAUSSIAN DISTRIBUTION OF MATTER PERTURBATIONS?
+
+Our result is consistent within the statistical uncertainties with
+previous estimates reported by
+ \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6} \hMsun$),
+ \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9} \hMsun$) and
+ \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} = 10^{10.8^{+1.8}_{-0.8}} \hMsun$) 
+using semi-analitical approaches.   
+In spite of the large uncertainties, we note that our median mass is
+systematically below theirs by $0.3$ to $0.5$ dex.
 
@@
 boundary of the central 68 percentile of the mass distribution. 
-\todo HERE WE NEED TO CLARIFY THAT MMAX CAN BE STILL VERY 
-LARGE BECAUSE OF THE ASSYMETRY IN THE DARK MATTER HALO MASS 
-FUNCTION MAYBE MENTIONING THE 2-SIGMA WIDTH THAT IS WAY MUCH 
-HIGHER THAN THE 1-SIGMA WIDTH. THIS IS ACTUALLY THE REASON FOR 
-THE POOR CONSTRAIN THAT WE OBTAIN IN MMAX BUT IT IS STILL IMPORTANT
-BECAUSE IT DETRMINES THE  STRENGTH OF THE CLUSTERING AT SHORT SCALES.
+We emphasize that \mmax\ can still be very large while the width is
+small due to the asymetry in the dark matter halo mass function.
 
@@
 \subsection{Constraining Dark matter halos mass  with cosmic variance}
+
 Fig. \ref{fig:cosmicv0}  shows the  halo number distribution (HND) in
 the  mock fields of the simulation for different models
-$\mathcal{M}$. By simple inspection one can infer an increase in the
-distribution with as \lmmin\ increases.  This trend is confirmed in
-Fig. \ref{fig:cosmicv}  where we plot the central 1-$\sigma$ (blue
-diamonds) and 2-$\sigma$  (red dots) widths  of the NDH as a function
-of \lmmin. We particularly found that when we consider survey fields
-of $\sim1{\rm deg^2}$, the central  1-$\sigma$ (2-$\sigma$) width of
-the HND increases monotonically from 0.05dex (0.10dex) when
-$\lmmin=9.5$ to 0.20dex (0.35dex) when $\lmmin=12.0$. The latter
-result opens the possibility to constrain the \lmmin (as well as the
-median mass) of LAEs by simply measure the width of the distribution
-of observed LAE along several observational fields mapping $\sim1{\rm
-  deg^2}$ in area and the observational depth determined by the NB479
-filter.
+$\mathcal{M}$. 
+By simple inspection one can infer that the distribution width
+increases with \mmin.
+
+In Fig. \ref{fig:cosmicv} we confirm this trend by plotting the
+HND $1\sigma$ width for good models ($\chi^{2}_{\mathcal{M}}/2 < 1$) as a function
+of \lmmin. 
+We find that considering all the mock $25$ field the $1\sigma$ width, $W_{1\sigma}$
+increases with \mmin following
+
+\begin{equation}
+W_{1\sigma} = (0.138\pm 0.002) \times \left( \frac{\mmin}{10^{11}\hMsun} \right)^{0.177\pm0.009}.
+\label{eq:width}
+\end{equation}
+
+This result opens the possibility to constrain the \lmmin (as well as the
+median mass) of LAEs by simply measuring the width of the distribution
+of observed LAE along several observational fields. 
+This idea has been already explored for $z>6$ galaxies
+\citep{Robertson10}.
+
+To keep the validity of Eq. (\ref{eq:width}) there should at least be
+$27$ fields (to follow the same numbers we use here) of size $\sim1{\rm
+  deg^2}$ with the same observational coditions (filters, equivalent
+width cuts). 
+However, repeating the same kind of cosmic variance study for different
+survey strategies should help to provide a constraint of the same
+kind.
 
@@
 {\rm deg^2}$).      
-In our model a dark matter halo with mass in the range $M_{\rm
-  min}<M_{\mathrm h}<M_{\rm   max}$ can only host one detectable LAE
-at most.  
+In our model a dark matter halo with mass in the range $\mmin
+<M_{h}<\mmax$ can only host one detectable LAE at most.  
 We explored the parameter space determined by \mmin\ and \mmax\ using
@@
 We find that once cosmic variance is taken into account, the
-observational data can only put weak constraints on \ \mmax\ and \focc. 
+observational data can only put weak constraints on  \mmax\ and \focc. 
 When we translate these loos constraints into the median mass, we find
@@
 
-Nevertheless, our analysis allowed us to draw three results that can
+Nevertheless, our analysis allowed us to draw two results that can
 be used to put tighter constraints on \mmin and \focc once
@@
 \item \focc is uniquely determined by \mmin, regardless of
-  \mmax. A precise determination of \mmin\ will thus fix \focc. As a consequence of this, for a given  \mmin the media mass is also  fixed.
+  \mmax. A precise determination of \mmin\ will thus fix \focc. As a
+  consequence of this, for a given  \mmin the media mass is also
+  fixed.
 
@@
   obtained over several fields of $\approx 1$ deg$^2$ is tightly
-  correlated with \mmin. That measurement with next generation surveys
+  correlated with \mmin. 
+  That measurement with next generation surveys
   will be able to constrain \mmin within a factor of $\sim 2$.
+\end{enumerate}
 
@@
 highly constrained to be between $0.2$ and $0.6$ dex. 
-This result imposes constraints on different models for LAEs formation
-in a cosmological context as to why observable LAEs are constrained
-into a narrow halo mass range.
-
-Overall, our approach highlights the importance of forward modelling
-to take explicitly into account the effects of cosmic variance.
-We expect this
-
-\end{enumerate}
+This result can be used to test different models for LAEs formation
+in a cosmological context to better understand why observable LAEs are
+constrained into a narrow halo mass range.
 
@@
 %\bibliography{references.bib}
-\begin{thebibliography}{38}
+\begin{thebibliography}{39}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 
+\bibitem[{{Robertson}(2010)}]{Robertson10}
+{Robertson}, B.~E. 2010, \apjl, 716, L229
+
 \bibitem[{{Springel} {et~al.}(2005){Springel}, {White}, {Jenkins}, {Frenk},

### 2016-04-25 paper/ms.tex
updated plots with new  robust mass range for results

@@
 We find that the preferred minium and maximum masses in our model span
-a wide range $10^{9.6}\hMsun\leq \mmin \leq 10^{11.0}\hMsun$ ,
+a wide range $10^{9.8}\hMsun\leq \mmin \leq 10^{11.0}\hMsun$ ,
 $10^{10.9}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a

### 2016-04-25 paper/ms.tex
corner_plot.py updated to take only objects with logM>9.8. Little changes in ms.tex

@@
 We focus our work on halos more massive than $1.5\times
-10^{9}$\hMsun\ resolved with at least  $10$ particles. 
+10^{9}$\hMsun\ resolved with at least  $40$ particles 
+to guarantee a well behaved halo mass function. 
 We do not take into account sub-halos.
@@
 Correlation Function (ACF). We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
-$9.2$ up to $13.4$, corresponding to the halo mass range of
+$9.8$ up to $13.4$, corresponding to the halo mass range of
 the simulation at $z=3$.

### 2016-04-25 code/corner_plot.py

@@ -17,7 +17,11 @@ rc('font', **font)
 
 parspace=genfromtxt('../output/LAEBayes_mcmc_dM_1deg_fixed.out')
 parprob=genfromtxt('../output/LAEBayes_mcmc_dM_chi_1deg_fixed.out')
-parall=genfromtxt('../output/focc_1deg_fixed.txt',sxiprows=1)
+parall=genfromtxt('../output/focc_1deg_fixed.txt',skiprows=1)
+wmmin=parspace[:,0]>9.8
+parspace=parspace[wmmin]
+parprob=parprob[wmmin]
+parall=parall[wmmin]
 parspace[:,1]+=parspace[:,0]
 
 
@@ -34,7 +38,7 @@ fig.savefig('../output/likelyplot_1deg.png',  format='png', dpi=150,bbox_inches=
 fig = corner.corner(transpose([parall[:,0][arg_ini:],(1-fc)*parall[:,2][arg_ini:]]),weight=exp(parprob)[ :len( parall[:,0] ) ][arg_ini:],bins=20, smooth=0.6, labels=[r"$\log M_{\rm min}\left[\rm{M_{\odot}h^{-1}}\right]$", r"$\log f_{\rm occ}$"],quantiles=[0.16, 0.5, 0.84])
 fig.savefig('../output/likelyplot_1degf.png', format='png', dpi=150,bbox_inches='tight')
 fig = corner.corner(transpose([parall[:,0][arg_ini:], (parall[:,1]-parall[:,0])[arg_ini:] ]), weight=exp(parprob)[ :len( parall[:,0] ) ][arg_ini:], bins=20, smooth=0.6, labels=[r"$\log M_{\rm min}\left[\rm{M_{\odot}h^{-1}}\right]$", r"$\Delta \log M\left[\rm{M_{\odot}h^{-1}}\right]$"],quantiles=[0.16, 0.5, 0.84])
-fig.savefig('../output/likelyplot_1degdM.png', format='png', dpi=150,bbox_inches='tight')
+fig.savefig('../output/fig31.pdf', format='pdf', dpi=150,bbox_inches='tight')
 
[…]

### 2016-04-26 paper/ms.tex
new figure 3
udpates mass ranges

@@
 We find that the preferred minium and maximum masses in our model span
-a wide range $10^{9.8}\hMsun\leq \mmin \leq 10^{11.0}\hMsun$ ,
-$10^{10.9}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
+a wide range $10^{10.0}\hMsun\leq \mmin \leq 10^{11.1}\hMsun$ ,
+$10^{11.0}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
 wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
@@
 For each  halo in the box we extract its comoving position and mass.  
-We focus our work on halos more massive than $1.5\times
+We focus our work on halos more massive than $6.3\times
 10^{9}$\hMsun\ resolved with at least  $40$ particles 
@@
 \begin{center}
-\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
+\includegraphics[width=0.85\textwidth]{fig3.pdf}
 \end{center}
@@
 
-The preferred $1-\sigma$ range for the masses is $9.6<\log \mmin<11.0$
-and $10.9<\log\mmax<13.0$.
+The preferred $1-\sigma$ range for the masses is $10.0<\log \mmin<11.1$
+and $11.0<\log\mmax<13.0$.
 \focc\ is completely determined by \mmin\ from \focc$=$0.015 when
-$\log\mmin=9.6$ to $\focc=0.30$ when $\log\mmin=11.0$. 
+$\log\mmin=9.8$ to $\focc=0.30$ when $\log\mmin=11.0$. 
 We compute the power-law dependece between \focc\ and \mmin\ to be 

### 2016-04-26 paper/ms.tex
JM last revision. Few minor changes. I agree with submission

@@
 In our model a dark matter halo with mass in the range $\mmin
-<M_{\mathrm h}<\mmax$ can only host one detectable LAEat most.    
+<M_{\mathrm h}<\mmax$ can only host one detectable LAE at most.    
 We explore the parameter space determined by \mmin, \mmax\ and \focc\
@@
 constraints the angular correlation function (ACF) and the LAEs number density. 
-We find that the preferred minium and maximum masses in our model span
+We find that the preferred minimum and maximum masses in our model span
 a wide range $10^{10.0}\hMsun\leq \mmin \leq 10^{11.1}\hMsun$ ,
@@
 However, we find that the same individual models have a relatively tight
-$1\sigma$ mass gap $\Delta M_{1\sigma} = 0.55^{+0.11}_{-0.31}$ dex.
+$1\sigma$  scatter around the median mass $\Delta M_{1\sigma} = 0.55^{+0.11}_{-0.31}$ dex.
 We are also able show that \focc\ is uniquely determined by $M_{\rm
@@
 context.  
-Under the current structure formation paradigm the dominant matter
+Under the current structure formation paradigm, the dominant matter
 content of the Universe is dark matter (DM).  
@@
 regulate the star formation cycle are dependent on halo mass
-\citep[e.g.][]{Behroozi2013a}. 
-The mass becomes the most important element in the halo-galaxy
-connection.
+\citep[e.g.][]{Behroozi2013a}. Therefore, the mass becomes 
+the most important element in the halo-galaxy connection.
 
@@
 assuming a minimum, \mmin, and maximum mass, \mmax, for the dark
-matter halos hosting LAEs  without assuming  an underlying relation 
+matter halos hosting LAEs. We do not  assume  an underlying relation 
 between the \ly\  luminosity and the dark matter halo mass.  
@@
 density, vacuum density and the Hubble constant in units of 100 km
-s$^{-1}$ Mpc$^{-1}$.
+s$^{-1}$ Mpc$^{-1}$.  The values are consistent with \citet{Planck2014} results.
 
@@
   27 mock fields. Each line corresponds to a
-  different model with increasig values of \mmin. 
+  different model with increasing values of \mmin. 
   Different models produce different number density distributions. 
@@
 of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
-Using spectroscopy they found a 22\% contamination fraction $f_{\rm c}$.
+Using follow-up spectroscopy they found a 22\% contamination fraction $f_{\rm c}$.
 Their observations cover 5 (out of 9) independent and adjacent
@@
 \citet{Bielby16} used the NB497  narrow-band filter whose 77\AA\ FWHM
-and 154\AA\ Full width  tenth maximum (FWTM) correspond to a total observational depth of
-44\hMpc\  and 82\hMpc\ comoving, respectively.
+and 154\AA\ Full width  tenth maximum (FWTM) correspond to a total observational comoving depth of
+44\hMpc\  and 82\hMpc, respectively.
 
@@
   due to cosmic variance. Radically different models in $\Delta \log M$ are consistent with
-  observations once cosmic variance is modelled in detail.} 
+  observations once cosmic variance is modeled in detail.} 
 \label{fig:corr}
@@
 We use results from the BolshoiP simulation \citep{Bolshoi,BolshoiP} 
-performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side. 
+performed in a cubic  comoving volume of 250 $h^{-1}$\hMpc  on a side. 
 The dark matter distribution was sampled using  $2048^{3}$
@@
 For each  halo in the box we extract its comoving position and mass.  
-We focus our work on halos more massive than $6.3\times
+We focus our work on halos more massive than $6.0\times
 10^{9}$\hMsun\ resolved with at least  $40$ particles 
-to guarantee a well behaved halo mass function. 
+to guarantee statistical significance and a well behaved halo mass function. 
 We do not take into account sub-halos.
@@
 correlation function \citep{Jose2013b} and observations that confirm a
-lack of class pairs in LAEs \cite{Bond2009}.  
+lack of  class pairs in LAEs \citep{Bond2009}.  
 Then we say that a halo will host a LAE with probability $\focc$
@@
   h} < \mmax$. 
-We also use the variable \dlm to represent the mass range width,
+We also use the variable \dlm\ to represent the mass range width,
 $\dlm\equiv\ \log \mmax - \log \mmax$.
@@
 For each mock catalog we also randomly remove a fraction $f_{\rm c}=0.22$  of the mock-LAEs and replace 
-them with randomly distrubuted points to mimic the effect of interloper
+them with randomly distributed points to mimic the effect of interloper
 contamination   in \citet{Bielby16} observations. 
@@
 Fig. \ref{fig:cosmicv0}  shows the cumulative halo number density
-for all 27 subvolumes in the simulation, with a normalization by the
-average number density among fields. 
+for all 27 sub-volumes in the simulation, with a normalization by the
+median number density among fields ($\langle n \rangle$). 
 Each line represents a different model $\mathcal{M}$ with fixed
@@
 Fig. \ref{fig:cosmicv0}.   Our likelihood is taken proportional to
-$ \exp(-\chi_{\mathcal  M}^2/2)$, with the $\chi_{\mathcal{M}}^2$ where:
+$ \exp(-\chi_{\mathcal  M}^2/2)$  where:
 
@@
 of the explored model ${\mathcal M}$ and the observational ACF
-reported by \citet{Bielby16} respectively.
+reported by \citet{Bielby16}, respectively.
 $\sigma_{\rm \mathcal M}$ is the associated 1-$\sigma$ scatter  of the
@@
 This already shows that radically different models can be compatible
-with observations once cosmic variance uncertainties are modelled in
+with observations once cosmic variance uncertainties are modeled in
 detail.
@@
 
-The preferred $1-\sigma$ range for the masses is $10.0<\log \mmin<11.1$
+The preferred $1-\sigma$ range for the masses is $10.0<\log \mmin<11.2$
 and $11.0<\log\mmax<13.0$.
-\focc\ is completely determined by \mmin\ from \focc$=$0.015 when
-$\log\mmin=9.8$ to $\focc=0.30$ when $\log\mmin=11.0$. 
-We compute the power-law dependece between \focc\ and \mmin\ to be 
+\focc\ is completely determined by \mmin\ from \focc$=$0.011 when
+$\log\mmin=10.0$ to $\focc=0.39$ when $\log\mmin=11.15$. 
+We compute the power-law dependence between \focc\ and \mmin\ to be 
 \begin{equation}
-\focc = 0.1\left(\frac{\mmin}{10^{10.5}\hMsun}\right)^{0.93}.
+\focc = 0.08\left(\frac{\mmin}{10^{10.3}\hMsun}\right)^{0.77}.
 \end{equation}
-We remind the reader that models whith $\log \focc>0.00$ ($\focc>1$)
+We remind the reader that models with $\log \focc>0.00$ ($\focc>1$)
 correspond to cases where the halo number density is smaller 
@@
 \citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} that used
-a more simplified semi-analitical approach.
+a more simplified semi-analytical approach.
 
@@
 
-From this distribution we obtain $\log M_{50} = 10.5\pm 0.6$ or
-equivalently $M_{50} = 3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.  
+From this distribution we obtain $\log M_{50} = 10.8\pm 0.6$ or
+equivalently $M_{50} = 6.3^{+18.8}_{-4.7}\times 10^{10}$\hMsun.  
 The $1\sigma$ uncertainty for this median value is estimated from the
@@
 previous estimates reported by
- \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6} \hMsun$),
- \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9} \hMsun$) and
- \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} = 10^{10.8^{+1.8}_{-0.8}} \hMsun$) 
-using semi-analitical approaches.   
-In spite of the large uncertainties, we note that our median mass is
-systematically below theirs by $0.3$ to $0.5$ dex.
+ \citet{Bielby16} ($\log M_{50} = 10^{11.0\pm0.6} \hMsun$),
+ \citet{Gawiser07} ($\log M_{50}= 10^{10.9\pm0.9} \hMsun$) and
+ \citet{Ouchi2010} ($\log M_{50} = 10^{10.8^{+1.8}_{-0.8}} \hMsun$) 
+using semi-analytical approaches.   Our result is slightly below the  \citet{Bielby16}
+ median mass estimation. This could probably be attributed to the fact that  \citet{Bielby16}
+only represent a particular field of the universe while our $\log M_{50}$  represents the
+median mass of the universe after taking into account cosmic variance that allows lower mass 
+halos to be also consistent with observations.
 
-However, the same Figure \ref{fig:mmed} shows something 
+Figure \ref{fig:mmed} also shows something 
 that semi-analytical approaches were not able to predict.
@@
 median value and $1\sigma$ uncertainty of $\Delta \log M_{1\sigma} =
-0.55^{+0.11}_{-0.31}$ dex.
+0.51^{+0.10}_{-0.30}$ dex.
 This means that the mass range for halos hosting LAEs is very narrow.
@@
 We emphasize that \mmax\ can still be very large while the width is
-small due to the asymetry in the dark matter halo mass function.
+small due to the asymmetry in the dark matter halo mass function.
 
 Summarizing, the median mass could be anything in the range
-$10^{9.5}$\hMsun\ and $10^{11.5}$\hMsun\ (a $2.0$ dex range), 
+$10^{10.2}$\hMsun\ and $10^{11.4}$\hMsun\ (a $2.0$ dex range), 
 but the 1-$\sigma$ width of the mass distribution is highly constrained 
@@
 $27$ fields (to follow the same numbers we use here) of size $\sim1{\rm
-  deg^2}$ with the same observational coditions (filters, equivalent
+  deg^2}$ with the same observational conditions (filters, equivalent
 width cuts). 
@@
   ($\chi_{\mathcal M}/2 < 1$) are included.
-  The strong dependence of $n/ \langle n\rangle$ with \mmin was
+  The strong dependence of $\langle
+ n\rangle$ with \mmin was
   parameterized as a power law with the parameters shown in the legend.
@@
 We explored the parameter space determined by \mmin\ and \mmax\ using 
-Monte Carlo Markov-Chain minimization to match the observed  ACF and
-mean number density of LAEs.    
+affine invariant Monte Carlo Markov-Chain minimization to match
+ the observed  ACF and mean number density of LAEs.    
 It is the first time that such a thorough exploration of the cosmic
@@
 We find that once cosmic variance is taken into account, the
-observational data can only put weak constraints on  \mmax\ and \focc. 
-When we translate these loos constraints into the median mass, we find
+observational data can only put weak constraints on  \mmin\ and \focc. 
+When we translate these loose constraints into the median mass, we find
 a general consistency with previous works \citep{Hayashino2004,
@@
 Nevertheless, our analysis allowed us to draw two results that can
-be used to put tighter constraints on \mmin and \focc once
+be used to put tighter constraints on \mmin\ and \focc\ once
 upcoming large LAE surveys, such as the HETDEX project 
@@
 \begin{enumerate}
-\item \focc is uniquely determined by \mmin, regardless of
+\item \focc\ is uniquely determined by \mmin, regardless of
   \mmax. A precise determination of \mmin\ will thus fix \focc. As a
-  consequence of this, for a given  \mmin the media mass is also
+  consequence of this, for a given  \mmin\ the median mass is also
   fixed.

### 2016-04-26 paper/ms.tex
minor changes

@@
 We use results from the BolshoiP simulation \citep{Bolshoi,BolshoiP} 
-performed in a cubic  comoving volume of 250 $h^{-1}$\hMpc  on a side. 
+performed in a cubic  comoving volume of 250\hMpc\  on a side. 
 The dark matter distribution was sampled using  $2048^{3}$
@@
 for all 27 sub-volumes in the simulation, with a normalization by the
-median number density among fields ($\langle n \rangle$). 
+median number density among fields, $\langle n \rangle$. 
 Each line represents a different model $\mathcal{M}$ with fixed
@@
 The MCMC exploration is done using a total of 24 seeds and 400
-iterations (9600 models) to sample the posterior  probability distribution function 
-($P(\mathcal{M}|\mathrm{observations}$) based on the Angular
+iterations (9600 models) to sample the posterior  probability distribution function, $P(\mathcal{M}|\mathrm{observations})$, based on the Angular
 Correlation Function (ACF). We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
@@
 previous estimates reported by
- \citet{Bielby16} ($\log M_{50} = 10^{11.0\pm0.6} \hMsun$),
- \citet{Gawiser07} ($\log M_{50}= 10^{10.9\pm0.9} \hMsun$) and
- \citet{Ouchi2010} ($\log M_{50} = 10^{10.8^{+1.8}_{-0.8}} \hMsun$) 
+ \citet{Bielby16} ($M_{50} = 10^{11.0\pm0.6} \hMsun$),
+ \citet{Gawiser07} ($M_{50}= 10^{10.9\pm0.9} \hMsun$) and
+ \citet{Ouchi2010} ($M_{50} = 10^{10.8^{+1.8}_{-0.8}} \hMsun$) 
 using semi-analytical approaches.   Our result is slightly below the  \citet{Bielby16}
@@
 of \lmmin. 
-We find that considering all the mock $25$ field the $1\sigma$ width, $W_{1\sigma}$
+We find that considering all the $27$ mock fields the $1\sigma$ width, $W_{1\sigma}$
 increases with \mmin following
@@
 \caption{$1\sigma$ width of the number density distribution over the
-  54 mock fields of the simulation as a function of \mmin. 
+  as a function of \mmin. 
   Only the models that have a good match with observations
@@
 This result can be used to test different models for LAEs formation
-in a cosmological context to better understand why observable LAEs are
+in a cosmological context to better understand why observable LAEs seem to be
 constrained into a narrow halo mass range.

### 2016-05-05 paper/ms.tex
submitted paper

@@
 
-In this letter we investigate the impact of cosmic variance in
+In this paper we investigate the impact of cosmic variance in
 constraining the mass and occupation fraction of halos hosting LAEs at $z=3$.
@@
 
-Throughout this letter we assume a $\Lambda$CDM cosmology with the
+Throughout this paper we assume a $\Lambda$CDM cosmology with the
 following values for the cosmological parameters, $\Omega_{m}=0.30711$,
@@
 \caption{One and two dimensional projections of the posterior
-  probability distributions of \mmin, \mmax\ and \focc\. 
+  probability distributions of \mmin, \mmax\ and \focc. 
   The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
@@
 
-In what follows we note by the letter ${\mathcal M}$ a model
+In what follows we note by the paper ${\mathcal M}$ a model
 defined by a particular choice of the two parameters $M_{\rm min}$, 
@@
 
-In this letter we studied the impact of cosmic variance and
+In this paper we studied the impact of cosmic variance and
 observational uncertainties in constraining the mass range and

### 2016-06-13 paper/ms.tex
nuevos puntos en el paper, mas detalle en la primera respuesta

@@
 $1\sigma$  scatter around the median mass $\Delta M_{1\sigma} = 0.55^{+0.11}_{-0.31}$ dex.
-We are also able show that \focc\ is uniquely determined by $M_{\rm
+We are also able to show that \focc\ is uniquely determined by $M_{\rm
   min}$, regardless of $M_{\rm max}$. 
@@
 $\sim 1$ deg$^{2}$.
+These results suggest that taking explicitly into account the effect of cosmic
+variance using cosmological simulations is a valuable tool to 
+interpret LAEs observations at high redshift.
 \end{abstract}
@@
 particles.
+
+We chose this simulation based on three requirements. 
+First, the simulation should have cosmological parameters consistent
+with the most recent constraints from Cosmic Microwave Background
+experiments and provide public acces to the data.
+Second, the halo mass function from the simulation should be robust
+down to masses that include the range of possibilities from previous
+observational efforts \cite[e.g. results from][impose a lower bound of
+  $10^{10}$\hMsun.]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} .
+Third, the total volume of the simulation should be at least 10 times
+larger the equivalent volume of a single LAE observation field.
+This conditions are met as we describe below.
+
 The cosmological parameters are consistent with Planck
@@
 $h^{-1}$ M$_{\odot}$. 
+Data is available to the
+public through an online
+interface \footnote{\url{http://www.multidark.org/MultiDark/}}
+\citep{MultiDark}.
 
@@
 algorithm. 
-The catalogs were obtained from the publicly available Multidark
-database  \footnote{\url{http://www.multidark.org/MultiDark/}}
-\citep{MultiDark}. 
 For each  halo in the box we extract its comoving position and mass.  
@@
 
+\subsection{Hints of larger uncertainties}
+
+Fig. \ref{fig:like} shows an interesting feature for \mmin. 
+The histogram (upper left) showing the probability for this parameter
+given the observational constraints does not considerably decreases for lower
+masses. 
+A valid questions is the following. Down to which values of
+\mmin\ does the probability significantly decreases?
+
+Lower values of \mmin\ would imply a lower \focc\ and larger
+uncertainties on the parameters \mmin\, \focc and $M_{50}$.
+In other words, the limitations in our priors for \mmin\ (which
+set the limitations for the kind of numerical simulation we use) might
+be underestimating the uncertainties and slightly biasing our results
+for \mmin\, \focc\ and $M_{50}$.
+
+Although Fig. \ref{fig:mmed} suggest that models with lower values of
+$M_{\rm 50}$, i.e. lower values of \mmin, have a higher
+$\chi^2_{\mathcal{M}}$ and could be thus discarded, we suggest that a
+proper test of this hypothesis requires performing new cosmological
+simulations to be able to probe \mmin\ masses below our limit of
+$6\times  10^{9}$\hMsun.
+
+This highlights the main thesis of this paper. 
+Namely, the high impact that cosmic variance can have on constraining
+the paremeters of our model. 
+With the current limitations in the cosmological simulations available
+to the public we cannot significantly decrease or prior on \mmin.
+We consider such test beyond the scope of this paper.
+
+This extension to larger priors cannot change other central results of
+our paper, such as the relationship between \focc\ and \mmin\, the
+narrow mass range for individual models and the possibility to
+constraint the halo mass with cosmic variance on the number density
+counts. 
+However, we suggest that future work building upon the
+technique presented in this paper should count with simulations that
+extend at least one order of magnitude below our limit $6\times
+10^{9}$\hMsun.
+
 %*************************************************************************
@@
 \citep{Bielby16}.
+
+This work also highlights the need to explore a wider range on the
+prior of \mmin\ if one wants to better estimate the uncertainty on
+\mmin, \focc\ and $M_{50}$.  
+In this paper we use priors given by previous observations, but our
+results suggest that once cosmic variance is explicitly taken into
+account, even lower values of \mmin\ might be in fact consistent with
+observations. 
+We recommend that future work making use of the technique presented
+in this paper should extend the prior for \mmin\ to masses at least
+one order of magnitude below $6\times 10^{9}$\hMsun.
 

### 2016-06-13 paper/ms.tex
typo
segunda respuesta, modificacion en el cuerpo del paper

@@
 larger the equivalent volume of a single LAE observation field.
-This conditions are met as we describe below.
+These conditions are met as we describe below.
 
@@
 \focc = 0.08\left(\frac{\mmin}{10^{10.3}\hMsun}\right)^{0.77}.
+\label{eq:focc}
 \end{equation}
@@
 \S\ref{subsec:explore}).
+
+The result in Eq.(\ref{eq:focc}) can be qualitatively understood as
+follows.   
+A choice of $\focc<1$ means that the halo mass function is scaled down.
+If \mmin\ decreases the total number of halos increases because less
+massive halos are more abundant.
+This requires smaller values of $\focc$ to keep the total
+number of halos equal to the number of LAES in observations.
 

### 2016-06-14 paper/ms.tex
agradecimientos
Some changes in the abstract to improve readability. Also some changes in referee_report.txt

@@
 \begin{abstract}
-We study the impact of cosmic variance and observational uncertainties
+In this paper we study the impact of cosmic variance and observational uncertainties
 in constraining the mass and occupation fraction, \focc, of
 dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
-We construct mock catalogs from an N-body simulation to match the 
+To this end, we constructed mock catalogs from an N-body simulation to match the 
 typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
@@
 <M_{\mathrm h}<\mmax$ can only host one detectable LAE at most.    
-We explore the parameter space determined by \mmin, \mmax\ and \focc\
-with a Markov Chain Monte-Carlo algorithm using as observational
-constraints the angular correlation function (ACF) and the LAEs number density. 
+We proceed to  explore the parameter space determined by \mmin, \mmax\ and \focc\
+with a Markov Chain Monte-Carlo algorithm using the angular correlation function (ACF) and the LAEs number density  as observational constraints. 
 We find that the preferred minimum and maximum masses in our model span
@@
 wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
-As a consequence the median mass, $M_{50}$, of all models consistent with
-observations has a large uncertainty $M_{50} =
+As a consequence the median mass, $M_{50}$, of all the consistent models has a large uncertainty $M_{50} =
 3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.
@@
 \citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
-at $z\sim 3$  with Ly-$\alpha$ equivalent widths of $\gtrsim$65\AA\ and a Ly-$\alpha$ flux limit
+at $z\sim 3$  with Ly-$\alpha$ rest-frame equivalent widths $\gtrsim$65\AA\ and a  Ly-$\alpha$ flux limit
 of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
@@
 
-In what follows we note by the paper ${\mathcal M}$ a model
-defined by a particular choice of the two parameters $M_{\rm min}$, 
+In what follows we will describe by the letter ${\mathcal M}$  a model
+defined by a particular choice of the two parameters $M_{\rm min}$ and
 $M_{\rm  max}$. For each model  ${\mathcal M}$ we define
@@
 
+The authors acknowldge the referee, Nelson Padilla, for useful
+remarks and questions that helped us to improve the quality and
+clarity of our paper.
+
 JEMR acknowledges ``CONICYT-PCHA/doctorado Nacional para

### 2016-06-14 paper/ms.tex
going trhough the minor comments on the referee report and the paper

@@
 In these studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
-the conclusions derived on the halo host mass do not elaborate on the
-uncertainty resulting from the cosmic variance on these fields.
+the conclusions derived on the halo host mass do not elaborate deeply on the
+uncertainty resulting from the cosmic variance on these fields. {\bf  \citet{Guaita2010} attempted to analytically 
+estimate the uncertainty from cosmic variance 
+following \citet{Somerville2004} and \citet{Peebles1980}. Their prescription assumes 
+that the correlation function can represented by a power-law $\psi\left(r\right)=\left(r_{0}/r\right)^{\gamma}$.
+Their estimation of cosmic variance strongly depends on $r_{0}$ and $\gamma$.
+However, $\gamma$ is only  poorly constrained with current observations which in turns indicates that their cosmic variance estimation could not be precise.}
 
@@
 We then use the Markov Chain Monte Carlo technique to obtain the
-likelihood of the parameters given the observational constraints.
+likelihood of the parameters given the observational constraints. {\bf This approach 
+allow us to estimate cosmic variance directly from simulations without making any assumption 
+on the correlation function behavior.}
 
@@
 \citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
-at $z\sim 3$  with Ly-$\alpha$ rest-frame equivalent widths $\gtrsim$65\AA\ and a  Ly-$\alpha$ flux limit
+at $z\sim 3$  with Ly-$\alpha$ {\bf rest-frame} equivalent widths $\gtrsim$65\AA\ and a  Ly-$\alpha$ flux limit
 of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
@@
 
-The result in Eq.(\ref{eq:focc}) can be qualitatively understood as
+{\bf The result in Eq.(\ref{eq:focc}) can be qualitatively understood as
 follows.   
@@
 This requires smaller values of $\focc$ to keep the total
-number of halos equal to the number of LAES in observations.
+number of halos hosting LAEs equal to the number of LAEs in observations.}
 
@@
 
+\bibitem[{{Guaita} {et~al.}(2010){Guaita}, {Gawiser}, {Padilla},
+  {Francke}, {Bond}, {Gronwall}, {Ciardullo}, {Feldmeier}, {Sinawa}, {Blanc},
+  \& {Virani}}]{Guaita2010}
+{Guaita}, L., {Gawiser}, E., {Padilla}, N., {Francke}, H.,
+	{Bond}, N.~A., {Gronwall}, C., {Ciardullo}, R., {Feldmeier}, J.~J., 
+	{Sinawa}, S., {Blanc}, G.~A., \& {Virani}, S. 2010, \apj, 714, 255
+
 \bibitem[{{Hayashino} {et~al.}(2004){Hayashino}, {Matsuda}, {Tamura},
@@
 
+@ARTICLE{2004ApJ...600L.171S,
+   author = {{Somerville}, R.~S. and {Lee}, K. and {Ferguson}, H.~C. and 
+	{Gardner}, J.~P. and {Moustakas}, L.~A. and {Giavalisco}, M.
+	},
+    title = "{Cosmic Variance in the Great Observatories Origins Deep Survey}",
+  journal = {\apjl},
+   eprint = {astro-ph/0309071},
+ keywords = {Galaxies: Statistics, Cosmology: Large-Scale Structure of Universe},
+     year = 2004,
+    month = jan,
+   volume = 600,
+    pages = {L171-L174},
+      doi = {10.1086/378628},
+   adsurl = {http://adsabs.harvard.edu/abs/2004ApJ...600L.171S},
+  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
+}
+
+\bibitem[{{Somerville} {et~al.}(2004){Somerville}, {Lee}, {Ferguson}, {Gardner},
+  {Moustakas}, \& {Giavalisco}}]{Somerville2004}
+{Somerville}, R.~S., {Lee}, K., {Ferguson}, H.~C.,
+	{Gardner}, J.~P., {Moustakas}, L.~A., \& {Giavalisco}, M. 204, \apj,
+  600, 171
+
 \bibitem[{{Springel} {et~al.}(2005){Springel}, {White}, {Jenkins}, {Frenk},

### 2016-06-14 paper/ms.tex
new references

@@
 \submitted{{\it Submitted for publication in ApJ}}
-\usepackage{multirow,color,wrapfig,ulem}
+\usepackage{multirow,color,wrapfig}
 \usepackage {graphicx}
@@
 % To highlight comments
-\definecolor{red}{rgb}{1,0.0,0.0}
-\newcommand{\red}{\color{red}}
-\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
-\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
-\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
-\newcommand{\before}[1]{\textcolor{red}{ #1}}
-\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
 
@@
 dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
-To this end, we constructed mock catalogs from an N-body simulation to match the 
+To this end, we construct mock catalogs from an N-body simulation to match the 
 typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
@@
 masses. 
-A valid questions is the following. Down to which values of
+This raises the following question. Down to which values of
 \mmin\ does the probability significantly decreases?
@@
 
-@ARTICLE{2004ApJ...600L.171S,
-   author = {{Somerville}, R.~S. and {Lee}, K. and {Ferguson}, H.~C. and 
-	{Gardner}, J.~P. and {Moustakas}, L.~A. and {Giavalisco}, M.
-	},
-    title = "{Cosmic Variance in the Great Observatories Origins Deep Survey}",
-  journal = {\apjl},
-   eprint = {astro-ph/0309071},
- keywords = {Galaxies: Statistics, Cosmology: Large-Scale Structure of Universe},
-     year = 2004,
-    month = jan,
-   volume = 600,
-    pages = {L171-L174},
-      doi = {10.1086/378628},
-   adsurl = {http://adsabs.harvard.edu/abs/2004ApJ...600L.171S},
-  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
-}
-
 \bibitem[{{Somerville} {et~al.}(2004){Somerville}, {Lee}, {Ferguson}, {Gardner},

### 2016-06-14 paper/ms_old.tex
previous version + diff

--- 2016-06-14 paper/ms.tex
@@
 \begin{abstract}
-In this paper we study the impact of cosmic variance and observational uncertainties
+We study the impact of cosmic variance and observational uncertainties
 in constraining the mass and occupation fraction, \focc, of
 dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
-To this end, we constructed mock catalogs from an N-body simulation to match the 
+We construct mock catalogs from an N-body simulation to match the 
 typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
@@
 <M_{\mathrm h}<\mmax$ can only host one detectable LAE at most.    
-We proceed to  explore the parameter space determined by \mmin, \mmax\ and \focc\
-with a Markov Chain Monte-Carlo algorithm using the angular correlation function (ACF) and the LAEs number density  as observational constraints. 
+We explore the parameter space determined by \mmin, \mmax\ and \focc\
+with a Markov Chain Monte-Carlo algorithm using as observational
+constraints the angular correlation function (ACF) and the LAEs number density. 
 We find that the preferred minimum and maximum masses in our model span
@@
 wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
-As a consequence the median mass, $M_{50}$, of all the consistent models has a large uncertainty $M_{50} =
+As a consequence the median mass, $M_{50}$, of all models consistent with
+observations has a large uncertainty $M_{50} =
 3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.
@@
 $1\sigma$  scatter around the median mass $\Delta M_{1\sigma} = 0.55^{+0.11}_{-0.31}$ dex.
-We are also able to show that \focc\ is uniquely determined by $M_{\rm
+We are also able show that \focc\ is uniquely determined by $M_{\rm
   min}$, regardless of $M_{\rm max}$. 
@@
 $\sim 1$ deg$^{2}$.
-These results suggest that taking explicitly into account the effect of cosmic
-variance using cosmological simulations is a valuable tool to 
-interpret LAEs observations at high redshift.
 \end{abstract}
@@
 \citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
-at $z\sim 3$  with Ly-$\alpha$ rest-frame equivalent widths $\gtrsim$65\AA\ and a  Ly-$\alpha$ flux limit
+at $z\sim 3$  with Ly-$\alpha$ equivalent widths of $\gtrsim$65\AA\ and a Ly-$\alpha$ flux limit
 of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
@@
 particles. 
-
-We chose this simulation based on three requirements. 
-First, the simulation should have cosmological parameters consistent
-with the most recent constraints from Cosmic Microwave Background
-experiments and provide public acces to the data.
-Second, the halo mass function from the simulation should be robust
-down to masses that include the range of possibilities from previous
-observational efforts \cite[e.g. results from][impose a lower bound of
-  $10^{10}$\hMsun.]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} .
-Third, the total volume of the simulation should be at least 10 times
-larger the equivalent volume of a single LAE observation field.
-These conditions are met as we describe below.
-
 The cosmological parameters are consistent with Planck
@@
 $h^{-1}$ M$_{\odot}$.
-Data is available to the
-public through an online
-interface \footnote{\url{http://www.multidark.org/MultiDark/}}
-\citep{MultiDark}.
 
@@
 algorithm. 
+The catalogs were obtained from the publicly available Multidark
+database  \footnote{\url{http://www.multidark.org/MultiDark/}}
+\citep{MultiDark}. 
 For each  halo in the box we extract its comoving position and mass.  
@@
 
-In what follows we will describe by the letter ${\mathcal M}$  a model
-defined by a particular choice of the two parameters $M_{\rm min}$ and
+In what follows we note by the paper ${\mathcal M}$ a model
+defined by a particular choice of the two parameters $M_{\rm min}$, 
 $M_{\rm  max}$. For each model  ${\mathcal M}$ we define
@@
 \focc = 0.08\left(\frac{\mmin}{10^{10.3}\hMsun}\right)^{0.77}.
-\label{eq:focc}
 \end{equation}
@@
 \S\ref{subsec:explore}).
-
-The result in Eq.(\ref{eq:focc}) can be qualitatively understood as
-follows.   
-A choice of $\focc<1$ means that the halo mass function is scaled down.
-If \mmin\ decreases the total number of halos increases because less
-massive halos are more abundant.
-This requires smaller values of $\focc$ to keep the total
-number of halos equal to the number of LAES in observations.
 
@@
 
-\subsection{Hints of larger uncertainties}
-
-Fig. \ref{fig:like} shows an interesting feature for \mmin. 
-The histogram (upper left) showing the probability for this parameter
-given the observational constraints does not considerably decreases for lower
-masses. 
-A valid questions is the following. Down to which values of
-\mmin\ does the probability significantly decreases?
-
-Lower values of \mmin\ would imply a lower \focc\ and larger
-uncertainties on the parameters \mmin\, \focc and $M_{50}$.
-In other words, the limitations in our priors for \mmin\ (which
-set the limitations for the kind of numerical simulation we use) might
-be underestimating the uncertainties and slightly biasing our results
-for \mmin\, \focc\ and $M_{50}$.
-
-Although Fig. \ref{fig:mmed} suggest that models with lower values of
-$M_{\rm 50}$, i.e. lower values of \mmin, have a higher
-$\chi^2_{\mathcal{M}}$ and could be thus discarded, we suggest that a
-proper test of this hypothesis requires performing new cosmological
-simulations to be able to probe \mmin\ masses below our limit of
-$6\times  10^{9}$\hMsun.
-
-This highlights the main thesis of this paper. 
-Namely, the high impact that cosmic variance can have on constraining
-the paremeters of our model. 
-With the current limitations in the cosmological simulations available
-to the public we cannot significantly decrease or prior on \mmin.
-We consider such test beyond the scope of this paper.
-
-This extension to larger priors cannot change other central results of
-our paper, such as the relationship between \focc\ and \mmin\, the
-narrow mass range for individual models and the possibility to
-constraint the halo mass with cosmic variance on the number density
-counts. 
-However, we suggest that future work building upon the
-technique presented in this paper should count with simulations that
-extend at least one order of magnitude below our limit $6\times
-10^{9}$\hMsun.
-
 %*************************************************************************
@@
 
-This work also highlights the need to explore a wider range on the
-prior of \mmin\ if one wants to better estimate the uncertainty on
-\mmin, \focc\ and $M_{50}$.  
-In this paper we use priors given by previous observations, but our
-results suggest that once cosmic variance is explicitly taken into
-account, even lower values of \mmin\ might be in fact consistent with
-observations. 
-We recommend that future work making use of the technique presented
-in this paper should extend the prior for \mmin\ to masses at least
-one order of magnitude below $6\times 10^{9}$\hMsun.
-
 Nevertheless, our analysis allowed us to draw two results that can
@@
 \section*{Acknowledgments}
-
-The authors acknowldge the referee, Nelson Padilla, for useful
-remarks and questions that helped us to improve the quality and
-clarity of our paper.
 

### 2016-06-14 paper/ms.tex
new reply

@@
 should be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
-distribution width, $W_{1\sigma}$, constructed over several fields of
+distribution width constructed over several fields of
 $\sim 1$ deg$^{2}$.
@@
 the conclusions derived on the halo host mass do not elaborate deeply on the
-uncertainty resulting from the cosmic variance on these fields. {\bf  \citet{Guaita2010} attempted to analytically 
+uncertainty resulting from the cosmic variance on these fields. 
+For instance, \citet{Guaita2010} attempted to analytically 
 estimate the uncertainty from cosmic variance 
-following \citet{Somerville2004} and \citet{Peebles1980}. Their prescription assumes 
-that the correlation function can represented by a power-law $\psi\left(r\right)=\left(r_{0}/r\right)^{\gamma}$.
-Their estimation of cosmic variance strongly depends on $r_{0}$ and $\gamma$.
-However, $\gamma$ is only  poorly constrained with current observations which in turns indicates that their cosmic variance estimation could not be precise.}
+following \citet{Somerville2004} and \citet{Peebles1980}. 
+Their prescription assumed that the correlation function can be
+represented by a power-law
+$\psi\left(r\right)=\left(r_{0}/r\right)^{\gamma}$. 
+Their estimation of cosmic variance strongly depends on $r_{0}$ and
+$\gamma$.  
+However, $\gamma$ is only poorly constrained with current
+observations which in turns indicates that their cosmic variance
+estimation could not be precise.
 
@@
 We then use the Markov Chain Monte Carlo technique to obtain the
-likelihood of the parameters given the observational constraints. {\bf This approach 
-allow us to estimate cosmic variance directly from simulations without making any assumption 
-on the correlation function behavior.}
+likelihood of the parameters given the observational constraints.
+This approach allows us to estimate cosmic variance directly from
+simulations without making any assumption  on the correlation function
+behavior. ma
 
@@
 \citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
-at $z\sim 3$  with Ly-$\alpha$ {\bf rest-frame} equivalent widths $\gtrsim$65\AA\ and a  Ly-$\alpha$ flux limit
-of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
+at $z\sim 3$  with Ly-$\alpha$ rest-frame equivalent widths
+$\gtrsim$65\AA\ and a  Ly-$\alpha$ flux limit of $2\times10^{17}{\rm
+  erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $).  
 Using follow-up spectroscopy they found a 22\% contamination fraction $f_{\rm c}$.
@@
 and $11.0<\log\mmax<13.0$.
-\focc\ is completely determined by \mmin\ from \focc$=$0.011 when
-$\log\mmin=10.0$ to $\focc=0.39$ when $\log\mmin=11.15$. 
+\focc\ is completely determined by \mmin\ from \focc$=$0.004 when
+$\log\mmin=10.0$ to $\focc=0.38$ when $\log\mmin=11.15$. 
 We compute the power-law dependence between \focc\ and \mmin\ to be 
 \begin{equation}
-\focc = 0.08\left(\frac{\mmin}{10^{10.3}\hMsun}\right)^{0.77}.
+\focc = 0.05\left(\frac{\mmin}{10^{10}\hMsun}\right)^{0.77}.
 \label{eq:focc}
@@
 
-{\bf The result in Eq.(\ref{eq:focc}) can be qualitatively understood as
+The result in Eq.(\ref{eq:focc}) can be qualitatively understood as
 follows.   
@@
 This requires smaller values of $\focc$ to keep the total
-number of halos hosting LAEs equal to the number of LAEs in observations.}
+number of halos hosting LAEs equal to the number of LAEs in observations.
 

### 2016-06-14 paper/ms.tex
done with the major points

@@
 
+We do not include the covariance matrix due to the
+practical impossibility to estimate it in a robust way.
+The small size of the fields and galaxies make it
+unfeasible the application of jackknife and bootstrap techniques \citep{2009MNRAS.396...19N}. 
+An estimate from N-body simulation faces the same problem with the
+additional limitation that we want to solve in the first place. 
+Namely, not knowing the range of halo masses that produces the
+observed clustering signal.  
+Tests that we performed in the simulation show that, due to the small
+number of points to estimate the clustering, the covariance matrix is
+not stable, even for similar models. 
+Using the full error covariance matrix, when not noise
+dominated, versus only diagonal elements usually has a small effect
+on clustering analyses \citep{2011ApJ...736...59Z}.
+
 We compute the $\rm{ACF}_{\mathcal M}$ using the Landy \&  Szalay
@@
 %\bibliography{references.bib}
+
 \begin{thebibliography}{39}
@@
 
+\bibitem[{{Norberg} {et~al.}(2009){Norberg}, {Baugh}, {Gazta{\~n}aga}, \&
+  {Croton}}]{2009MNRAS.396...19N}
+{Norberg}, P., {Baugh}, C.~M., {Gazta{\~n}aga}, E., \& {Croton}, D.~J. 2009,
+  \mnras, 396, 19
+
 \bibitem[{{Orsi} {et~al.}(2012){Orsi}, {Lacey}, \& {Baugh}}]{Orsi2012}
@@
 
+\bibitem[{{Zehavi} {et~al.}(2011){Zehavi}, {Zheng}, {Weinberg}, {Blanton},
+  {Bahcall}, {Berlind}, {Brinkmann}, {Frieman}, {Gunn}, {Lupton}, {Nichol},
+  {Percival}, {Schneider}, {Skibba}, {Strauss}, {Tegmark}, \&
+  {York}}]{2011ApJ...736...59Z}
+{Zehavi}, I., {Zheng}, Z., {Weinberg}, D.~H., {Blanton}, M.~R., {Bahcall},
+  N.~A., {Berlind}, A.~A., {Brinkmann}, J., {Frieman}, J.~A., {Gunn}, J.~E.,
+  {Lupton}, R.~H., {Nichol}, R.~C., {Percival}, W.~J., {Schneider}, D.~P.,
+  {Skibba}, R.~A., {Strauss}, M.~A., {Tegmark}, M., \& {York}, D.~G. 2011,
+  \apj, 736, 59
+
 \end{thebibliography}

### 2016-06-14 paper/ms.tex
full reply ready, new references

@@
 simulations without making any assumption  on the correlation function
-behavior. ma
+behavior.
 
@@
 We chose this simulation based on three requirements. 
-First, the simulation should have cosmological parameters consistent
+First, the simulation has cosmological parameters consistent
 with the most recent constraints from Cosmic Microwave Background
 experiments and provide public acces to the data.
-Second, the halo mass function from the simulation should be robust
-down to masses that include the range of possibilities from previous
-observational efforts \cite[e.g. results from][impose a lower bound of
-  $10^{10}$\hMsun.]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} .
-Third, the total volume of the simulation should be at least 10 times
+Second, the halo mass function from the simulation is robust
+down to  $10^{10}$\hMsun, which is the lower halo mass bound suggested
+by previous observational 
+studies\citep{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. 
+Third, the total volume of the simulation is at least 10 times
 larger the equivalent volume of a single LAE observation field.
@@
   probability distributions of \mmin, \mmax\ and \focc. 
+  Vertical lines in the one dimensional proyections correspond to the
+  14-50,84 percentiles of the distribtions.
+  Thick lines in the two dimensional planes mark the 1-2-3 $\sigma$
+  contours of the corresponding joint distributions.
   The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
@@
 %\bibliography{references.bib}
-
-\begin{thebibliography}{39}
+\begin{thebibliography}{43}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 
-\bibitem[{{Guaita} {et~al.}(2010){Guaita}, {Gawiser}, {Padilla},
-  {Francke}, {Bond}, {Gronwall}, {Ciardullo}, {Feldmeier}, {Sinawa}, {Blanc},
-  \& {Virani}}]{Guaita2010}
-{Guaita}, L., {Gawiser}, E., {Padilla}, N., {Francke}, H.,
-	{Bond}, N.~A., {Gronwall}, C., {Ciardullo}, R., {Feldmeier}, J.~J., 
-	{Sinawa}, S., {Blanc}, G.~A., \& {Virani}, S. 2010, \apj, 714, 255
+\bibitem[{{Guaita} {et~al.}(2010){Guaita}, {Gawiser}, {Padilla}, {Francke},
+  {Bond}, {Gronwall}, {Ciardullo}, {Feldmeier}, {Sinawa}, {Blanc}, \&
+  {Virani}}]{Guaita2010}
+{Guaita}, L., {Gawiser}, E., {Padilla}, N., {Francke}, H., {Bond}, N.~A.,
+  {Gronwall}, C., {Ciardullo}, R., {Feldmeier}, J.~J., {Sinawa}, S., {Blanc},
+  G.~A., \& {Virani}, S. 2010, \apj, 714, 255
 
@@
   {Subramanian}}]{Jose2013b}
-{Jose}, C., {Srianand}, R., \& {Subramanian}, K. 2013, ArXiv e-prints
+{Jose}, C., {Srianand}, R., \& {Subramanian}, K. 2013, \mnras, 435, 368
 
-\bibitem[{{Klypin} {et~al.}(2014){Klypin}, {Yepes}, {Gottlober}, {Prada}, \&
-  {Hess}}]{BolshoiP}
-{Klypin}, A., {Yepes}, G., {Gottlober}, S., {Prada}, F., \& {Hess}, S. 2014,
-  ArXiv e-prints
+\bibitem[{{Klypin} {et~al.}(2016){Klypin}, {Yepes}, {Gottl{\"o}ber}, {Prada},
+  \& {He{\ss}}}]{BolshoiP}
+{Klypin}, A., {Yepes}, G., {Gottl{\"o}ber}, S., {Prada}, F., \& {He{\ss}}, S.
+  2016, \mnras, 457, 4340
 
@@
 
-\bibitem[{{Somerville} {et~al.}(2004){Somerville}, {Lee}, {Ferguson}, {Gardner},
-  {Moustakas}, \& {Giavalisco}}]{Somerville2004}
-{Somerville}, R.~S., {Lee}, K., {Ferguson}, H.~C.,
-	{Gardner}, J.~P., {Moustakas}, L.~A., \& {Giavalisco}, M. 204, \apj,
-  600, 171
+\bibitem[{{Somerville} {et~al.}(2004){Somerville}, {Lee}, {Ferguson},
+  {Gardner}, {Moustakas}, \& {Giavalisco}}]{Somerville2004}
+{Somerville}, R.~S., {Lee}, K., {Ferguson}, H.~C., {Gardner}, J.~P.,
+  {Moustakas}, L.~A., \& {Giavalisco}, M. 2004, \apjl, 600, L171
 

### 2016-06-14 paper/ms.tex
minor changes in the paper and referee report

--- 2016-06-14 paper/ms.tex
@@
 
+ To keep the validity of Eq. (\ref{eq:width}) there should be of the order of
+ $27$ field or even a larger number. Each of these fields should have  $\sim1{\rm
+  deg^2}$ in size and reproduce the same observational conditions of 
+  \citet{Bielby16} in terms of filters, equivalent
+width cuts .  However, repeating the same kind of cosmic variance 
+study for different survey strategies should help to provide a equivalent
+constraint.
+
 \subsection{Hints of larger uncertainties}

### 2016-06-14 paper/ms.tex
last JEMR check

@@
 represented by a power-law
-$\psi\left(r\right)=\left(r_{0}/r\right)^{\gamma}$. 
+$\xi\left(r\right)=\left(r_{0}/r\right)^{\gamma}$. 
 Their estimation of cosmic variance strongly depends on $r_{0}$ and
@@
 by previous observational 
-studies\citep{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. 
+studies \citep{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. 
 Third, the total volume of the simulation is at least 10 times
-larger the equivalent volume of a single LAE observation field.
+larger than the equivalent volume of a single LAE observational field.
 These conditions are met as we describe below.

### 2016-06-14 paper/ms.tex
new title, new acknowledgemets

@@
 %=========================================================================
-\title{Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$}
+\title{Impact of cosmic variance on the galaxy-halo connection for Lyman-$\alpha$ emitters }
 \author{
@@
 remarks and questions that helped us to improve the quality and
-clarity of our paper.
+clarity of our paper. The authors also acknowldge Valentino Gonzalez,
+Eric Gawiser and Mark Dijkstra for the fruitful discussion and
+suggestions that also contributed to improve the quality of this work.
 

### 2016-06-14 paper/ms.tex
typos

--- 2016-06-14 paper/ms.tex
@@
 %=========================================================================
-\title{Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$}
+\title{Impact of cosmic variance on the galaxy-halo connection for Lyman-$\alpha$ emitters}
 \author{
@@
 with the most recent constraints from Cosmic Microwave Background
-experiments and provide public acces to the data.
+experiments and provide public access to the data.
 Second, the halo mass function from the simulation is robust
@@
   probability distributions of \mmin, \mmax\ and \focc. 
-  Vertical lines in the one dimensional proyections correspond to the
-  14-50,84 percentiles of the distribtions.
+  Vertical lines in the one dimensional projections correspond to the
+  14-50,84 percentiles of the distributions.
   Thick lines in the two dimensional planes mark the 1-2-3 $\sigma$
@@
 
-The authors acknowldge the referee, Nelson Padilla, for useful
+The authors acknowledge the referee, Nelson Padilla, for useful
 remarks and questions that helped us to improve the quality and
-clarity of our paper.
+clarity of our paper. The authors also acknowledge Valentino Gonzalez,
+Eric Gawiser and Mark Dijkstra for the fruitful discussion and
+suggestions that also contributed to improve the quality of this work.
 

### 2016-06-14 paper/ms.tex
massive refactoring

@@
 not stable, even for similar models. 
-Using the full error covariance matrix, when not noise
+Furthermore, using the full error covariance matrix, when not noise
 dominated, versus only diagonal elements usually has a small effect
